---
title: "TOPX DDM Test-Retest"
author: "Jessica Arend"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r}
# clear workspace
rm(list=ls())

# read in packages
pacman::p_load(stats, stringr, dplyr, tidyr, ggplot2, lme4, emmeans, lmerTest, Matrix, pbkrtest, psych, patchwork, purrr)
```

# Read/reformat TOPX data
```{r}
# dat_topx <- read.csv("~/Documents/umn_work/analyses/topx_analyses/topx_clean/aggregate_data/aggregate_topx_20250125.csv") 
dat_topx <- read.csv("~/Documents/umn_work/analyses/topx_analyses/topx_clean/aggregate_data/aggregate_topx_20260509.csv")

dat_topx[dat_topx == "BL1.5"] <- "BL1"
dat_topx[dat_topx == "BL2.5"] <- "BL2"
dat_topx[dat_topx == "6M.5"] <- "6M"
dat_topx[dat_topx == "7M.5"] <- "7M"
dat_topx[dat_topx == "12M.5"] <- "12M"

## Baseline 1
dat_bl1_topx <- dat_topx %>% 
  filter(visit == "BL1") 

## Baseline 2
dat_bl2_topx <- dat_topx %>% 
  filter(visit == "BL2") 

## 6-Month
dat_6m_topx <- dat_topx %>% 
  filter(visit == "6M") 

## match BL1 to BL2 TOPX 
dat_bl1_topx_rev <- subset(dat_bl1_topx, (subj %in% dat_bl2_topx$subj))
dat_bl2_topx_rev <- subset(dat_bl2_topx, (subj %in% dat_bl1_topx$subj))

## merge TOPX data
dat_all_topx <- rbind(dat_bl1_topx_rev, dat_bl2_topx_rev)
dat_all_topx$subj_idx <- dat_all_topx$subj
```

## optional: filter dat behav by another dataset
```{r}
# ddm_sample_subjx <- read.csv("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/data/topx_ddm_sample_subjx_20250316.csv") 
ddm_sample_subjx <- read.csv("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/data/topx_ddm_sample_subjx_20260509.csv")

# subj1 <- ddm_sample_subjx$subj
# subj2 <- ddm_sample_subjx2$subj
# only_in_1 <- setdiff(subj1, subj2)
# only_in_1

dat_all_topx <- subset(dat_all_topx, subj %in% ddm_sample_subjx$subj)
```

### write functions to calculate ICCs for TOPX
```{r}
# function to run ICCs by group
calc_ICC_topx <- function(icc_trialtype, icc_group, var) {
  library(dplyr)
  library(psych)
  
  # filter and rename bl1 data
  icc_dat_bl1 <- dat_bl1_topx_rev %>% 
    filter(trial_type == icc_trialtype) %>% 
    select(subj, group, !!sym(var)) %>% 
    rename(icc_bl1_var = !!sym(var))
  
  # Filter and rename bl2 data
  icc_dat_bl2 <- dat_bl2_topx_rev %>% 
    filter(trial_type == icc_trialtype) %>% 
    select(subj, group, !!sym(var)) %>% 
    rename(icc_bl2_var = !!sym(var))
  
  # Combine baseline 1 and 2 data
  icc_dat_comb <- merge(icc_dat_bl1, icc_dat_bl2, by = c("subj","group"),
                        all = TRUE)
  
  # Subset combined data for one group only
  icc_dat_comb_grp <- icc_dat_comb %>%
    filter(group == icc_group) %>%
    select(icc_bl1_var, icc_bl2_var)
  
  # Run ICC for group
  return(ICC(icc_dat_comb_grp, lmer = TRUE))
}

# function to run ICCs for all participants
calc_ICC_topx_all <- function(icc_trialtype, var) {
  library(dplyr)
  library(psych)

  # filter and rename bl1 data
  icc_dat_bl1 <- dat_bl1_topx_rev %>%
    filter(trial_type == icc_trialtype) %>%
    select(subj, !!sym(var)) %>%
    rename(icc_bl1_var = !!sym(var))

  # Filter and rename bl2 data
  icc_dat_bl2 <- dat_bl2_topx_rev %>%
    filter(trial_type == icc_trialtype) %>%
    select(subj, !!sym(var)) %>%
    rename(icc_bl2_var = !!sym(var))

  # Combine baseline 1 and 2 data
  icc_dat_comb <- merge(icc_dat_bl1, icc_dat_bl2, by = c("subj"), 
                        all = TRUE)

  # Subset combined data for both pts and controls
  icc_dat_comb <- icc_dat_comb %>%
    select(icc_bl1_var, icc_bl2_var)

  # Run ICC for all ppts
  return(ICC(icc_dat_comb, lmer = TRUE))
}

```

## TOPX Error: ICC
```{r, message=F}
icc_err_ax_all <- calc_ICC_topx_all("AX", "error")
icc_err_ax_pt <- calc_ICC_topx("AX", "Patient", "error")
icc_err_ax_ctl <- calc_ICC_topx("AX", "Control", "error")

icc_err_ay_all <- calc_ICC_topx_all("AY", "error")
icc_err_ay_pt <- calc_ICC_topx("AY", "Patient", "error") 
icc_err_ay_ctl <- calc_ICC_topx("AY", "Control", "error") 

icc_err_bx_all <- calc_ICC_topx_all("BX", "error")
icc_err_bx_pt <- calc_ICC_topx("BX", "Patient", "error")
icc_err_bx_ctl <- calc_ICC_topx("BX", "Control", "error")

icc_err_by_all <- calc_ICC_topx_all("BY", "error")
icc_err_by_pt <- calc_ICC_topx("BY", "Patient", "error") 
icc_err_by_ctl <- calc_ICC_topx("BY", "Control", "error") 
```

#### NEW Table: TOPX Error ICC Correlations/P-values
```{r}
# trial_types <- c("AX", "AY", "BX", "BY")
# groups <- c("Patient", "Control")
# 
# # helper to extract ICC row
# extract_icc <- function(icc_obj) {
#   tibble(
#     icc = icc_obj$results[1, 2],
#     low = icc_obj$results[1, 7],
#     up  = icc_obj$results[1, 8],
#     p = icc_obj$results[1, 6]
#   )
# }
# 
# icc_table_topx_err <- expand_grid(
#   trial_type = trial_types,
#   group = groups
# ) %>%
#   mutate(
#     icc_obj = map2(trial_type, group,
#                    ~ calc_ICC_topx(.x, .y, "error")),
#     icc_vals = map(icc_obj, extract_icc)
#   ) %>%
#   unnest(icc_vals) %>%
#   select(-icc_obj)
# 
# # Print the data frame to verify
# print(icc_table_topx_err)
```

#### OLD Table: TOPX Error ICC Correlations/P-values
```{r, echo=F}
icc_table_topx_err <- data.frame(
  trial_type = character(4),
  all_icc= numeric(4),
  all_lowCI = numeric(4),
  all_upCI  = numeric(4),
  # all_p = numeric(4),
  pt_icc = character(4),
  pt_lowCI = numeric(4),
  pt_upCI = numeric(4),
  # pt_p = numeric(4),
  ctl_icc = numeric(4),
  ctl_lowCI = numeric(4),
  ctl_upCI = numeric(4),
  # ctl_p = numeric(4),
  stringsAsFactors = FALSE
)

# Fill in the "parameter" column with the specified values
icc_table_topx_err$trial_type <- c("AX", "AY", "BX", "BY")

# all ICCs
icc_table_topx_err$all_icc <- c(icc_err_ax_all$results[1,2], icc_err_ay_all$results[1,2], icc_err_bx_all$results[1,2], icc_err_by_all$results[1,2])
icc_table_topx_err$all_lowCI <- c(icc_err_ax_all$results[1,7], icc_err_ay_all$results[1,7],  icc_err_bx_all$results[1,7], icc_err_by_all$results[1,7])
icc_table_topx_err$all_upCI <- c(icc_err_ax_all$results[1,8], icc_err_ay_all$results[1,8],  icc_err_bx_all$results[1,8], icc_err_by_all$results[1,8])
# icc_table_topx_err$all_p <- c(icc_err_ax_all$results[1,6], icc_err_ay_all$results[1,6],  icc_err_bx_all$results[1,6], icc_err_by_all$results[1,6])

# patient ICCs
icc_table_topx_err$pt_icc <- c(icc_err_ax_pt$results[1,2], icc_err_ay_pt$results[1,2], icc_err_bx_pt$results[1,2], icc_err_by_pt$results[1,2])
icc_table_topx_err$pt_lowCI <- c(icc_err_ax_pt$results[1,7], icc_err_ay_pt$results[1,7],  icc_err_bx_pt$results[1,7], icc_err_by_pt$results[1,7])
icc_table_topx_err$pt_upCI <- c(icc_err_ax_pt$results[1,8], icc_err_ay_pt$results[1,8],  icc_err_bx_pt$results[1,8], icc_err_by_pt$results[1,8])
# icc_table_topx_err$pt_p <- c(icc_err_ax_pt$results[1,6], icc_err_ay_pt$results[1,6], icc_err_bx_pt$results[1,6], icc_err_by_pt$results[1,6])

# control ICCs
icc_table_topx_err$ctl_icc <- c(icc_err_ax_ctl$results[1,2], icc_err_ay_ctl$results[1,2], icc_err_bx_ctl$results[1,2], icc_err_by_ctl$results[1,2])
icc_table_topx_err$ctl_lowCI <- c(icc_err_ax_ctl$results[1,7], icc_err_ay_ctl$results[1,7],  icc_err_bx_ctl$results[1,7], icc_err_by_ctl$results[1,7])
icc_table_topx_err$ctl_upCI <- c(icc_err_ax_ctl$results[1,8], icc_err_ay_ctl$results[1,8],  icc_err_bx_ctl$results[1,8], icc_err_by_ctl$results[1,8])
# icc_table_topx_err$ctl_p <- c(icc_err_ax_ctl$results[1,6], icc_err_ay_ctl$results[1,6],  icc_err_bx_ctl$results[1,6], icc_err_by_ctl$results[1,6])

# Round the values in the corr_table data frame to 4 decimal points
icc_table_topx_err$all_icc <- round(icc_table_topx_err$all_icc, 2)
icc_table_topx_err$all_lowCI <- round(icc_table_topx_err$all_lowCI, 2)
icc_table_topx_err$all_upCI <- round(icc_table_topx_err$all_upCI, 2)
# icc_table_topx_err$all_p <- round(icc_table_topx_err$all_p, 4)
icc_table_topx_err$pt_icc <- round(icc_table_topx_err$pt_icc, 2)
icc_table_topx_err$pt_lowCI <- round(icc_table_topx_err$pt_lowCI, 2)
icc_table_topx_err$pt_upCI <- round(icc_table_topx_err$pt_upCI, 2)
# icc_table_topx_err$pt_p <- round(icc_table_topx_err$pt_p, 4)
icc_table_topx_err$ctl_icc <- round(icc_table_topx_err$ctl_icc, 2)
icc_table_topx_err$ctl_lowCI <- round(icc_table_topx_err$ctl_lowCI, 2)
icc_table_topx_err$ctl_upCI <- round(icc_table_topx_err$ctl_upCI, 2)
# icc_table_topx_err$ctl_p <- round(icc_table_topx_err$ctl_p, 4)

# Print the data frame to verify
print(icc_table_topx_err)
```

###Plot: TOPX Error
```{r}
# Reshape into long format and drop "All"
icc_table_err_plot <- icc_table_topx_err %>%
  select(trial_type,
         All_icc = all_icc, All_low = all_lowCI, All_up = all_upCI,
         Pt_icc  = pt_icc,  Pt_low  = pt_lowCI,  Pt_up  = pt_upCI,
         Ctl_icc = ctl_icc, Ctl_low = ctl_lowCI, Ctl_up = ctl_upCI) %>%
  pivot_longer(
    cols = -trial_type,
    names_to = c("SubjGroup", ".value"),
    names_pattern = "(All|Pt|Ctl)_(icc|low|up)"
  ) %>%
  filter(SubjGroup != "All") %>%  # drop the "All" group
  mutate(
    icc_label = sprintf("%.2f", icc),
    ci_label  = sprintf("[%.2f, %.2f]", low, up),
    # icc_label = round(icc, 2),
    # ci_label  = paste0("[", round(low, 2), ", ", round(up, 2), "]"),
    # reverse row order manually
    trial_type = factor(trial_type, levels = rev(c("AX", "AY", "BX", "BY"))),
    # set text color based on ICC
    text_col = ifelse(!is.na(icc) & icc > 0.40, "white", "black"),
    # order Pt first
    SubjGroup = dplyr::recode(SubjGroup, "Pt" = "EP",
                              "Ctl" = "Ctl"),
    SubjGroup = factor(SubjGroup, levels = c("EP", "Ctl"))
  )

# Plot heatmap with reversed row order - one color
err_plot <- ggplot(icc_table_err_plot, aes(x = SubjGroup, y = trial_type, fill = icc)) +
  geom_tile(color = "white") +
  geom_text(aes(label = icc_label, color = text_col), size = 5, fontface = "bold", vjust = -0.2) +
  geom_text(aes(label = ci_label, color = text_col), size = 3.5, vjust = 1.2) +
  scale_fill_gradient(low = "white", high = "#610014",
                      limits = c(0, 1), name = "ICC") +
  scale_color_identity() +  # use the text_col values directly
  scale_x_discrete(position = "top") +
  theme_minimal(base_size = 14) +
  labs(x = "", y = "",
       title = "Error Rates") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(face = "bold", size = 14),
        axis.text.y = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14), 
        plot.title = element_text(face = "bold", size = 14, 
                                  hjust = 0.5,
                                  margin = margin(t = 0, r = 0, b = 5, l = 0)))
err_plot

# Save figure
ggsave(
  filename = paste0("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/graphs/test-retest/", 
                    format(Sys.Date(), "%Y%m%d"), "_TOPX_err_ICC.png"),
  plot = err_plot,
  bg = "white",
  width = 4.5,   # width in inches
  height = 3.5,  # height in inches
  dpi = 300    # high-resolution
)

plot_err_sep <- ggplot(dat_all_topx, 
                        aes(x= trial_type, y=error, group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Error Rates", 
       y = "Error Rate", 
       x = "Trial Type", 
       color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(0, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_sep
```

## TOPX RT: ICC
```{r}
icc_rt_ax_all <- calc_ICC_topx_all("AX", "rt_mdn")
icc_rt_ax_pt <- calc_ICC_topx("AX", "Patient", "rt_mdn") 
icc_rt_ax_ctl <- calc_ICC_topx("AX", "Control", "rt_mdn")

icc_rt_ay_all <- calc_ICC_topx_all("AY", "rt_mdn")
icc_rt_ay_pt <- calc_ICC_topx("AY", "Patient", "rt_mdn") 
icc_rt_ay_ctl <- calc_ICC_topx("AY", "Control", "rt_mdn") 

icc_rt_bx_all <- calc_ICC_topx_all("BX", "rt_mdn")
icc_rt_bx_pt <- calc_ICC_topx("BX", "Patient", "rt_mdn")
icc_rt_bx_ctl <- calc_ICC_topx("BX", "Control", "rt_mdn")

icc_rt_by_all <- calc_ICC_topx_all("BY", "rt_mdn")
icc_rt_by_pt <- calc_ICC_topx("BY", "Patient", "rt_mdn") 
icc_rt_by_ctl <- calc_ICC_topx("BY", "Control", "rt_mdn") 
```

#### Table: TOPX RT ICC Correlations/P-values
```{r, echo=F}
icc_table_topx_rt <- data.frame(
  trial_type = character(4),
  all_icc = character(4),
  all_lowCI = numeric(4),
  all_upCI = numeric(4),
  # all_p = numeric(4),
  pt_icc = character(4),
  pt_lowCI = numeric(4),
  pt_upCI = numeric(4),
  # pt_p = numeric(4),
  ctl_icc = numeric(4),
  ctl_lowCI = numeric(4),
  ctl_upCI = numeric(4),
  # ctl_p = numeric(4),
  stringsAsFactors = FALSE
)

# Fill in the "parameter" column with the specified values
icc_table_topx_rt$trial_type <- c("AX", "AY", "BX", "BY")

# whole sample ICCs
icc_table_topx_rt$all_icc <- c(icc_rt_ax_all$results[1,2], icc_rt_ay_all$results[1,2], icc_rt_bx_all$results[1,2], icc_rt_by_all$results[1,2])
icc_table_topx_rt$all_lowCI <- c(icc_rt_ax_all$results[1,7], icc_rt_ay_all$results[1,7],  icc_rt_bx_all$results[1,7], icc_rt_by_all$results[1,7])
icc_table_topx_rt$all_upCI <- c(icc_rt_ax_all$results[1,8], icc_rt_ay_all$results[1,8],  icc_rt_bx_all$results[1,8], icc_rt_by_all$results[1,8])
# # icc_table_topx_rt$all_p <- c(icc_rt_ax_all$results[1,6], icc_rt_ay_all$results[1,6], icc_rt_bx_all$results[1,6], icc_rt_by_all$results[1,6])

# patient ICCs
icc_table_topx_rt$pt_icc <- c(icc_rt_ax_pt$results[1,2], icc_rt_ay_pt$results[1,2], icc_rt_bx_pt$results[1,2], icc_rt_by_pt$results[1,2])
icc_table_topx_rt$pt_lowCI <- c(icc_rt_ax_pt$results[1,7], icc_rt_ay_pt$results[1,7], icc_rt_bx_pt$results[1,7], icc_rt_by_pt$results[1,7])
icc_table_topx_rt$pt_upCI <- c(icc_rt_ax_pt$results[1,8], icc_rt_ay_pt$results[1,8], icc_rt_bx_pt$results[1,8], icc_rt_by_pt$results[1,8])
# icc_table_topx_rt$pt_p <- c(icc_rt_ax_pt$results[1,6], icc_rt_ay_pt$results[1,6], icc_rt_bx_pt$results[1,6], icc_rt_by_pt$results[1,6])

# control ICCs
icc_table_topx_rt$ctl_icc <- c(icc_rt_ax_ctl$results[1,2], icc_rt_ay_ctl$results[1,2], icc_rt_bx_ctl$results[1,2], icc_rt_by_ctl$results[1,2])
icc_table_topx_rt$ctl_lowCI <- c(icc_rt_ax_ctl$results[1,7], icc_rt_ay_ctl$results[1,7],  icc_rt_bx_ctl$results[1,7], icc_rt_by_ctl$results[1,7])
icc_table_topx_rt$ctl_upCI <- c(icc_rt_ax_ctl$results[1,8], icc_rt_ay_ctl$results[1,8],  icc_rt_bx_ctl$results[1,8], icc_rt_by_ctl$results[1,8])
# icc_table_topx_rt$ctl_p <- c(icc_rt_ax_ctl$results[1,6], icc_rt_ay_ctl$results[1,6], icc_rt_bx_ctl$results[1,6], icc_rt_by_ctl$results[1,6])

# Round the values in the corr_table data frame to 4 decimal points
icc_table_topx_rt$all_icc <- round(icc_table_topx_rt$all_icc, 2)
icc_table_topx_rt$all_lowCI <- round(icc_table_topx_rt$all_lowCI, 2)
icc_table_topx_rt$all_upCI <- round(icc_table_topx_rt$all_upCI, 2)
# icc_table_topx_rt$all_p <- round(icc_table_topx_rt$all_p, 4)
icc_table_topx_rt$pt_icc <- round(icc_table_topx_rt$pt_icc, 2)
icc_table_topx_rt$pt_lowCI <- round(icc_table_topx_rt$pt_lowCI, 2)
icc_table_topx_rt$pt_upCI <- round(icc_table_topx_rt$pt_upCI, 2)
# icc_table_topx_rt$pt_p <- round(icc_table_topx_rt$pt_p, 4)
icc_table_topx_rt$ctl_icc <- round(icc_table_topx_rt$ctl_icc, 2)
icc_table_topx_rt$ctl_lowCI <- round(icc_table_topx_rt$ctl_lowCI, 2)
icc_table_topx_rt$ctl_upCI <- round(icc_table_topx_rt$ctl_upCI, 2)
# icc_table_topx_rt$ctl_p <- round(icc_table_topx_rt$ctl_p, 4)

# Print the data frame to verify
print(icc_table_topx_rt)
```

###Plot: TOPX RT
```{r}
# Reshape into long format and drop "All" (Reaction Times)
icc_table_rt_plot <- icc_table_topx_rt %>%
  select(trial_type,
         All_icc = all_icc, All_low = all_lowCI, All_up = all_upCI,
         Pt_icc  = pt_icc,  Pt_low  = pt_lowCI,  Pt_up  = pt_upCI,
         Ctl_icc = ctl_icc, Ctl_low = ctl_lowCI, Ctl_up = ctl_upCI) %>%
  pivot_longer(
    cols = -trial_type,
    names_to = c("SubjGroup", ".value"),
    names_pattern = "(All|Pt|Ctl)_(icc|low|up)"
  ) %>%
  filter(SubjGroup != "All") %>%  # drop the "All" group
  mutate(
    icc_label = sprintf("%.2f", icc),
    ci_label  = sprintf("[%.2f, %.2f]", low, up),
    # icc_label = round(icc, 2),
    # ci_label  = paste0("[", round(low, 2), ", ", round(up, 2), "]"),
    # reverse row order manually
    trial_type = factor(trial_type, levels = rev(c("AX", "AY", "BX", "BY"))),
    # set text color based on ICC
    text_col = ifelse(!is.na(icc) & icc > 0.35, "white", "black"),
    # rename Pt -> EP and order first
    SubjGroup = dplyr::recode(SubjGroup, "Pt" = "EP",
                       "Ctl" = "Ctl"),
    SubjGroup = factor(SubjGroup, levels = c("EP", "Ctl"))
  )

# Plot heatmap with reversed row order
rt_plot <- ggplot(icc_table_rt_plot, aes(x = SubjGroup, y = trial_type, fill = icc)) +
  geom_tile(color = "white") +
  geom_text(aes(label = icc_label, color = text_col), size = 5, fontface = "bold", vjust = -0.2) +
  geom_text(aes(label = ci_label, color = text_col), size = 3.5, vjust = 1.2) +
  scale_fill_gradient(low = "white", high = "#610014",
                      limits = c(0, 1), name = "ICC") +
  scale_color_identity() +
  scale_x_discrete(position = "top") +
  theme_minimal(base_size = 14) +
  labs(x = "", y = "",
       title = "Reaction Times") +  # updated title for RTs
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(face = "bold", size = 14),
        axis.text.y = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14), 
        plot.title = element_text(face = "bold", size = 14, 
                                  hjust = 0.5,
                                  margin = margin(t = 0, r = 0, b = 5, l = 0)))

# Save figure
ggsave(
  filename = paste0("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/graphs/test-retest/", 
                    format(Sys.Date(), "%Y%m%d"), "_TOPX_RT_ICC.png"),
  plot = rt_plot,
  bg = "white",
  width = 4.5,   # width in inches
  height = 3.5,  # height in inches
  dpi = 300    # high-resolution
)
rt_plot
```

## TOPX d' ICC
```{r}
# Filtering by AX to avoid duplicate rows, but d' is same for all trials
icc_d_con_all <- calc_ICC_topx_all("AX", "d_context")
icc_d_con_pt <- calc_ICC_topx("AX", "Patient", "d_context")
icc_d_con_ctl <- calc_ICC_topx("AX", "Control", "d_context")

icc_d_exp_all <- calc_ICC_topx_all("AX", "d_expect")
icc_d_exp_pt <- calc_ICC_topx("AX", "Patient", "d_expect")
icc_d_exp_ctl <- calc_ICC_topx("AX", "Control", "d_expect")
```

#### Table: TOPX d' ICC Correlations/P-values
```{r, echo=F}
icc_table_topx_d <- data.frame(
  d_type = character(2),
  all_icc = numeric(2),
  all_lowCI = numeric(2),
  all_upCI = numeric(2),
  # all_p = numeric(2),
  pt_icc = character(2),
  pt_lowCI = numeric(2),
  pt_upCI = numeric(2),
  # pt_p = numeric(2),
  ctl_icc = numeric(2),
  ctl_lowCI = numeric(2),
  ctl_upCI = numeric(2),
  # ctl_p = numeric(2),
  stringsAsFactors = FALSE
)

# Fill in the "parameter" column with the specified values
icc_table_topx_d$d_type <- c("d_context", "d_expect")

# all ICCs
icc_table_topx_d$all_icc <- c(icc_d_con_all$results[1,2], icc_d_exp_all$results[1,2])
icc_table_topx_d$all_lowCI <- c(icc_d_con_all$results[1,7], icc_d_exp_all$results[1,7])
icc_table_topx_d$all_upCI <- c(icc_d_con_all$results[1,8], icc_d_exp_all$results[1,8])
# icc_table_topx_d$all_p <- c(icc_d_con_all$results[1,6], icc_d_exp_all$results[1,6])

# patient ICCs
icc_table_topx_d$pt_icc <- c(icc_d_con_pt$results[1,2], icc_d_exp_pt$results[1,2])
icc_table_topx_d$pt_lowCI <- c(icc_d_con_pt$results[1,7], icc_d_exp_pt$results[1,7])
icc_table_topx_d$pt_upCI <- c(icc_d_con_pt$results[1,8], icc_d_exp_pt$results[1,8])
# icc_table_topx_d$pt_p <- c(icc_d_con_pt$results[1,6], icc_d_exp_pt$results[1,6])

# control ICCs
icc_table_topx_d$ctl_icc <- c(icc_d_con_ctl$results[1,2], icc_d_exp_ctl$results[1,2])
icc_table_topx_d$ctl_lowCI <- c(icc_d_con_ctl$results[1,7], icc_d_exp_ctl$results[1,7])
icc_table_topx_d$ctl_upCI <- c(icc_d_con_ctl$results[1,8], icc_d_exp_ctl$results[1,8])
# icc_table_topx_d$ctl_p <- c(icc_d_con_ctl$results[1,6],  icc_d_exp_ctl$results[1,6])

# Round the values in the corr_table data frame to 4 decimal points
icc_table_topx_d$all_icc <- round(icc_table_topx_d$all_icc, 2)
icc_table_topx_d$all_lowCI <- round(icc_table_topx_d$all_lowCI, 2)
icc_table_topx_d$all_upCI <- round(icc_table_topx_d$all_upCI, 2)
# # icc_table_topx_d$all_p <- round(icc_table_topx_d$all_p, 4)

icc_table_topx_d$pt_icc <- round(icc_table_topx_d$pt_icc, 2)
icc_table_topx_d$pt_lowCI <- round(icc_table_topx_d$pt_lowCI, 2)
icc_table_topx_d$pt_upCI <- round(icc_table_topx_d$pt_upCI, 2)
# icc_table_topx_d$pt_p <- round(icc_table_topx_d$pt_p, 4)

icc_table_topx_d$ctl_icc <- round(icc_table_topx_d$ctl_icc, 2)
icc_table_topx_d$ctl_lowCI <- round(icc_table_topx_d$ctl_lowCI, 2)
icc_table_topx_d$ctl_upCI <- round(icc_table_topx_d$ctl_upCI, 2)
# icc_table_topx_d$ctl_p <- round(icc_table_topx_d$ctl_p, 4)

# Print the data frame to verify
print(icc_table_topx_d)
```

###Plot: TOPX d'
```{r}
# Reshape into long format and drop "All"
icc_table_d_plot <- icc_table_topx_d %>%
  select(d_type,
         All_icc = all_icc, All_low = all_lowCI, All_up = all_upCI,
         Pt_icc  = pt_icc,  Pt_low  = pt_lowCI,  Pt_up  = pt_upCI,
         Ctl_icc = ctl_icc, Ctl_low = ctl_lowCI, Ctl_up = ctl_upCI) %>%
  pivot_longer(
    cols = -d_type,
    names_to = c("SubjGroup", ".value"),
    names_pattern = "(All|Pt|Ctl)_(icc|low|up)"
  ) %>%
  filter(SubjGroup != "All") %>%  # drop "All" column
  mutate(
    icc_label = sprintf("%.2f", icc),
    ci_label  = sprintf("[%.2f, %.2f]", low, up),
    # icc_label = round(icc, 2),
    # ci_label  = paste0("[", round(low, 2), ", ", round(up, 2), "]"),
    # factor for y-axis (two rows: d_context, d_expect)
    d_type = dplyr::recode(d_type, d_context = "d' context", d_expect = "d' expectancy"),
    d_type = factor(d_type, levels = rev(c("d' context", "d' expectancy"))),
    # set text color based on ICC
    text_col = ifelse(!is.na(icc) & icc > 0.35, "white", "black"),
    # rename Pt -> EP and order first
    SubjGroup = dplyr::recode(SubjGroup, "Pt" = "EP",
                              "Ctl" = "Ctl"),
    SubjGroup = factor(SubjGroup, levels = c("EP", "Ctl"))
  )

# Plot heatmap
d_plot <- ggplot(icc_table_d_plot, aes(x = SubjGroup, y = d_type, fill = icc)) +
  geom_tile(color = "white") +
  geom_text(aes(label = icc_label, color = text_col), size = 5, fontface = "bold", vjust = -0.2) +
  geom_text(aes(label = ci_label, color = text_col), size = 3.5, vjust = 1.2) +
  scale_fill_gradient(low = "white", high = "#610014",
                      limits = c(0, 1), name = "ICC") +
  scale_color_identity() +
  scale_x_discrete(position = "top") +
  labs(x = "", y = "",
       title = "D-prime Statistics") +
  theme_minimal(base_size = 14) +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(face = "bold", size = 14),
        axis.text.y = element_text(face = "bold", size = 14),
        axis.title.y = element_text(face = "bold", size = 14), 
        plot.title = element_text(face = "bold", size = 14, 
                                  hjust = 0.5,
                                  margin = margin(t = 0, r = 0, b = 5, l = 0)))

# Save figure
ggsave(
  filename = paste0("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/graphs/test-retest/", 
                    format(Sys.Date(), "%Y%m%d"), "_TOPX_dprime_ICC.png"),
  plot = d_plot,
  bg = "white",
  width = 5,   # width in inches
  height = 2.5,  # height in inches
  dpi = 300    # high-resolution
)
d_plot

```


# Read/reformat DDM data
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data <- function(block, types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/data/20241031_ddm_data/", block, "/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]]))
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = toupper(block), .after = participant_id)
}

# Column mappings for different file types
column_mappings <- list(
  v = c("participant_id", "v_ax", "v_ay", "v_bx", "v_by"),
  a = c("participant_id", "a_ax", "a_ay", "a_bx", "a_by"),
  t = c("participant_id", "t_ax", "t_ay", "t_bx", "t_by"),
  z = c("participant_id", "z_a", "z_b")
)

# Process data for each block
types <- names(column_mappings)
dat_bl1_ddm <- process_data("bl1", types, column_mappings)
dat_bl2_ddm <- process_data("bl2", types, column_mappings)

# Filter to retain only common participant_ids
common_ids <- intersect(dat_bl1_ddm$participant_id, dat_bl2_ddm$participant_id)
dat_bl1_ddm <- filter(dat_bl1_ddm, participant_id %in% common_ids)
dat_bl2_ddm <- filter(dat_bl2_ddm, participant_id %in% common_ids)

# Combine both datasets
dat_ddm_all <- bind_rows(dat_bl1_ddm, dat_bl2_ddm)

# Rename, pivot, and add `group` column
dat_ddm_all <- dat_ddm_all %>%
  rename(subj_idx = participant_id) %>%
  pivot_longer(
    cols = c(v_ax, v_ay, v_bx, v_by, a_ax, a_ay, a_bx, a_by, 
             t_ax, t_ay, t_bx, t_by, z_a, z_b),
    names_to = c("parameter", "cttype"), 
    names_sep = "_", 
    values_to = "mean"
  ) %>%
  mutate(
    group = case_when(
      str_sub(subj_idx, 1, 3) == "SP1" ~ "Control",
      str_sub(subj_idx, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ NA
    )
  )
```

## optional: filter dat behav by another dataset
```{r}
ddm_sample_subjx$subj_idx <- ddm_sample_subjx$subj
dat_ddm_all <- subset(dat_ddm_all, subj_idx %in% ddm_sample_subjx$subj_idx)

dat_bl1_ddm_rev <- filter(dat_ddm_all, visit == "BL1")
dat_bl2_ddm_rev <- filter(dat_ddm_all, visit == "BL2")
```

# DDM: ICC (Intraclass Correlation Coefficients)
```{r}
calc_ICC_ddm <- function(icc_parameter, icc_cttype, icc_group) {
  library(dplyr)
  library(psych)
  
  # subset v-BX baseline 1 data
  icc_dat_bl1 <- dat_bl1_ddm_rev %>% 
    filter(parameter == icc_parameter & cttype == icc_cttype) %>% 
    select(subj_idx, group, mean) %>% 
    rename(icc_bl1_mean = mean)

  # Filter and rename for v_BX_bl2
  icc_dat_bl2 <- dat_bl2_ddm_rev %>%
    filter(parameter == icc_parameter & cttype == icc_cttype) %>%
    select(subj_idx, group, mean) %>%
    rename(icc_bl2_mean = mean)
  
  # Combine v-BX baseline 1 and 2 data
  icc_dat_comb <- merge(icc_dat_bl1, icc_dat_bl2, 
                        by = c("subj_idx", "group"), all = TRUE)
  
  # Subset v-BX combined data for patients only
  icc_dat_comb_grp <- icc_dat_comb %>%
    filter(group == icc_group) %>%
    select(icc_bl1_mean, icc_bl2_mean)
  
  # Run ICC for patients
  # new as of 8/9/2024: set LMER = FALSE bc no missing data in DDM
  return(ICC(icc_dat_comb_grp, lmer = FALSE))
}

calc_ICC_ddm_all <- function(icc_parameter, icc_cttype) {
  library(dplyr)
  library(psych)
  
  # subset v-BX baseline 1 data
  icc_dat_bl1 <- dat_bl1_ddm_rev %>% 
    filter(parameter == icc_parameter & cttype == icc_cttype) %>% 
    select(subj_idx, mean) %>% 
    rename(icc_bl1_mean = mean)
  
  # Filter and rename for v_BX_bl2
  icc_dat_bl2 <- dat_bl2_ddm_rev %>%
    filter(parameter == icc_parameter & cttype == icc_cttype) %>%
    select(subj_idx, mean) %>%
    rename(icc_bl2_mean = mean)
  
  # Combine v-BX baseline 1 and 2 data
  icc_dat_comb <- merge(icc_dat_bl1, icc_dat_bl2, 
                        by = c("subj_idx"), all = TRUE)
  
  # Subset v-BX combined data for patients only
  icc_dat_comb <- icc_dat_comb %>%
    select(icc_bl1_mean, icc_bl2_mean)
  
  # Run ICC for patients
  # new as of 8/9/2024: set LMER = FALSE bc no missing data
  return(ICC(icc_dat_comb, lmer = FALSE))
}
```

### Drift Rates (ICC)
```{r, echo=F, results='hide'}
icc_v_ax_all <- calc_ICC_ddm_all("v", "ax")
icc_v_ax_pt <- calc_ICC_ddm("v", "ax", "Patient")
icc_v_ax_ctl <- calc_ICC_ddm("v", "ax", "Control")

icc_v_ay_all <- calc_ICC_ddm_all("v", "ay")
icc_v_ay_pt <- calc_ICC_ddm("v", "ay", "Patient")
icc_v_ay_ctl <- calc_ICC_ddm("v", "ay", "Control")

icc_v_bx_all <- calc_ICC_ddm_all("v", "bx")
icc_v_bx_pt <- calc_ICC_ddm("v", "bx", "Patient")
icc_v_bx_ctl <- calc_ICC_ddm("v", "bx", "Control")

icc_v_by_all <- calc_ICC_ddm_all("v", "by")
icc_v_by_pt <- calc_ICC_ddm("v", "by", "Patient")
icc_v_by_ctl <- calc_ICC_ddm("v", "by", "Control")
```

### Decision Thresholds (ICC)
```{r, echo=F, results='hide'}
icc_a_ax_all <- calc_ICC_ddm_all("a", "ax")
icc_a_ax_pt <- calc_ICC_ddm("a", "ax", "Patient")
icc_a_ax_ctl <- calc_ICC_ddm("a", "ax", "Control")

icc_a_ay_all <- calc_ICC_ddm_all("a", "ay")
icc_a_ay_pt <- calc_ICC_ddm("a", "ay", "Patient")
icc_a_ay_ctl <- calc_ICC_ddm("a", "ay", "Control")

icc_a_bx_all <- calc_ICC_ddm_all("a", "bx")
icc_a_bx_pt <- calc_ICC_ddm("a", "bx", "Patient")
icc_a_bx_ctl <- calc_ICC_ddm("a", "bx", "Control")

icc_a_by_all <- calc_ICC_ddm_all("a", "by")
icc_a_by_pt <- calc_ICC_ddm("a", "by", "Patient")
icc_a_by_ctl <- calc_ICC_ddm("a", "by", "Control")
```

### Non-Decision Times (ICC)
```{r, echo=F, results='hide'}
icc_t_ax_all <- calc_ICC_ddm_all("t", "ax")
icc_t_ax_pt <- calc_ICC_ddm("t", "ax", "Patient")
icc_t_ax_ctl <- calc_ICC_ddm("t", "ax", "Control")

icc_t_ay_all <- calc_ICC_ddm_all("t", "ay")
icc_t_ay_pt <- calc_ICC_ddm("t", "ay", "Patient")
icc_t_ay_ctl <- calc_ICC_ddm("t", "ay", "Control")

icc_t_bx_all <- calc_ICC_ddm_all("t", "bx")
icc_t_bx_pt <- calc_ICC_ddm("t", "bx", "Patient")
icc_t_bx_ctl <- calc_ICC_ddm("t", "bx", "Control")

icc_t_by_all <- calc_ICC_ddm_all("t", "by")
icc_t_by_pt <- calc_ICC_ddm("t", "by", "Patient")
icc_t_by_ctl <- calc_ICC_ddm("t", "by", "Control")
```

### Bias (ICC)
```{r, echo=F, results='hide'}
icc_z_a_all <- calc_ICC_ddm_all("z", "a")
icc_z_a_ctl <- calc_ICC_ddm("z", "a", "Control")
icc_z_a_pt <- calc_ICC_ddm("z", "a", "Patient")

icc_z_b_all <- calc_ICC_ddm_all("z", "b")
icc_z_b_ctl <- calc_ICC_ddm("z", "b", "Control")
icc_z_b_pt <- calc_ICC_ddm("z", "b", "Patient")
```

### Table: DDM ICC Correlations/P-values
```{r, echo=F}
icc_table <- data.frame(
  parameter = character(14),
  cttype = character(14),
  all_icc = numeric(14),
  all_lowCI = numeric(14),
  all_upCI = numeric(14),
  # all_p = numeric(14),
  pt_icc = numeric(14),
  pt_lowCI = numeric(14),
  pt_upCI = numeric(14),
  # pt_p = numeric(14),
  ctl_icc = numeric(14),
  ctl_lowCI = numeric(14),
  ctl_upCI = numeric(14),
  # ctl_p = numeric(14),
  stringsAsFactors = FALSE
)

# Fill in the "parameter" column with the specified values
icc_table$parameter <- c(rep("v", 4), rep("a", 4), rep("t", 4), rep("z", 2))

icc_table$cttype <- c(rep(c("AX", "AY", "BX", "BY"), 3), "A", "B")

# whole sample ICC
icc_table$all_icc <- c(icc_v_ax_all$results[1,2], icc_v_ay_all$results[1,2],
                           icc_v_bx_all$results[1,2], icc_v_by_all$results[1,2],
                           icc_a_ax_all$results[1,2], icc_a_ay_all$results[1,2],
                           icc_a_bx_all$results[1,2], icc_a_by_all$results[1,2],
                           icc_t_ax_all$results[1,2], icc_t_ay_all$results[1,2],
                           icc_t_bx_all$results[1,2], icc_t_by_all$results[1,2],
                           icc_z_a_all$results[1,2], icc_z_b_all$results[1,2])

# 
icc_table$all_lowCI <- c(icc_v_ax_all$results[1,7], icc_v_ay_all$results[1,7],
                           icc_v_bx_all$results[1,7], icc_v_by_all$results[1,7],
                           icc_a_ax_all$results[1,7], icc_a_ay_all$results[1,7],
                           icc_a_bx_all$results[1,7], icc_a_by_all$results[1,7],
                           icc_t_ax_all$results[1,7], icc_t_ay_all$results[1,7],
                           icc_t_bx_all$results[1,7], icc_t_by_all$results[1,7],
                           icc_z_a_all$results[1,7], icc_z_b_all$results[1,7])
# 
icc_table$all_upCI <- c(icc_v_ax_all$results[1,8], icc_v_ay_all$results[1,8],
                           icc_v_bx_all$results[1,8], icc_v_by_all$results[1,8],
                           icc_a_ax_all$results[1,8], icc_a_ay_all$results[1,8],
                           icc_a_bx_all$results[1,8], icc_a_by_all$results[1,8],
                           icc_t_ax_all$results[1,8], icc_t_ay_all$results[1,8],
                           icc_t_bx_all$results[1,8], icc_t_by_all$results[1,8],
                           icc_z_a_all$results[1,8], icc_z_b_all$results[1,8])
# 
# icc_table$all_p <- c(icc_v_ax_all$results[1,6], icc_v_ay_all$results[1,6], 
#                            icc_v_bx_all$results[1,6], icc_v_by_all$results[1,6],
#                            icc_a_ax_all$results[1,6], icc_a_ay_all$results[1,6], 
#                            icc_a_bx_all$results[1,6], icc_a_by_all$results[1,6],
#                            icc_t_ax_all$results[1,6], icc_t_ay_all$results[1,6], 
#                            icc_t_bx_all$results[1,6], icc_t_by_all$results[1,6],
#                            icc_z_a_all$results[1,6], icc_z_b_all$results[1,6])

# patient ICCs
icc_table$pt_icc <- c(icc_v_ax_pt$results[1,2], icc_v_ay_pt$results[1,2], 
                           icc_v_bx_pt$results[1,2], icc_v_by_pt$results[1,2],
                           icc_a_ax_pt$results[1,2], icc_a_ay_pt$results[1,2], 
                           icc_a_bx_pt$results[1,2], icc_a_by_pt$results[1,2],
                           icc_t_ax_pt$results[1,2], icc_t_ay_pt$results[1,2], 
                           icc_t_bx_pt$results[1,2], icc_t_by_pt$results[1,2],
                           icc_z_a_pt$results[1,2], icc_z_b_pt$results[1,2])

icc_table$pt_lowCI <- c(icc_v_ax_pt$results[1,7], icc_v_ay_pt$results[1,7], 
                           icc_v_bx_pt$results[1,7], icc_v_by_pt$results[1,7],
                           icc_a_ax_pt$results[1,7], icc_a_ay_pt$results[1,7], 
                           icc_a_bx_pt$results[1,7], icc_a_by_pt$results[1,7],
                           icc_t_ax_pt$results[1,7], icc_t_ay_pt$results[1,7], 
                           icc_t_bx_pt$results[1,7], icc_t_by_pt$results[1,7],
                           icc_z_a_pt$results[1,7], icc_z_b_pt$results[1,7])

icc_table$pt_upCI <- c(icc_v_ax_pt$results[1,8], icc_v_ay_pt$results[1,8], 
                           icc_v_bx_pt$results[1,8], icc_v_by_pt$results[1,8],
                           icc_a_ax_pt$results[1,8], icc_a_ay_pt$results[1,8], 
                           icc_a_bx_pt$results[1,8], icc_a_by_pt$results[1,8],
                           icc_t_ax_pt$results[1,8], icc_t_ay_pt$results[1,8], 
                           icc_t_bx_pt$results[1,8], icc_t_by_pt$results[1,8],
                           icc_z_a_pt$results[1,8], icc_z_b_pt$results[1,8])

# icc_table$pt_p <- c(icc_v_ax_pt$results[1,6], icc_v_ay_pt$results[1,6], 
#                            icc_v_bx_pt$results[1,6], icc_v_by_pt$results[1,6],
#                            icc_a_ax_pt$results[1,6], icc_a_ay_pt$results[1,6], 
#                            icc_a_bx_pt$results[1,6], icc_a_by_pt$results[1,6],
#                            icc_t_ax_pt$results[1,6], icc_t_ay_pt$results[1,6], 
#                            icc_t_bx_pt$results[1,6], icc_t_by_pt$results[1,6],
#                            icc_z_a_pt$results[1,6], icc_z_b_pt$results[1,6])

# control ICCs
icc_table$ctl_icc <- c(icc_v_ax_ctl$results[1,2], icc_v_ay_ctl$results[1,2], 
                           icc_v_bx_ctl$results[1,2], icc_v_by_ctl$results[1,2],
                           icc_a_ax_ctl$results[1,2], icc_a_ay_ctl$results[1,2], 
                           icc_a_bx_ctl$results[1,2], icc_a_by_ctl$results[1,2],
                           icc_t_ax_ctl$results[1,2], icc_t_ay_ctl$results[1,2], 
                           icc_t_bx_ctl$results[1,2], icc_t_by_ctl$results[1,2],
                           icc_z_a_ctl$results[1,2], icc_z_b_ctl$results[1,2])

icc_table$ctl_lowCI <- c(icc_v_ax_ctl$results[1,7], icc_v_ay_ctl$results[1,7], 
                           icc_v_bx_ctl$results[1,7], icc_v_by_ctl$results[1,7],
                           icc_a_ax_ctl$results[1,7], icc_a_ay_ctl$results[1,7], 
                           icc_a_bx_ctl$results[1,7], icc_a_by_ctl$results[1,7],
                           icc_t_ax_ctl$results[1,7], icc_t_ay_ctl$results[1,7], 
                           icc_t_bx_ctl$results[1,7], icc_t_by_ctl$results[1,7],
                           icc_z_a_ctl$results[1,7], icc_z_b_ctl$results[1,7])

icc_table$ctl_upCI <- c(icc_v_ax_ctl$results[1,8], icc_v_ay_ctl$results[1,8], 
                           icc_v_bx_ctl$results[1,8], icc_v_by_ctl$results[1,8],
                           icc_a_ax_ctl$results[1,8], icc_a_ay_ctl$results[1,8], 
                           icc_a_bx_ctl$results[1,8], icc_a_by_ctl$results[1,8],
                           icc_t_ax_ctl$results[1,8], icc_t_ay_ctl$results[1,8], 
                           icc_t_bx_ctl$results[1,8], icc_t_by_ctl$results[1,8],
                           icc_z_a_ctl$results[1,8], icc_z_b_ctl$results[1,8])

# icc_table$ctl_p <- c(icc_v_ax_ctl$results[1,6], icc_v_ay_ctl$results[1,6], 
#                            icc_v_bx_ctl$results[1,6], icc_v_by_ctl$results[1,6],
#                            icc_a_ax_ctl$results[1,6], icc_a_ay_ctl$results[1,6], 
#                            icc_a_bx_ctl$results[1,6], icc_a_by_ctl$results[1,6],
#                            icc_t_ax_ctl$results[1,6], icc_t_ay_ctl$results[1,6], 
#                            icc_t_bx_ctl$results[1,6], icc_t_by_ctl$results[1,6],
#                            icc_z_a_ctl$results[1,6], icc_z_b_ctl$results[1,6])

# Round the values in the corr_table data frame to 4 decimal points
icc_table$all_icc <- round(icc_table$all_icc, 2)
icc_table$all_lowCI <- round(icc_table$all_lowCI, 2)
icc_table$all_upCI <- round(icc_table$all_upCI, 2)
# icc_table$all_p <- round(icc_table$all_p, 4)

icc_table$pt_icc <- round(icc_table$pt_icc, 2)
icc_table$pt_lowCI <- round(icc_table$pt_lowCI, 2)
icc_table$pt_upCI <- round(icc_table$pt_upCI, 2)
# icc_table$pt_p <- round(icc_table$pt_p, 4)

icc_table$ctl_icc <- round(icc_table$ctl_icc, 2)
icc_table$ctl_lowCI <- round(icc_table$ctl_lowCI, 2)
icc_table$ctl_upCI <- round(icc_table$ctl_upCI, 2)
# icc_table$ctl_p <- round(icc_table$ctl_p, 4)

# Print the data frame to verify
print(icc_table)
```


### Plot: DDM icc 1x1
```{r}
# Reshape into long format for DDM ICCs
# Combine parameter + cttype to make full variable names
icc_table_ddm_plot <- icc_table %>%
  mutate(var_label = case_when(
    parameter %in% c("v","a","t") ~ paste0(parameter, "_", cttype),
    parameter == "z" ~ paste0(parameter, "_", cttype)
  )) %>%
  select(var_label,
         All_icc = all_icc, All_low = all_lowCI, All_up = all_upCI,
         Pt_icc  = pt_icc,  Pt_low  = pt_lowCI,  Pt_up = pt_upCI,
         Ctl_icc = ctl_icc, Ctl_low = ctl_lowCI, Ctl_up = ctl_upCI) %>%
  pivot_longer(
    cols = -var_label,
    names_to = c("SubjGroup", ".value"),
    names_pattern = "(All|Pt|Ctl)_(icc|low|up)"
  ) %>%
  mutate(
    icc_label = sprintf("%.2f", icc),
    ci_label  = sprintf("[%.2f, %.2f]", low, up),
    # icc_label = round(icc, 2),
    # ci_label  = paste0("(", round(low, 2), "–", round(up, 2), ")"),
    var_label = factor(var_label, levels = rev(c("v_AX","v_AY","v_BX","v_BY",
                                                 "a_AX","a_AY","a_BX","a_BY",
                                                 "t_AX","t_AY","t_BX","t_BY",
                                                 "z_A","z_B")))
  )

# Add a column for text color based on icc
icc_table_ddm_plot <- icc_table_ddm_plot %>%
  mutate(text_col = ifelse(icc > 0.2, "white", "gray22"))

# Plot heatmap for DDM ICCs
ddm_plot <- ggplot(icc_table_ddm_plot, aes(x = SubjGroup, y = var_label, fill = icc)) +
  geom_tile(color = "white") +
  geom_text(aes(label = icc_label, color = text_col), size = 5, fontface = "bold", vjust = -0.35) +
  geom_text(aes(label = ci_label, color = text_col), size = 3.3, vjust = 0.9) +
  scale_fill_gradient(low = "white", high = "darkblue", limits = c(-0.1, 1), name = "ICC") +
  scale_color_identity() +   # use the text_col values directly
  scale_x_discrete(position = "top") +
  theme_minimal(base_size = 14) +
  labs(x = "", y = "", title = "DDM Parameter ICCs (95% CIs)") +
  theme(panel.grid = element_blank(),
        axis.text.x = element_text(face = "bold"),
        axis.text.y = element_text(face = "bold"))

# Save the heatmap as PNG with white background
ggsave(
  filename = paste0("~/Documents/umn_work/analyses/topx_analyses/topx_ddm/graphs/test-retest/", 
                    format(Sys.Date(), "%Y%m%d"), "_DDM_ICC.png"),
  plot = ddm_plot,
  bg = "white",
  width = 8,
  height = 10,
  dpi = 300
)
ddm_plot
```

###Plot: DDM icc 2x2
```{r}
# --- Reshape ICC table ---
icc_table_ddm_long <- icc_table %>%
  pivot_longer(
    cols = c(pt_icc, ctl_icc, all_icc,
             pt_lowCI, ctl_lowCI, all_lowCI,
             pt_upCI, ctl_upCI, all_upCI),
    names_to = c("Group", ".value"),
    names_pattern = "(pt|ctl|all)_(icc|lowCI|upCI)"
  )

# --- Clean table ---
icc_table_ddm_plot <- icc_table_ddm_long %>%
  # drop "all"
  filter(Group != "all") %>%
  # Pt first, then Ctl
  mutate(Group = factor(Group, levels = c("pt", "ctl"),
                        labels = c("EP", "Ctl"))) %>%
  # formatted labels for plotting
  mutate(
    icc_label = ifelse(is.na(icc), "", sprintf("%.2f", icc)),
    ci_label  = ifelse(is.na(lowCI) | is.na(upCI), "",
                       paste0("[", sprintf("%.2f", lowCI), ", ", sprintf("%.2f", upCI), "]")),
    text_col  = ifelse(!is.na(icc) & icc > 0.35, "white", "black")
  )

# --- Titles for each parameter ---
param_titles <- c(
  v = "Drift Rate",
  a = "Decision Threshold",
  t = "Non-decision Time",
  z = "Bias"
)

# --- Plot function ---
make_ddm_plot <- function(param_prefix) {
  df <- icc_table_ddm_plot %>% filter(parameter == param_prefix)
  
  # figure out which conditions are present in this parameter
  present_ct <- sort(unique(df$cttype))
  if (all(c("AX","AY","BX","BY") %in% present_ct)) {
    cond_levels <- c("AX","AY","BX","BY")
  } else if (all(c("A","B") %in% present_ct)) {
    cond_levels <- c("A","B")
  } else {
    cond_levels <- present_ct
  }
  
  df <- df %>%
    mutate(cond_label = factor(cttype, levels = rev(cond_levels)))  # rev() = top-down order
  
  ggplot(df, aes(x = Group, y = cond_label, fill = icc)) +
    geom_tile(color = "white") +
    geom_text(aes(label = icc_label, color = text_col),
              size = 5, fontface = "bold", vjust = -0.35) +
    geom_text(aes(label = ci_label, color = text_col),
              size = 3.2, vjust = 0.9) +
    scale_fill_gradient(low = "white", high = "#610014",
                        limits = c(-0.1, 1), name = "ICC") +
    scale_color_identity() +
    scale_x_discrete(position = "top") +
    labs(x = "", y = "", title = param_titles[[param_prefix]]) +
    theme_minimal(base_size = 14) +
    theme(
      panel.grid = element_blank(),
      plot.title = element_text(hjust = 0.5, face = "bold", size = 14,
      margin = margin(t = 0, r = 0, b = 4, l = 0)),
      # bring title closer
      plot.title.position = "plot", 
    # title just above panel
      axis.text.x = element_text(face = "bold", size = 14),
      axis.text.y = element_text(face = "bold", size = 14)
    )
  
}

# --- Build four parameter plots ---
plot_v <- make_ddm_plot("v")
plot_a <- make_ddm_plot("a")
plot_t <- make_ddm_plot("t")
plot_z <- make_ddm_plot("z")

# --- Combine with patchwork ---
combined_plot <- (plot_v | plot_a) / (plot_t | plot_z)

# --- Show & Save ---
print(combined_plot)

ggsave(
  filename = "~/Documents/umn_work/analyses/topx_analyses/topx_ddm/graphs/test-retest/DDM_ICC_matrix.png",
  plot = combined_plot,
  width = 8.5, height = 7, dpi = 300, bg = "white"
)
```

