---
title: "TOPX DDM Regressions"
author: "Jessica Arend"
date:  "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

# prep data
## clear space & load packages
```{r}
# clear workspace
rm(list=ls())

# read in packages
pacman::p_load(stats, stringr, dplyr, tidyr, ggplot2, ggpubr, emmeans, lme4, lmerTest, Matrix, pbkrtest, psych, car, performance, parameters, xgboost, SHAPforxgboost, stats, corrplot, MuMIn) 
```

## load DDM data
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data <- function(block, types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_ddm/data/20241031_ddm_data/", block, "/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]]))
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = toupper(block), .after = participant_id)
}

# Column mappings for different file types
column_mappings <- list(
  v = c("participant_id", "v_ax", "v_ay", "v_bx", "v_by"),
  a = c("participant_id", "a_ax", "a_ay", "a_bx", "a_by"),
  t = c("participant_id", "t_ax", "t_ay", "t_bx", "t_by"),
  z = c("participant_id", "z_a", "z_b")
)

# Process data for each block
types <- names(column_mappings)
dat_ddm_bl1 <- process_data("bl1", types, column_mappings)
dat_ddm_bl2 <- process_data("bl2", types, column_mappings)

# Filter to retain only common participant_ids
common_ids <- intersect(dat_ddm_bl1$participant_id, dat_ddm_bl2$participant_id)
dat_ddm_bl1 <- filter(dat_ddm_bl1, participant_id %in% common_ids)
dat_ddm_bl2 <- filter(dat_ddm_bl2, participant_id %in% common_ids)

# Combine both datasets
dat_ddm_all <- bind_rows(dat_ddm_bl1, dat_ddm_bl2)

# save long format for later, before pivoting wider
dat_ddm_all_long <- dat_ddm_all

# Rename, pivot, and add `subj_type` column
dat_ddm_all <- dat_ddm_all %>%
  rename(subj_idx = participant_id) %>%
  pivot_longer(
    cols = c(v_ax, v_ay, v_bx, v_by, a_ax, a_ay, a_bx, a_by, 
             t_ax, t_ay, t_bx, t_by, z_a, z_b),
    names_to = c("parameter", "cttype"), 
    names_sep = "_", 
    values_to = "mean"
  ) %>%
  mutate(
    group = case_when(
      str_sub(subj_idx, 1, 3) == "SP1" ~ "Control",
      str_sub(subj_idx, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ NA
    )
  )

# rename trials
dat_ddm_all <- dat_ddm_all %>% 
  mutate(cttype = case_when(cttype == "ax" ~ "AX",
                             cttype == "ay" ~ "AY",
                             cttype == "bx" ~ "BX", 
                             cttype == "by" ~ "BY",
                             cttype == "a" ~ "A",
                             cttype == "b" ~ "B",
                             TRUE ~ cttype))

# dat_ddm_all <- filter(dat_ddm_all, subj_idx != "SP1051")
dat_ddm_bl1 <- filter(dat_ddm_all, visit == "BL1")
dat_ddm_bl2 <- filter(dat_ddm_all, visit == "BL2")
```

## save list of subj
```{r}
# save list of DDM subject IDs
# write.csv( data.frame(subj = unique(dat_ddm_all$subj_idx)), file = file.path("data", paste0("topx_ddm_sample_subjx_", format(Sys.Date(), "%Y%m%d"), ".csv")), row.names = FALSE)
```

## load TOPX data
```{r}
### TOPX data ----------
dat_topx <- read.csv("../topx_clean/aggregate_data/aggregate_topx_20250125.csv")

# clean and rename
dat_topx[dat_topx == "BL1.5"] <- "BL1"
dat_topx[dat_topx == "BL2.5"] <- "BL2"
dat_topx[dat_topx == "6M.5"] <- "6M"
dat_topx[dat_topx == "7M.5"] <- "7M"
dat_topx[dat_topx == "12M.5"] <- "12M"

dat_topx <- dat_topx %>%
  rename(subj_idx = subj) %>% 
  rename(group = subj_type) %>% 
  rename(cttype = trial_type)

## Baseline 1
dat_topx_bl1 <- dat_topx %>% 
  filter(visit == "BL1") 

## Baseline 2
dat_topx_bl2 <- dat_topx %>% 
  filter(visit == "BL2") 

## 6-Month
dat_6m_topx <- dat_topx %>% 
  filter(visit == "6M") 

## match BL1 to BL2 TOPX 
dat_topx_bl1 <- subset(dat_topx_bl1, (subj_idx %in% dat_topx_bl2$subj_idx))
dat_topx_bl2 <- subset(dat_topx_bl2, (subj_idx %in% dat_topx_bl1$subj_idx))

## merge TOPX data
dat_topx_all <- rbind(dat_topx_bl1, dat_topx_bl2)

# remove TOPX data if not in DDM
dat_topx_all <- subset(dat_topx_all, (subj_idx %in% dat_ddm_all$subj_idx))
```

## load behav data
```{r}
dat_behav <- read.csv("data/step_behav_dat_for_ddm_20250317.csv")
colnames(dat_behav)[1] <- "subj_idx"

dat_behav <- dat_behav %>%
  mutate(age_split = ifelse(age >= median(age, , na.rm = TRUE), 1, 0),  .after = age) %>% 
  mutate(age_split = as.numeric(age_split))

table(dat_behav$age_split)
median(dat_behav$age)

dat_behav %>%
  group_by(age_split) %>%
  summarize(age = mean(age, na.rm = TRUE))
```

## combine + subset data
```{r}
# Merge TOPX + behav data --------
dat_topx_behav = merge(dat_topx_all, dat_behav, by = c("subj_idx","group"), all.x = TRUE)
dat_topx_behav_bl1 = merge(dat_topx_bl1, dat_behav, by = c("subj_idx","group"), all.x = TRUE)
dat_topx_behav_bl2 = merge(dat_topx_bl2, dat_behav, by = c("subj_idx","group"), all.x = TRUE)

# Merge DDM + behav data --------
dat_ddm_behav = merge(dat_ddm_all, dat_behav, by = c("subj_idx","group"), all.x = TRUE)
dat_ddm_behav_bl1 = merge(dat_ddm_bl1, dat_behav, by = c("subj_idx","group"), all.x = TRUE)
dat_ddm_behav_bl2 = merge(dat_ddm_bl2, dat_behav, by = c("subj_idx","group"), all.x = TRUE)

# subset DDM data by visit/parameter, for later use ------------------
# DDM by parameter for BL1 + BL2  ---------------------
v_dat_all = filter(dat_ddm_behav, parameter == 'v')
a_dat_all = filter(dat_ddm_behav, parameter == 'a')
t_dat_all = filter(dat_ddm_behav, parameter == 't')
z_dat_all = filter(dat_ddm_behav, parameter == 'z') 

# DDM by parameter for BL1 ---------------------
v_dat_bl1 = filter(dat_ddm_behav_bl1, parameter == 'v')
a_dat_bl1 = filter(dat_ddm_behav_bl1, parameter == 'a')
t_dat_bl1 = filter(dat_ddm_behav_bl1, parameter == 't')
z_dat_bl1 = filter(dat_ddm_behav_bl1, parameter == 'z') 

# DDM by parameter for BL2 ---------------------
v_dat_bl2 = filter(dat_ddm_behav_bl2, parameter == 'v')
a_dat_bl2 = filter(dat_ddm_behav_bl2, parameter == 'a')
t_dat_bl2 = filter(dat_ddm_behav_bl2, parameter == 't')
z_dat_bl2 = filter(dat_ddm_behav_bl2, parameter == 'z') 
```

# OBSERVED ANALYSES

## calculate d'
```{r}
## create df with  1 row/set of d-primes per subj, picked AX at random. And create numeric value for subj type
dat_dprime_all <- dat_topx_behav %>% 
  filter(cttype == "AX") %>% 
  mutate(group_n = ifelse(group=="Control", 0, 1))

# create long form of data - needed for graphs
dat_dprime_all_long <- dat_dprime_all %>% 
  select(subj_idx, visit, group, d_context, d_expect, age, gender) %>% 
  pivot_longer(
    cols = c(d_context, d_expect),
    names_to = "dprime_type",
    values_to = "dprime")

# create dataframes with only BL1/only BL2 dat - long
dat_dprime_bl1_long <- dat_dprime_all_long %>%
  filter(visit == "BL1")
dat_dprime_bl2_long <- dat_dprime_all_long %>%
  filter(visit == "BL2")

```



## visualize density/distribution
```{r}
plot_dist_behav <- function(dat, var) {
  plot <- ggplot(dat, aes(x = var, group = cttype, fill = cttype)) +
  geom_density(adjust = 1.5, alpha = 0.4) +
  facet_wrap(~ interaction(group, visit))
  print(plot)
}

plot_dist_behav(dat_topx_behav, )
plot_dist_behav(dat_topx_behav, )
plot_dist_behav(dat_topx_behav, )
plot_dist_behav(dat_topx_behav, )

normality_test <- function(dat) {
  results <- dat %>% 
    group_by(group, visit, cttype) %>%
    summarise(p_value = tryCatch(round(shapiro.test(mean)$p.value, 3), 
                                 error = function(e) NA), .groups = "drop")
  print(results)
}

normality_test(v_dat_all)
normality_test(a_dat_all)
normality_test(t_dat_all)
normality_test(z_dat_all)

```

## BL1 -----------------------
### error
```{r}
# plot error BL1
plot_err_bl1 <- ggplot(dat_topx_bl1, 
                        aes(x= cttype, y=error, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group), linewidth = 1.5) +
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Error Rates at Visit 1", 
       y = "Error Rate", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.05, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_bl1
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Error_BL1.png"),
#        plot_err_bl1, width = 6, height = 4)

### LMER error BL1
mod_err_bl1 <- lmer(error ~ group * cttype + age + (1|subj_idx), data = dat_topx_behav_bl1)
anova(mod_err_bl1, type = 3)
summary(mod_err_bl1)
r.squaredGLMM(mod_err_bl1)
print(emmeans(mod_err_bl1, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_err_bl1, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_err_bl1, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_err_bl1, list(pairwise ~ cttype|group), adjust = "mvt"))
check_model(mod_err_bl1)
```

###d'
```{r}
# plot d' BL1
plot_dprime_bl1 <- ggplot(dat_dprime_bl1_long, 
                          aes(x= dprime_type, y=dprime, 
                              group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group),
               linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               width = 0.05, size = 1) + 
  labs(title = "D-prime (d') at Visit 1", 
       y = "d' Value", 
       x = "d' Type", color = "Group") +
  coord_cartesian(ylim = c(2.0, 3.5)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_x_discrete(labels = c("d_context" = "d' Context", 
                              "d_expect" = "d' Expectancy")) +
  scale_y_continuous(breaks = c(seq(2.0, 3.5, by = 0.25)),
                     labels = c("2.0","", "2.5", "", "3.0", "", "3.5")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_dprime_bl1
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Dprime_BL1.png"),
#        plot_dprime_bl1, width = 6, height = 4)

#### LMER d' BL1 -----
mod_d_bl1 <- lmer(dprime ~ group * dprime_type + age + (1|subj_idx), data = dat_dprime_bl1_long)
anova(mod_d_bl1, type = 3)
summary(mod_d_bl1)
r.squaredGLMM(mod_d_bl1)
print(emmeans(mod_d_bl1, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_d_bl1, list(pairwise ~ dprime_type), adjust = "mvt"))
print(emmeans(mod_d_bl1, list(pairwise ~ group|dprime_type), adjust = "mvt"))
print(emmeans(mod_d_bl1, list(pairwise ~ dprime_type|group), adjust = "mvt"))
check_model(mod_d_bl1)
```

### RT
```{r}
# plot RT BL1
plot_rt_bl1 <- ggplot(dat_topx_bl1, 
                       aes(x= cttype, y=rt_mdn, group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Reaction Times (RT) at Visit 1", 
       y = "Median Correct RT (ms)", 
       x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_bl1
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_RT_BL1.png"),
#        plot_rt_bl1, width = 6, height = 4)

### LMER RT BL1 
mod_rt_bl1 <- lmer(rt_mdn ~ group * cttype + age + (1|subj_idx), data = dat_topx_behav_bl1)
anova(mod_rt_bl1, type = 3)
summary(mod_rt_bl1)
r.squaredGLMM(mod_rt_bl1)
print(emmeans(mod_rt_bl1, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_rt_bl1, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rt_bl1, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_rt_bl1, list(pairwise ~ cttype|group), adjust = "mvt"))
check_model(mod_rt_bl1)
```

## BL2 -----------------------
### error
```{r}
# plot error BL2
plot_err_bl2 <- ggplot(dat_topx_bl2, 
                        aes(x= cttype, y=error, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group), linewidth = 1.5) +
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Error Rates at Visit 2", 
       y = "Error Rate", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.05, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_bl2
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Error_BL2.png"),
#        plot_err_bl2, width = 6, height = 4)

### LMER Error BL2
mod_err_bl2 <- lmer(error ~ group * cttype + age + (1|subj_idx), data = dat_topx_behav_bl2)
anova(mod_err_bl2, type = 3)
summary(mod_err_bl2)
r.squaredGLMM(mod_err_bl2)
print(emmeans(mod_err_bl2, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_err_bl2, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_err_bl2, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_err_bl2, list(pairwise ~ cttype|group), adjust = "mvt"))
check_model(mod_err_bl2)
```

### d'
```{r}
# plot d' BL2
plot_dprime_bl2 <- ggplot(dat_dprime_bl2_long, 
                          aes(x= dprime_type, y=dprime, 
                              group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group),
               linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               width = 0.05, size = 1) + 
  labs(title = "D-prime (d') at Visit 2", 
       y = "d' Value", 
       x = "d' Type", color = "Group") +
  coord_cartesian(ylim = c(2.0, 3.5)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_x_discrete(labels = c("d_context" = "d' Context", 
                              "d_expect" = "d' Expectancy")) +
  scale_y_continuous(breaks = c(seq(2.0, 3.5, by = 0.25)),
                     labels = c("2.0","", "2.5", "", "3.0", "", "3.5")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_dprime_bl2
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Dprime_BL2.png"),
#        plot_dprime_bl2, width = 6, height = 4)

#### LMER d' BL2 -----
mod_d_bl2 <- lmer(dprime ~ group * dprime_type + age + (1|subj_idx), data = dat_dprime_bl2_long)
anova(mod_d_bl2, type = 3)
summary(mod_d_bl2)
r.squaredGLMM(mod_d_bl2)
print(emmeans(mod_d_bl2, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_d_bl2, list(pairwise ~ dprime_type), adjust = "mvt"))
print(emmeans(mod_d_bl2, list(pairwise ~ group|dprime_type), adjust = "mvt"))
print(emmeans(mod_d_bl2, list(pairwise ~ dprime_type|group), adjust = "mvt"))
check_model(mod_d_bl2)
```

### RT
```{r}
# plot RT BL2
plot_rt_bl2 <- ggplot(dat_topx_bl2, 
                       aes(x= cttype, y=rt_mdn, group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Reaction Times (RT) at Visit 2", 
       y = "Median Correct RT (ms)", 
       x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_bl2
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_RT_BL2.png"),
#        plot_rt_bl2, width = 6, height = 4)

### LMER RT BL2
mod_rt_bl2 <- lmer(rt_mdn ~ group * cttype + age + (1|subj_idx), data = dat_topx_behav_bl2)
anova(mod_rt_bl2, type = 3)
summary(mod_rt_bl2)
r.squaredGLMM(mod_rt_bl2)
print(emmeans(mod_rt_bl2, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_rt_bl2, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rt_bl2, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_rt_bl2, list(pairwise ~ cttype|group), adjust = "mvt"))
check_model(mod_rt_bl2)
```

## BL1+BL2 sep ----------
### error
```{r}
### plot error BL1+BL2 sep (w/ visit)----------
plot_err_sep <- ggplot(dat_topx_all, 
                        aes(x= cttype, y=error, group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Error Rates", 
       y = "Error Rate", 
       x = "Trial Type", 
       color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(0.05, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_sep
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Error_Sep.png"),
#        plot_err_sep, width = 6, height = 4)

### LMER error BL1+BL2 Sep (w/ visit) -----------
mod_err_sep <- lmer(error ~ group * cttype * visit + age + (1|subj_idx), data = dat_topx_behav)


anova(mod_err_sep, type = 3)
print(summary(mod_err_sep))
r.squaredGLMM(mod_err_sep)
print(emmeans(mod_err_sep, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ visit), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ cttype|group), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ group|visit), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ visit|group), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ cttype|visit), adjust = "mvt"))
print(emmeans(mod_err_sep, list(pairwise ~ visit|cttype), adjust = "mvt"))
check_model(mod_err_sep)
```

### d'
```{r}
# plot d' BL1+BL2 Sep (w/ visit)
plot_dprime_sep <- ggplot(dat_dprime_all_long, 
                             aes(x= dprime_type, y=dprime, 
                                 group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit),
               position = position_dodge(width = 0.1),
               linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group),
               position = position_dodge(width = 0.1), 
               size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               position = position_dodge(width = 0.1),
               width = 0.2, size = 1) + 
  labs(title = "D-primes (d')", 
       y = "d' Value", 
       x = "d' Type", color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(2.0, 3.5)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) + 
  scale_x_discrete(labels = c("d_context" = "d' Context", 
                              "d_expect" = "d' Expectancy")) +
  scale_y_continuous(breaks = c(seq(2.0, 3.5, by = 0.25)),
                     labels = c("2.0","", "2.5", "", "3.0", "", "3.5")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_dprime_sep

# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Dprime_Sep.png"),
#        plot_dprime_sep, width = 6, height = 4)

#### LMER d' BL1+BL2 sep (w/ visit)-----
mod_d_sep <- lmer(dprime ~ group * dprime_type * visit + age + (1|subj_idx), data = dat_dprime_all_long)
anova(mod_d_sep, type = 3)
r.squaredGLMM(mod_d_sep)
print(emmeans(mod_d_sep, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ dprime_type), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ visit), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ group|dprime_type), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ dprime_type|group), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ dprime_type|visit), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ visit|dprime_type), adjust = "mvt"))
print(emmeans(mod_d_sep, list(pairwise ~ group|dprime_type|visit), adjust = "mvt"))
check_model(mod_d_sep)
```

### RT
```{r}
### plot RT BL1+BL2 Sep (w/ visit) ----------
plot_rt_sep <- ggplot(dat_topx_all, 
                       aes(x= cttype, y=rt_mdn, 
                           group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Reaction Times (RT)", 
       y = "Median Correct RT (ms)", 
       x = "Trial Type", color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_sep
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_RT_Sep.png"),
#        plot_rt_sep, width = 6, height = 4)

### LMER RT BL1+BL2 sep (w/ visit) -----------
mod_rt_sep <- lmer(rt_mdn ~ group * cttype * visit + age + (1|subj_idx), data = dat_topx_behav)
anova(mod_rt_sep, type = 3)
summary(mod_rt_sep)
r.squaredGLMM(mod_rt_sep)
print(emmeans(mod_rt_sep, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_rt_sep, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rt_sep, list(pairwise ~ visit), adjust = "mvt"))
print(emmeans(mod_rt_sep, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_rt_sep, list(pairwise ~ cttype|group), adjust = "mvt"))
print(emmeans(mod_rt_sep, list(pairwise ~ group|visit), adjust = "mvt"))
print(emmeans(mod_rt_sep, list(pairwise ~ visit|group), adjust = "mvt"))
check_model(mod_rt_sep)
```

## BL1+BL2 comb -------
### error
```{r}
# plot error BL1+BL2 Combined (w/o visit)
plot_err_comb <- ggplot(dat_topx_all,
                        aes(x= cttype, y=error, group = group)) +
  stat_summary(fun="mean", geom="line", aes(color = group), linewidth = 1.5) +
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) +
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               width = 0.1, size = 1) +
  labs(title = "Error Rates",
       y = "Error Rate", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.05, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_comb
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Error_Comb.png"),
#        plot_err_comb, width = 6, height = 4)

### LMER Error BL1+BL2 Combined (w/o visit)
mod_err_comb <- lmer(error ~ group * cttype + age + (1|subj_idx), data = dat_topx_behav)
anova(mod_err_comb, type = 3)
summary(mod_err_comb)
r.squaredGLMM(mod_err_comb)
print(emmeans(mod_err_comb, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_err_comb, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_err_comb, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_err_comb, list(pairwise ~ cttype|group), adjust = "mvt"))
check_model(mod_err_comb)
```

### d'
```{r}
# plot d' BL1+BL2 Comb (w/o visit)
plot_dprime_comb <- ggplot(dat_dprime_all_long, 
                          aes(x= dprime_type, y=dprime, 
                              group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group),
               linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               width = 0.05, size = 1) + 
  labs(title = "D-prime (d') Statistics", 
       y = "d' Value", 
       x = "d' Type", color = "Group") +
  coord_cartesian(ylim = c(2.0, 3.5)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_x_discrete(labels = c("d_context" = "d' Context", 
                              "d_expect" = "d' Expectancy")) +
  scale_y_continuous(breaks = c(seq(2.0, 3.5, by = 0.25)),
                     labels = c("2.0","", "2.5", "", "3.0", "", "3.5")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_dprime_comb
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_Dprime_Comb.png"),
#        plot_dprime_comb, width = 6, height = 4)

#### LMER d' BL1+BL2 Combined (w/o visit)
mod_d_comb <- lmer(dprime ~ group * dprime_type + age + (1|subj_idx), data = dat_dprime_all_long)
anova(mod_d_comb, type = 3)
r.squaredGLMM(mod_d_comb)
print(emmeans(mod_d_comb, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_d_comb, list(pairwise ~ dprime_type), adjust = "mvt"))
print(emmeans(mod_d_comb, list(pairwise ~ group|dprime_type), adjust = "mvt"))
print(emmeans(mod_d_comb, list(pairwise ~ dprime_type|group), adjust = "mvt"))
check_model(mod_d_comb)

# exploring with t-tests
# t.test(d_context ~ group, dat_dprime_all)
# t.test(dat_dprime_all$group_n, dat_dprime_all$d_context, paired=FALSE, alternative = "two.sided")
# t.test(d_expect ~ group, dat_dprime_all)
# t.test(dat_dprime_all$group_n, dat_dprime_all$d_expect, paired=FALSE, alternative = "two.sided")
```


### RT
```{r}
# plot RT BL1+BL2 comb (w/o visit)
plot_rt_comb <- ggplot(dat_topx_all, 
                       aes(x= cttype, y=rt_mdn, group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Reaction Times (RT)", 
       y = "Median Correct RT (ms)", 
       x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_comb
# ggsave(paste0("graphs/topx/", format(Sys.Date(), "%Y%m%d"), "_RT_Comb.png"), 
#        plot_rt_comb, width = 6, height = 4)

### LMER RT BL1+BL2 Comb (w/o visit)
mod_rt_comb <- lmer(rt_mdn ~ group * cttype + age + (1|subj_idx), data = dat_topx_behav)
anova(mod_rt_comb, type = 3)
summary(mod_rt_comb)
r.squaredGLMM(mod_rt_comb)
print(emmeans(mod_rt_comb, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_rt_comb, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rt_comb, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_rt_comb, list(pairwise ~ cttype|group), adjust = "mvt"))
check_model(mod_rt_comb)
```

### investigate age
```{r}
# investigate age
# dat_topx_behav <- dat_topx_behav %>%
#   mutate(age_split = ifelse(age >= median(age, , na.rm = TRUE), 1, 0),  .after = age) %>% 
#   mutate(age_split = as.numeric(age_split))
# 
# table(dat_topx_behav$age_split)/8
# median(dat_topx_behav$age)

dat_topx_behav %>%
  group_by(age_split, cttype, visit) %>%
  summarize(mean_rt_mdn = mean(rt_mdn, na.rm = TRUE), 
            sd_mdn = sd(rt_mdn, na.rm = TRUE))

# repeated measures
t.test(rt_mdn ~ age_split, data = dat_topx_behav)
cor.test(dat_topx_behav$age, dat_topx_behav$rt_mdn)

# collapse 8 RTs to one RT
age_rt_summary <- dat_topx_behav %>%
  group_by(subj_idx, age_split) %>%  # include age_split in the group
  summarise(mean_rt_mdn = mean(rt_mdn, na.rm = TRUE), .groups = "drop")
t.test(mean_rt_mdn ~ age_split, data = age_rt_summary)

age_rt_summary_visit <- dat_topx_behav %>%
  group_by(subj_idx, age_split, visit) %>%  # include age_split in the group
  summarise(mean_rt_mdn = mean(rt_mdn, na.rm = TRUE), .groups = "drop")

# test avg RT at BL1
age_rt_summary_bl1 <- age_rt_summary_visit %>% 
  filter(visit == "BL1")
t.test(mean_rt_mdn ~ age_split, data = age_rt_summary_bl1)

# test avg RT at BL2
age_rt_summary_bl2 <- age_rt_summary_visit %>% 
  filter(visit == "BL2")
t.test(mean_rt_mdn ~ age_split, data = age_rt_summary_bl2)

age_rt_summary %>%
  group_by(age_split) %>%
  summarize(mean_rt_mdn = mean(mean_rt_mdn, na.rm = TRUE))

# test AX at BL1 - reporting this in paper's main text
dat_topx_behav_bl1_AX <- dat_topx_behav %>% 
  filter(visit == "BL1" & cttype == "AX")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl1_AX)
cor.test(dat_topx_behav_bl1_AX$age, dat_topx_behav_bl1_AX$rt_mdn)

# test AX at BL2 - reporting this in supplement
dat_topx_behav_bl2_AX <- dat_topx_behav %>% 
  filter(visit == "BL2" & cttype == "AX")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl2_AX)
cor.test(dat_topx_behav_bl2_AX$age, dat_topx_behav_bl2_AX$rt_mdn)

# test AY at BL1
dat_topx_behav_bl1_AY <- dat_topx_behav %>% 
  filter(visit == "BL1" & cttype == "AY")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl1_AY)
cor.test(dat_topx_behav_bl1_AY$age, dat_topx_behav_bl1_AY$rt_mdn)

# test AY at BL2
dat_topx_behav_bl2_AY <- dat_topx_behav %>% 
  filter(visit == "BL2" & cttype == "AY")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl2_AY)
cor.test(dat_topx_behav_bl2_AY$age, dat_topx_behav_bl2_AY$rt_mdn)

# test BX at BL1
dat_topx_behav_bl1_BX <- dat_topx_behav %>% 
  filter(visit == "BL1" & cttype == "BX")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl1_BX)
cor.test(dat_topx_behav_bl1_BX$age, dat_topx_behav_bl1_BX$rt_mdn)

# test BX at BL2
dat_topx_behav_bl2_BX <- dat_topx_behav %>% 
  filter(visit == "BL2" & cttype == "BX")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl2_BX)
cor.test(dat_topx_behav_bl2_BX$age, dat_topx_behav_bl2_BX$rt_mdn)

# test BY at BL1
dat_topx_behav_bl1_BY <- dat_topx_behav %>% 
  filter(visit == "BL1" & cttype == "BY")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl1_BY)
cor.test(dat_topx_behav_bl1_BY$age, dat_topx_behav_bl1_BY$rt_mdn)

# test BY at BL2
dat_topx_behav_bl2_BY <- dat_topx_behav %>% 
  filter(visit == "BL2" & cttype == "BY")
t.test(rt_mdn ~ age_split, data = dat_topx_behav_bl2_BY)
cor.test(dat_topx_behav_bl2_BY$age, dat_topx_behav_bl2_BY$rt_mdn)

# run as LMER
mod_rtAge <- lmer(rt_mdn ~ age_split * cttype * visit + (1|subj_idx), data = dat_topx_behav)
anova(mod_rtAge)
```

# MODELED ANALYSES

## ddm functions
lmer_bl, lmer_bl_sep, lmer_check, plot_bl, plot_bl_sep
```{r}
# run lmer for single dataset (BL1, BL2 or BL1-BL2 merged)
lmer_bl <- function(dat,  model_name = "model_output", posthoc = FALSE) {
  model <- lmer(mean ~ group * cttype + age + (1|subj_idx), dat) # group:cttype
  assign(model_name, model, envir = .GlobalEnv)
  print(anova(model, type = 3))
  print(summary(model))
  if(posthoc == TRUE) {
    print(emmeans(model, list(pairwise ~ group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|group), adjust = "mvt"))
  }
}

# run lmer for multiple visits (BL1 and BL2)
lmer_bl_sep <- function(dat, model_name = "model_output", posthoc = FALSE) {
  model <- lmer(mean ~ group * cttype * visit + age + (1|subj_idx), dat)
  assign(model_name, model, envir = .GlobalEnv)  # Save the model in the global environment
  print(anova(model, type = 3))
  print(summary(model))
  if(posthoc == TRUE) {
    print(emmeans(model, list(pairwise ~ group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit|group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit|cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|cttype|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|group|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit|group|cttype), adjust = "mvt"))
  }
}

# check lmer model fit
lmer_check <- function(model, title_lab) {
  # calculate variance inflation
  print(car::vif(model))
  print(model_parameters(model))
  # check model and save plots
  mod_check_plots <- check_model(model)
  print(mod_check_plots)
  png(paste0("graphs/model_check/", format(Sys.Date(), "%Y%m%d"),
             "_ModelCheck_", title_lab, ".png"),
      width = 500, height = 600)
  plot(mod_check_plots)
  dev.off()
}

# extra code taht could be used for further testing:
  # print(plot(model, resid(.) ~ fitted(.)))
  # print(qqnorm(resid(model)))
  # print(qqline(resid(model)))
  # ggdensity(dat$mean)
  # shapiro.test(dat$mean)

# plot single dataset (BL1, BL2 or BL1-BL2 merged)
plot_bl <- function(dat, title_lab, param_lab, file_lab, ymin, ymax) {
  dat_dummy <- dat %>%
    mutate(mean = if_else(cttype == "AY" & parameter == "v", -1 * mean, mean))
  plot <- ggplot(dat_dummy, aes(x= cttype, y=mean, group = group)) + 
    stat_summary(fun="mean", geom="line", aes(color = group), linewidth = 1.5) + 
    stat_summary(fun="mean", geom="point", aes(color = group), size = 3) +
    stat_summary(fun.data = mean_se, geom = "errorbar", 
                 aes(color = group), width = 0.1, size = 1) + 
    labs(title = title_lab, y = param_lab, 
         x = "Trial Type", color = "Group") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    scale_color_manual(values=c("#2C737F", "#AA8829"),
                       labels=c("Ctl", "EP")) + 
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"), 
          axis.text = element_text(face="bold", size = 16),
          axis.title = element_text(face="bold", size = 20),
          legend.text = element_text(face="bold", size = 14),
          legend.title = element_text(face = "bold", size = 16),
          plot.title = element_text(face = "bold", size = 22))
  print(plot)
  # ggsave(paste0("graphs/ddm/", format(Sys.Date(), "%Y%m%d"), "_", file_lab, ".png"),
  #        plot, width = 6, height = 4)
}

# plot multiple visits (BL1 and BL2)
plot_bl_sep <- function(dat, title_lab, param_lab, file_lab, ymin, ymax) {
  dat_dummy <- dat %>%
    mutate(mean = if_else(cttype == "AY" & parameter == "v", -1 * mean, mean))
  plot <- ggplot(dat_dummy, aes(x= cttype, y=mean, 
                   group = interaction(group,visit))) + 
    stat_summary(fun="mean", geom="line", 
                 aes(color = group, linetype = visit), size = 1.5) + 
    stat_summary(fun="mean", geom="point", aes(color = group), size = 3) +
    stat_summary(fun.data = mean_se, geom = "errorbar", 
                 aes(color = group), width = 0.1, 
                 size = 1) + 
    labs(title = title_lab, y = param_lab, 
         x = "Trial Type", color = "Group", linetype = "Visit") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    scale_color_manual(values=c("#2C737F", "#AA8829"),
                       labels=c("Ctl", "EP")) + 
    scale_linetype_manual(values = c("solid", "dotted"), 
                          labels = c("Visit 1", "Visit 2")) + 
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"), 
          axis.text = element_text(face="bold", size = 16),
          axis.title = element_text(face="bold", size = 20),
          legend.text = element_text(face="bold", size = 14),
          legend.title = element_text(face = "bold", size = 16),
          plot.title = element_text(face = "bold", size = 22))
  print(plot)
  # ggsave(paste0("graphs/ddm/", format(Sys.Date(), "%Y%m%d"), "_", file_lab, ".png"),
  #        plot, width = 6, height = 4)
}
```

## visualize density/distribution
```{r}
plot_dist_mod <- function(dat) {
  plot <- ggplot(dat, aes(x = mean, group = cttype, fill = cttype)) +
  geom_density(adjust = 1.5, alpha = 0.4) +
  facet_wrap(~ interaction(group, visit))
  print(plot)
}

plot_dist_mod(v_dat_all)
plot_dist_mod(a_dat_all)
plot_dist_mod(t_dat_all)
plot_dist_mod(z_dat_all)

normality_test <- function(dat) {
  results <- dat %>% 
    group_by(group, visit, cttype) %>%
    summarise(p_value = tryCatch(round(shapiro.test(mean)$p.value, 3), 
                                 error = function(e) NA), .groups = "drop")
  print(results)
}

normality_test(v_dat_all)
normality_test(a_dat_all)
normality_test(t_dat_all)
normality_test(z_dat_all)

```



## BL1----------------------
### drift rate (v)
```{r}
plot_bl(v_dat_bl1, "Drift Rates at Visit 1", "Drift Rate (v)", "DriftRate_BL1", .7, 3)
lmer_bl(v_dat_bl1, "mod_v_bl1", posthoc = FALSE)
lmer_check(mod_v_bl1, "v_bl1")
```

### decision threshold (a)
```{r}
plot_bl(a_dat_bl1, "Decision Thresholds at Visit 1", "Decision Threshold (a)", "DecisionThreshold_BL1", .47, .63)
lmer_bl(a_dat_bl1, "mod_a_bl1", posthoc = FALSE)
lmer_check(mod_a_bl1, "a_bl1")
```

### non-decision time (t)
```{r}
plot_bl(t_dat_bl1, "Non-Decision Times at Visit 1", "Non-Decision Time (t)", "NonDecisionTime_BL1", .17, .25)
lmer_bl(t_dat_bl1, "mod_t_bl1", posthoc = FALSE)
lmer_check(mod_t_bl1, "t_bl1")
```

### bias (z)
```{r}
plot_bl(z_dat_bl1, "Degrees of Bias at Visit 1", "Degree of Bias (w)", "Bias_BL1", .5, .65)
lmer_bl(z_dat_bl1, "mod_z_bl1", posthoc = FALSE)
lmer_check(mod_z_bl1, "z_bl1")
```


## BL2-----------------------
### drift rate (v)
```{r}
plot_bl(v_dat_bl2, "Drift Rates at Visit 2", "Drift Rate (v)", "DriftRate_BL2", .7, 3)
lmer_bl(v_dat_bl2, "mod_v_bl2", posthoc = FALSE)
lmer_check(mod_v_bl2, "v_bl2")
```

### decision threshold (a)
```{r}
plot_bl(a_dat_bl2, "Decision Thresholds at Visit 2", "Decision Threshold (a)", "DecisionThreshold_BL2", .47, .63)
lmer_bl(a_dat_bl2, "mod_a_bl2", posthoc = FALSE)
lmer_check(mod_a_bl2, "a_bl2")
```

### non-decision time (t)
```{r}
plot_bl(t_dat_bl2, "Non-Decision Times at Visit 2", "Non-Decision Time (t)", "NonDecisionTime_BL2", .17, .25)
lmer_bl(t_dat_bl2, "mod_t_bl2", posthoc = FALSE)
lmer_check(mod_t_bl2, "t_bl2")
```

### bias (z)
```{r}
plot_bl(z_dat_bl2, "Degrees of Bias at Visit 2", "Degree of Bias (w)", "Bias_BL2", .5, .65)
lmer_bl(z_dat_bl2, "mod_z_bl2", posthoc = FALSE)
lmer_check(mod_z_bl2, "z_bl2")
```

## BL+BL2 Comb --------

### drift rate (v)
```{r}
plot_bl(v_dat_all, "Drift Rates", "Drift Rate (v)", "DriftRate_Comb", .7, 3)
lmer_bl(v_dat_all, "mod_v_comb", posthoc = TRUE)
r.squaredGLMM(mod_v_comb)
lmer_check(mod_v_comb, "v_comb")
```

### decision threshold (a)
```{r}
plot_bl(a_dat_all, "Decision Thresholds", "Decision Threshold (a)", "DecisionThreshold_Comb", .47, .63)
lmer_bl(a_dat_all, "mod_a_comb", posthoc = TRUE)
r.squaredGLMM(mod_a_comb)
lmer_check(mod_a_comb, "a_comb")
```

### non-decision time (t)
```{r}
plot_bl(t_dat_all, "Non-Decision Times", "Non-Decision Time (t)", "NonDecisionTime_Comb", .17, .25)
lmer_bl(t_dat_all, "mod_t_comb", posthoc = TRUE)
r.squaredGLMM(mod_t_comb)
lmer_check(mod_t_comb, "t_comb")
```

### bias (z)
```{r}
plot_bl(z_dat_all, "Degrees of Bias", "Degree of Bias (w)", "Bias_Comb", .5, .65)
lmer_bl(z_dat_all, "mod_z_comb", posthoc = TRUE)
r.squaredGLMM(mod_z_comb)
lmer_check(mod_z_comb, "z_comb")
```

## BL+BL2 Sep --------

### drift rate (v)
```{r}
plot_bl_sep(v_dat_all, "Drift Rates at Visit 1 & 2", "Drift Rate (v)", "DriftRate_Sep", .7, 3)
lmer_bl_sep(v_dat_all, "mod_v_sep", posthoc = TRUE)
r.squaredGLMM(mod_v_sep)
lmer_check(mod_v_sep, "v_sep")
```

### decision threshold (a)
```{r}
plot_bl_sep(a_dat_all, "Decision Thresholds at Visit 1 & 2", "Decision Threshold (a)", "DecisionThreshold_Sep", .47, .63)
lmer_bl_sep(a_dat_all, "mod_a_sep", posthoc = TRUE)
r.squaredGLMM(mod_a_sep)
lmer_check(mod_a_sep, "a_sep")
```

### non-decision time (t)
```{r}
plot_bl_sep(t_dat_all, "Non-Decision Times at Visit 1 & 2", "Non-Decision Time (t)", "NonDecisionTime_Sep", .17, .25)
lmer_bl_sep(t_dat_all, "mod_t_sep", posthoc = TRUE)
r.squaredGLMM(mod_t_sep)
lmer_check(mod_t_sep, "t_sep")
```

### bias (z)
```{r}
plot_bl_sep(z_dat_all, "Degrees of Bias at Visit 1 & 2", "Degree of Bias (w)", "Bias_Sep", .5, .65)
lmer_bl_sep(z_dat_all, "mod_z_sep", posthoc = TRUE)
r.squaredGLMM(mod_z_sep)
lmer_check(mod_z_sep, "z_sep")
```


## other -------------------
### investigate age (a)
```{r}
# a_dat_all <- a_dat_all %>%
#   mutate(age_split = ifelse(age >= median(age, na.rm = TRUE), 1, 0)) %>% 
#   mutate(age_split = as.numeric(age_split))
# 
# a_dat_all %>%
#   group_by(age_split) %>%
#   summarize(mean = mean(mean, na.rm = TRUE))

# t.test(a_dat_all$age_split, a_dat_all$mean, na.rm = TRUE)

t.test(mean ~ age_split, data = a_dat_all)

mod_a_Age <- lmer(mean ~ age_split * cttype * visit + (1|subj_idx), data = a_dat_all)
anova(mod_a_Age)

# test AX at BL1 - reporting this in paper's main text
a_dat_bl1_AX <- a_dat_bl1 %>% 
  filter(cttype == "AX")
t.test(mean ~ age_split, data = a_dat_bl1_AX)
cor.test(a_dat_bl1_AX$age, a_dat_bl1_AX$mean)

# test AX at BL2 - reporting this in supplement
a_dat_bl2_AX <- a_dat_bl2 %>% 
  filter(cttype == "AX")
t.test(mean ~ age_split, data = a_dat_bl2_AX)
cor.test(a_dat_bl2_AX$age, a_dat_bl2_AX$mean)

# test AY at BL1 - reporting this in paper's main text
a_dat_bl1_AY <- a_dat_bl1 %>% 
  filter(cttype == "AY")
t.test(mean ~ age_split, data = a_dat_bl1_AY)
cor.test(a_dat_bl1_AY$age, a_dat_bl1_AY$mean)

# test AY at BL2 - reporting this in supplement
a_dat_bl2_AY <- a_dat_bl2 %>% 
  filter(cttype == "AY")
t.test(mean ~ age_split, data = a_dat_bl2_AY)
cor.test(a_dat_bl2_AY$age, a_dat_bl2_AY$mean)

# test BX at BL1 - reporting this in paper's main text
a_dat_bl1_BX <- a_dat_bl1 %>% 
  filter(cttype == "BX")
t.test(mean ~ age_split, data = a_dat_bl1_BX)
cor.test(a_dat_bl1_BX$age, a_dat_bl1_BX$mean)

# test BX at BL2 - reporting this in supplement
a_dat_bl2_BX <- a_dat_bl2 %>% 
  filter(cttype == "BX")
t.test(mean ~ age_split, data = a_dat_bl2_BX)
cor.test(a_dat_bl2_BX$age, a_dat_bl2_BX$mean)

# test BY at BL1 - reporting this in paper's main text
a_dat_bl1_BY <- a_dat_bl1 %>% 
  filter(cttype == "BY")
t.test(mean ~ age_split, data = a_dat_bl1_BY)
cor.test(a_dat_bl1_BY$age, a_dat_bl1_BY$mean)

# test BY at BL2 - reporting this in supplement
a_dat_bl2_BY <- a_dat_bl2 %>% 
  filter(cttype == "BY")
t.test(mean ~ age_split, data = a_dat_bl2_BY)
cor.test(a_dat_bl2_BY$age, a_dat_bl2_BY$mean)

# ggplot(a_dat_all, aes(x = age_split, y = mean)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Age", y = "Decision threshold", title = "1 = older, 0 = younger")

```

### investigate age (t)
```{r}
# investigate age
# t_dat_all <- t_dat_all %>%
#   mutate(age_split = ifelse(age >= median(age, , na.rm = TRUE), 1, 0)) %>% 
#   mutate(age_split = as.numeric(age_split))

# t.test(t_dat_all$age_split, t_dat_all$mean, na.rm = TRUE)

# ggplot(t_dat_all, aes(x = age_split, y = mean)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Age", y = "Non-decision time", title = "1 = older, 0 = younger")

t.test(mean ~ age_split, data = t_dat_all)

mod_t_Age <- lmer(mean ~ age_split * cttype * visit + (1|subj_idx), data = t_dat_all)
anova(mod_t_Age)

# test AX at BL1 - reporting this in paper's main text
t_dat_bl1_AX <- t_dat_bl1 %>% 
  filter(cttype == "AX")
t.test(mean ~ age_split, data = t_dat_bl1_AX)
cor.test(t_dat_bl1_AX$age, t_dat_bl1_AX$mean)

# test AX at BL2 - reporting this in supplement
t_dat_bl2_AX <- t_dat_bl2 %>% 
  filter(cttype == "AX")
t.test(mean ~ age_split, data = t_dat_bl2_AX)
cor.test(t_dat_bl2_AX$age, t_dat_bl2_AX$mean)

# test AY at BL1 - reporting this in paper's main text
t_dat_bl1_AY <- t_dat_bl1 %>% 
  filter(cttype == "AY")
t.test(mean ~ age_split, data = t_dat_bl1_AY)
cor.test(t_dat_bl1_AY$age, t_dat_bl1_AY$mean)

# test AY at BL2 - reporting this in supplement
t_dat_bl2_AY <- t_dat_bl2 %>% 
  filter(cttype == "AY")
t.test(mean ~ age_split, data = t_dat_bl2_AY)
cor.test(t_dat_bl2_AY$age, t_dat_bl2_AY$mean)

# test BX at BL1 - reporting this in paper's main text
t_dat_bl1_BX <- t_dat_bl1 %>% 
  filter(cttype == "BX")
t.test(mean ~ age_split, data = t_dat_bl1_BX)
cor.test(t_dat_bl1_BX$age, t_dat_bl1_BX$mean)

# test BX at BL2 - reporting this in supplement
t_dat_bl2_BX <- t_dat_bl2 %>% 
  filter(cttype == "BX")
t.test(mean ~ age_split, data = t_dat_bl2_BX)
cor.test(t_dat_bl2_BX$age, t_dat_bl2_BX$mean)

# test BY at BL1 - reporting this in paper's main text
t_dat_bl1_BY <- t_dat_bl1 %>% 
  filter(cttype == "BY")
t.test(mean ~ age_split, data = t_dat_bl1_BY)
cor.test(t_dat_bl1_BY$age, t_dat_bl1_BY$mean)

# test BY at BL2 - reporting this in supplement
t_dat_bl2_BY <- t_dat_bl2 %>% 
  filter(cttype == "BY")
t.test(mean ~ age_split, data = t_dat_bl2_BY)
cor.test(t_dat_bl2_BY$age, t_dat_bl2_BY$mean)
```

# correlations - 14 vars
## comb
```{r}
# filter ddm data (long form) to only include ddm variables, for correlation matrix
dat_cor_comb <- dat_ddm_all_long %>% 
  select(-c(participant_id, visit))

# run the correlations and rename variables
dat_cor_comb <- cor(dat_cor_comb)
colnames(dat_cor_comb) <- c("v-AX", "v-AY", "v-BX", "v-BY",
                           "a-AX", "a-AY", "a-BX", "a-BY",
                           "t-AX", "t-AY", "t-BX", "t-BY",
                           "w-A", "w-B")
rownames(dat_cor_comb) <- c("v-AX", "v-AY", "v-BX", "v-BY",
                           "a-AX", "a-AY", "a-BX", "a-BY",
                           "t-AX", "t-AY", "t-BX", "t-BY",
                           "w-A", "w-B")

# plot a correlation matrix
corrplot(dat_cor_comb, 
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 0.65,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 0.55,  # Coefficient text size
         title = "Parameter Correlations (Combined Visit 1+2)", # title
         mar = c(.5, .5, 1, .5))  # Adjust margins for title spacing
```

## bl1
```{r}
# filter data to BL1 DDM variables only
dat_ddm_bl1_long <- dat_ddm_all_long %>% 
  filter(visit == "BL1")
dat_cor_bl1 <- dat_ddm_bl1_long %>% 
  select(-c(participant_id, visit))

# run correlation and rename variables
dat_cor_bl1 <- cor(dat_cor_bl1)
colnames(dat_cor_bl1) <- c("v-AX", "v-AY", "v-BX", "v-BY",
                           "a-AX", "a-AY", "a-BX", "a-BY",
                           "t-AX", "t-AY", "t-BX", "t-BY",
                           "w-A", "w-B")
rownames(dat_cor_bl1) <- c("v-AX", "v-AY", "v-BX", "v-BY",
                           "a-AX", "a-AY", "a-BX", "a-BY",
                           "t-AX", "t-AY", "t-BX", "t-BY",
                           "w-A", "w-B")

# plot the correlation matrix
corrplot(dat_cor_bl1, 
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 0.65,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 0.55,  # Coefficient text size
         title = "Parameter Correlations at Visit 1", # title
         mar = c(.5, .5, 1, .5))  # Adjust margins for title spacing
  
```

## bl2
```{r}
# # filter data to BL2 DDM variables only
dat_ddm_bl2_long <- dat_ddm_all_long %>% 
  filter(visit == "BL2")
dat_cor_bl2 <- dat_ddm_bl2_long %>% 
  select(-c(participant_id, visit))

# run correlation and rename variables
dat_cor_bl2 <- cor(dat_cor_bl2)
colnames(dat_cor_bl2) <- c("v-AX", "v-AY", "v-BX", "v-BY",
                           "a-AX", "a-AY", "a-BX", "a-BY",
                           "t-AX", "t-AY", "t-BX", "t-BY",
                           "w-A", "w-B")
rownames(dat_cor_bl2) <- c("v-AX", "v-AY", "v-BX", "v-BY",
                           "a-AX", "a-AY", "a-BX", "a-BY",
                           "t-AX", "t-AY", "t-BX", "t-BY",
                           "w-A", "w-B")

# plot the correlation matrix
corrplot(dat_cor_bl2, 
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 0.65,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 0.55,  # Coefficient text size
         title = "Parameter Correlations at Visit 1", # title
         mar = c(.5, .5, 1, .5))  # Adjust margins for title spacing
```

# correlations - 4 vars
## calculate intercepts
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data_intc <- function(block, types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_ddm/data/20241031_ddm_data/", block, "/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]])) %>%
      rename(!!paste0(type, "_ppt") := participant)
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = toupper(block), .after = participant_id)
}

# Column mappings for different file types
column_mappings_intc <- list(
  v = c("participant_id", "v_intc", "participant"),
  a = c("participant_id", "a_intc", "participant"),
  t = c("participant_id", "t_intc", "participant"),
  z = c("participant_id", "z_intc", "participant")
)

# Process data for each block
types_intc <- names(column_mappings_intc)
dat_ddm_bl1_intc <- process_data_intc("bl1", types_intc, column_mappings_intc)
dat_ddm_bl2_intc <- process_data_intc("bl2", types_intc, column_mappings_intc)


# Filter to retain only common participant_ids
common_ids_intc <- intersect(dat_ddm_bl1_intc$participant_id, dat_ddm_bl2_intc$participant_id)
dat_ddm_bl1_intc <- filter(dat_ddm_bl1_intc, participant_id %in% common_ids)
dat_ddm_bl2_intc <- filter(dat_ddm_bl2_intc, participant_id %in% common_ids)

# Combine both datasets
dat_ddm_comb_intc <- bind_rows(dat_ddm_bl1_intc, dat_ddm_bl2_intc)
colnames(dat_ddm_comb_intc)[1] <- "subj_idx"

# add vars for group+pt intercepts (not accounting for trial type)
dat_ddm_bl1_intc <- dat_ddm_bl1_intc %>% 
  mutate(v_sum = v_intc + v_ppt, .after = v_ppt) %>% 
  mutate(a_sum = a_intc + a_ppt, .after = a_ppt) %>% 
  mutate(t_sum = t_intc + t_ppt, .after = t_ppt) %>% 
  mutate(z_sum = z_intc + z_ppt, .after = z_ppt)

dat_ddm_bl2_intc <- dat_ddm_bl2_intc %>% 
  mutate(v_sum = v_intc + v_ppt, .after = v_ppt) %>% 
  mutate(a_sum = a_intc + a_ppt, .after = a_ppt) %>% 
  mutate(t_sum = t_intc + t_ppt, .after = t_ppt) %>% 
  mutate(z_sum = z_intc + z_ppt, .after = z_ppt)

dat_ddm_comb_intc <- dat_ddm_comb_intc %>% 
  mutate(v_sum = v_intc + v_ppt, .after = v_ppt) %>% 
  mutate(a_sum = a_intc + a_ppt, .after = a_ppt) %>% 
  mutate(t_sum = t_intc + t_ppt, .after = t_ppt) %>% 
  mutate(z_sum = z_intc + z_ppt, .after = z_ppt)
```

## BL1+BL2 Comb
```{r}
# filter data, create vars for group+pt intercepts (not accounting for trial type)
dat_cor_comb_intc <- dat_ddm_comb_intc %>% 
  select(v_sum, a_sum, t_sum, z_sum)

# run correlations
dat_cor_comb_intc <- cor(dat_cor_comb_intc)
colnames(dat_cor_comb_intc) <- c("v", "a", "t", "w")
rownames(dat_cor_comb_intc) <- c("v", "a", "t", "w")

# plot the correlation matrix
corrplot(dat_cor_comb_intc, 
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 1,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 1,  # Coefficient text size
         title = "Parameter Correlations (Visits 1+2 Combined)", # title
         mar = c(1, 1, 2, 1))  # Adjust margins for title spacing
```

## bl1
```{r}
# filter data, create vars for group+pt intercepts (not accounting for trial type)
dat_cor_bl1_intc <- dat_ddm_bl1_intc %>% 
  select(v_sum, a_sum, t_sum, z_sum)

# run correlations
dat_cor_bl1_intc <- cor(dat_cor_bl1_intc)
colnames(dat_cor_bl1_intc) <- c("v", "a", "t", "w")
rownames(dat_cor_bl1_intc) <- c("v", "a", "t", "w")

# plot correlation matrix
corrplot(dat_cor_bl1_intc,
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 1,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 1,  # Coefficient text size
         title = "Parameter Correlations at Visit 1", # title
         mar = c(1, 1, 2, 1))  # Adjust margins for title spacing
```

## bl2
```{r}
# filter data, create vars for group+pt intercepts (not accounting for trial type)
dat_cor_bl2_intc <- dat_ddm_bl2_intc %>% 
  select(v_sum, a_sum, t_sum, z_sum)

# run correlations
dat_cor_bl2_intc <- cor(dat_cor_bl2_intc)
colnames(dat_cor_bl2_intc) <- c("v", "a", "t", "w")
rownames(dat_cor_bl2_intc) <- c("v", "a", "t", "w")

# plot correlation matrix
corrplot(dat_cor_bl2_intc,
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 1,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 1,  # Coefficient text size
         title = "Parameter Correlations at Visit 2", # title
         mar = c(1, 1, 2, 1))  # Adjust margins for title spacing
```

# v-BPRS correlations BL1+BL2 Comb - pearson
```{r}
# pearson
# filter data to include drift rate only
v_dat_all_pt = filter(dat_ddm_behav, parameter == 'v' & group == "Patient")

# Run correlations between "mean" and multiple bprs variables, grouped by "cttype"
cor_table_v <- v_dat_all_pt %>%
  group_by(cttype) %>%
  summarise(
    cor_bprs_pos= cor(mean, bprs_pos_ws, use = "complete.obs"), # exclude NAs
    cor_bprs_neg= cor(mean, bprs_neg_ws, use = "complete.obs"),
    cor_bprs_disorg = cor(mean, bprs_disorg_ws, use = "complete.obs"),
    .groups = "drop")
print(cor_table_v)

cor_matrix_v <- as.matrix(cor_table_v[, -1])
colnames(cor_matrix_v) <- c("Positive", "Negative", "Disorganized")
rownames(cor_matrix_v) <- c("v-AX", "v-AY", "v-BX", "v-BY")

# plot correlation matrix
corrplot(cor_matrix_v,
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 1,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 1,  # Coefficient text size
         title = "Correlations of Drift Rate and BPRS", # title
         mar = c(1, 1, 2, 1))  # Adjust margins for title spacing


# Compute correlation coefficients and p-values within summarise()
cor_table_v2 <- v_dat_all_pt %>%
  group_by(cttype) %>%
  summarise(
    cor_bprs_pos = cor(mean, bprs_pos_ws, use = "complete.obs"),
    p_bprs_pos = cor.test(mean, bprs_pos_ws)$p.value,  # Extract p-value
    
    cor_bprs_neg = cor(mean, bprs_neg_ws, use = "complete.obs"),
    p_bprs_neg = cor.test(mean, bprs_neg_ws)$p.value,
    
    cor_bprs_disorg = cor(mean, bprs_disorg_ws, use = "complete.obs"),
    p_bprs_disorg = cor.test(mean, bprs_disorg_ws)$p.value,
    
    .groups = "drop"
  )

# Print results
print(cor_table_v2)

```

# v-BPRS correlations BL1+BL2 Comb - spearman
```{r}
# Run Spearman correlations between "mean" and multiple BPRS variables, grouped by "cttype"
cor_table_v3 <- v_dat_all_pt %>%
  group_by(cttype) %>%
  summarise(
    cor_bprs_pos = cor(mean, bprs_pos_ws, use = "complete.obs", method = "spearman"),
    cor_bprs_neg = cor(mean, bprs_neg_ws, use = "complete.obs", method = "spearman"),
    cor_bprs_disorg = cor(mean, bprs_disorg_ws, use = "complete.obs", method = "spearman"),
    .groups = "drop"
  )
print(cor_table_v3)

cor_matrix_v3 <- as.matrix(cor_table_v3[, -1])
colnames(cor_matrix_v3) <- c("Positive", "Negative", "Disorganized")
rownames(cor_matrix_v3) <- c("v-AX", "v-AY", "v-BX", "v-BY")

# plot correlation matrix
corrplot(cor_matrix_v3,
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 1,
         tl.col = "black",
         number.cex = 1,
         title = "Spearman Correlations of Drift Rate and BPRS",
         mar = c(1, 1, 2, 1))

# Compute correlation coefficients and p-values using Spearman method
cor_table_v4 <- v_dat_all_pt %>%
  group_by(cttype) %>%
  summarise(
    cor_bprs_pos = cor(mean, bprs_pos_ws, use = "complete.obs", method = "spearman"),
    p_bprs_pos = cor.test(mean, bprs_pos_ws, method = "spearman")$p.value,
    
    cor_bprs_neg = cor(mean, bprs_neg_ws, use = "complete.obs", method = "spearman"),
    p_bprs_neg = cor.test(mean, bprs_neg_ws, method = "spearman")$p.value,
    
    cor_bprs_disorg = cor(mean, bprs_disorg_ws, use = "complete.obs", method = "spearman"),
    p_bprs_disorg = cor.test(mean, bprs_disorg_ws, method = "spearman")$p.value,
    
    .groups = "drop"
  )
print(cor_table_v4)

plot_drift_neg <- ggplot(v_dat_all_pt, aes(x=mean, y=bprs_negative, 
                         color = cttype, shape = cttype)) +
  geom_point() + 
  geom_smooth(method=lm, se = FALSE) + 
  scale_color_manual(values=c('#A280BD', '#3E8643', 
                              '#AA8829', '#2C737F')) +
  scale_shape_manual(values=c(15, 17, 18, 19)) + 
  labs(color = "Trial Type", shape = "Trial Type",
       x="Drift Rate", y = "Negative Symptoms") +
  theme_classic()
print(plot_drift_neg)
ggsave(paste0("graphs/ddm/", format(Sys.Date(), "%Y%m%d"), "_", "Drift_Rate_Neg_Sxs", ".png"), plot_drift_neg, width = 5, height = 3)

# plot BL1 AY only
v_dat_all_pt_bl1_AY <- v_dat_all_pt %>% filter(cttype == "AY" & visit == "BL1")
ggplot(v_dat_all_pt_bl1_AY, aes(x=mean, y=bprs_negative)) + geom_point() + geom_smooth(method=lm)



# Create plot with stars
# create correlation and p-value matrices
# cor_matrix_v4 <- as.matrix(cor_table_v4[, c("cor_bprs_pos", "cor_bprs_neg", "cor_bprs_disorg")])
# p_matrix_v4 <- as.matrix(cor_table_v4[, c("p_bprs_pos", "p_bprs_neg", "p_bprs_disorg")])
# # Set proper row and column names
# rownames(cor_matrix_v4) <- cor_table_v4$cttype
# rownames(p_matrix_v4) <- cor_table_v4$cttype
# colnames(cor_matrix_v4) <- c("Positive", "Negative", "Disorganized")
# colnames(p_matrix_v4) <- c("Positive", "Negative", "Disorganized")
# 
# corrplot(cor_matrix_v,
#          method = "color",
#          p.mat = p_matrix_v4,
#          sig.level = c(0.001, 0.01, 0.05),  # thresholds for stars
#          insig = "label_sig",
#          pch.cex = 1.2,
#          pch.col = "black",
#          addCoef.col = "grey45",
#          tl.col = "black",
#          tl.cex = 1,
#          number.cex = 1,
#          title = "Spearman Correlations with Significance Stars",
#          mar = c(1, 1, 2, 1))

```

# DDM-BPRS Correlations at BL1+BL2 Comb - pearson
```{r}
# merge intercepts with behav data
dat_ddm_comb_intc <- merge(dat_ddm_comb_intc, dat_behav, by = "subj_idx", all.x = TRUE)
dat_ddm_comb_intc_pt <- dat_ddm_comb_intc %>% 
  filter(group == "Patient")

# filter data to only include intercepts and bprs
dat_cor_comb_pt <- dat_ddm_comb_intc_pt %>% 
  select(v_sum, a_sum, t_sum, z_sum, bprs_pos_ws, bprs_neg_ws, bprs_disorg_ws)

# run correlations
sum(is.na(dat_cor_comb_pt))

dat_cor_comb_pt <- cor(dat_cor_comb_pt, use="pairwise.complete.obs")
colnames(dat_cor_comb_pt) <- c("v", "a", "t", "w", "Positive", "Negative", "Disorganized")
rownames(dat_cor_comb_pt) <- c("v", "a", "t", "w", "Positive", "Negative", "Disorganized")

# plot correlation matrix
corrplot(dat_cor_comb_pt,
         method = "color", 
         addCoef.col = 'grey45',
         tl.cex = 1,  # Axis label text size
         tl.col = "black", # Axis label text color
         number.cex = 1,  # Coefficient text size
         title = "Correlations of Parameters and BPRS", # title
         mar = c(1, 1, 2, 1))  # Adjust margins for title spacing


# get p-vals
# Create an empty matrix for p-values
n <- ncol(dat_cor_comb_pt)
p_values <- matrix(NA, n, n)
colnames(p_values) <- colnames(dat_cor_comb_pt)
rownames(p_values) <- rownames(dat_cor_comb_pt)

# Compute correlation coefficients and p-values
for (i in 1:(n - 1)) {
  for (j in (i + 1):n) {
    test <- cor.test(dat_cor_comb_pt[, i], dat_cor_comb_pt[, j])  # Perform cor.test
    p_values[i, j] <- test$p.value
    p_values[j, i] <- test$p.value  # Fill the symmetric matrix
  }
}

# Print p-value matrix
print(p_values)
```

# DDM-BPRS Correlations at BL1+BL2 Comb - spearman
```{r, warning=FALSE}
# filter data to only include intercepts and BPRS variables
dat_cor_comb_pt_v2 <- dat_ddm_comb_intc_pt %>% 
  select(v_sum, a_sum, t_sum, z_sum, bprs_pos_ws, bprs_neg_ws, bprs_disorg_ws)

# Remove rows with all NA
dat_cor_comb_pt_v2 <- dat_cor_comb_pt_v2[rowSums(is.na(dat_cor_comb_pt_v2)) < ncol(dat_cor_comb_pt_v2), ]

# Compute Spearman correlation matrix
cor_matrix_v5 <- cor(dat_cor_comb_pt_v2, use = "pairwise.complete.obs", method = "spearman")

# Rename for plotting
colnames(cor_matrix_v5) <- c("v", "a", "t", "w", "Positive", "Negative", "Disorganized")
rownames(cor_matrix_v5) <- c("v", "a", "t", "w", "Positive", "Negative", "Disorganized")
# 
# # Create p-value matrix for Spearman
# n <- ncol(dat_cor_comb_pt)
# p_values <- matrix(NA, n, n)
# colnames(p_values) <- colnames(cor_matrix_v5)
# rownames(p_values) <- rownames(cor_matrix_v5)
# 
# for (i in 1:(n - 1)) {
#   for (j in (i + 1):n) {
#     test <- cor.test(dat_cor_comb_pt[[i]], dat_cor_comb_pt[[j]], method = "spearman")
#     p_values[i, j] <- test$p.value
#     p_values[j, i] <- test$p.value
#   }
#   p_values[i, i] <- 0
# }
# p_values[n, n] <- 0  # Diagonal last cell

# Number of variables
n <- ncol(dat_cor_comb_pt_v2)
# Initialize p-value matrix
p_matrix_v5 <- matrix(NA, n, n)
colnames(p_matrix_v5) <- colnames(cor_matrix_v5)
rownames(p_matrix_v5) <- colnames(cor_matrix_v5)

# Loop through all unique variable pairs
for (i in 1:(n - 1)) {
  for (j in (i + 1):n) {
    x <- dat_cor_comb_pt_v2[[i]]
    y <- dat_cor_comb_pt_v2[[j]]
    valid_idx <- complete.cases(x, y)
    
    if (sum(valid_idx) >= 3) {
      test <- cor.test(x[valid_idx], y[valid_idx], method = "spearman")
      p_matrix_v5[i, j] <- test$p.value
      p_matrix_v5[j, i] <- test$p.value
    } else {
      p_matrix_v5[i, j] <- NA
      p_matrix_v5[j, i] <- NA
    }
  }
  p_matrix_v5[i, i] <- 0
}
p_matrix_v5[n, n] <- 0

print("spearman rho")
print(cor_matrix_v5)
print("spearman p")
print(p_matrix_v5)

# Plot Spearman correlation matrix with significance masking
library(corrplot)
corrplot(cor_matrix_v5,
         method = "color",
         p.mat = p_values,
         sig.level = 0.05,
         insig = "blank",
         addCoef.col = 'grey45',
         tl.cex = 1,
         tl.col = "black",
         number.cex = 1,
         title = "Spearman Correlations of Parameters and BPRS",
         mar = c(1, 1, 2, 1))

```


```{r}
# write function for correlations
cor_sxs <- function(dat, var) {
  cor.test(dat$mean, dat[[var]], method = "spearman")
}

# # create subsets for v-AX
v_dat_all_pt_AX <- filter(v_dat_all_pt, cttype == "AX")
# v_dat_BL1_pt_AX <- filter(v_dat_all_pt, cttype == "AX" & visit == "BL1")
# v_dat_BL2_pt_AX <- filter(v_dat_all_pt, cttype == "AX" & visit == "BL2")
# 
# # create subsets for v-AY
v_dat_all_pt_AY <- filter(v_dat_all_pt, cttype == "AY")
# v_dat_BL1_pt_AY <- filter(v_dat_all_pt, cttype == "AY" & visit == "BL1")
# v_dat_BL2_pt_AY <- filter(v_dat_all_pt, cttype == "AY" & visit == "BL2")
# 
# # create subsets for v-BX
v_dat_all_pt_BX <- filter(v_dat_all_pt, cttype == "BX")
# v_dat_BL1_pt_BX <- filter(v_dat_all_pt, cttype == "BX" & visit == "BL1")
# v_dat_BL2_pt_BX <- filter(v_dat_all_pt, cttype == "BX" & visit == "BL2")
# 
# # create subsets for v-BY
v_dat_all_pt_BY <- filter(v_dat_all_pt, cttype == "BY")
# v_dat_BL1_pt_BY <- filter(v_dat_all_pt, cttype == "BY" & visit == "BL1")
# v_dat_BL2_pt_BY <- filter(v_dat_all_pt, cttype == "BY" & visit == "BL2")
```

```{r}
# v-AX - BPRS
# cor_sxs(v_dat_all_pt_AX, "bprs_pos_ws")
cor_sxs(v_dat_all_pt_AX, "bprs_neg_ws")
# cor_sxs(v_dat_all_pt_AX, "bprs_disorg_ws")
# cor_sxs(v_dat_all_pt_AX, "bprs_dep_anx_ws")
# cor_sxs(v_dat_all_pt_AX, "bprs_mania_ws")
# # BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
# cor_sxs(v_dat_BL1_pt_AX, "bprs_neg_ws")
# cor_sxs(v_dat_BL2_pt_AX, "bprs_neg_ws")
# 

# v-AY - BPRS
cor_sxs(v_dat_all_pt_AY, "bprs_neg_ws")

# # v-BX - BPRS
# cor_sxs(v_dat_all_pt_BX, "bprs_pos_ws")
cor_sxs(v_dat_all_pt_BX, "bprs_neg_ws")
# cor_sxs(v_dat_all_pt_BX, "bprs_disorg_ws")
# cor_sxs(v_dat_all_pt_BX, "bprs_dep_anx_ws")
# cor_sxs(v_dat_all_pt_BX, "bprs_mania_ws")
# # BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
# cor_sxs(v_dat_BL1_pt_BX, "bprs_neg_ws")
# cor_sxs(v_dat_BL2_pt_BX, "bprs_neg_ws")
# 
# # v-BY - BPRS
# cor_sxs(v_dat_all_pt_BY, "bprs_pos_ws")
cor_sxs(v_dat_all_pt_BY, "bprs_neg_ws")
# cor_sxs(v_dat_all_pt_BY, "bprs_disorg_ws")
# cor_sxs(v_dat_all_pt_BY, "bprs_dep_anx_ws")
# cor_sxs(v_dat_all_pt_BY, "bprs_mania_ws")
# # BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
# cor_sxs(v_dat_BL1_pt_BY, "bprs_neg_ws")
# cor_sxs(v_dat_BL2_pt_BY, "bprs_neg_ws")
```

```{r}
# # v-AX - SANS-SAPS
# cor_sxs(v_dat_all_pt_AX, "sanssaps_pos_tib2")
# cor_sxs(v_dat_all_pt_AX, "sanssaps_neg_tib2")
# cor_sxs(v_dat_all_pt_AX, "sanssaps_disorg_tib2")
# # BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
# cor_sxs(v_dat_BL1_pt_AX, "sanssaps_neg_tib2")
# cor_sxs(v_dat_BL2_pt_AX, "sanssaps_neg_tib2")
# 
# # v-BX - SANS-SAPS
# cor_sxs(v_dat_all_pt_BX, "sanssaps_pos_tib2")
# cor_sxs(v_dat_all_pt_BX, "sanssaps_neg_tib2")
# cor_sxs(v_dat_all_pt_BX, "sanssaps_disorg_tib2")
# # BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
# cor_sxs(v_dat_BL1_pt_BX, "sanssaps_neg_tib2")
# cor_sxs(v_dat_BL2_pt_BX, "sanssaps_neg_tib2")
# 
# # # v-BY - SANS-SAPS
# cor_sxs(v_dat_all_pt_BY, "sanssaps_pos_tib2")
# cor_sxs(v_dat_all_pt_BY, "sanssaps_neg_tib2")
# cor_sxs(v_dat_all_pt_BY, "sanssaps_disorg_tib2")
# # BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
# cor_sxs(v_dat_BL1_pt_BY, "sanssaps_neg_tib2")
# cor_sxs(v_dat_BL2_pt_BY, "sanssaps_neg_tib2")
# 
# 
# plot_vbx_neg <- ggplot(v_dat_BL1_pt_BX, aes(x = bprs_neg_ws, y = mean, color = group)) +
#   geom_point() +
#   geom_smooth(method = "lm", se = FALSE, color = "black") +
#   scale_color_manual(values=c("#AA8829"),
#                        labels=c("EP")) + 
#   labs( title = "",
#     x = "BPRS Negative Symptoms",
#     y = "BX Drift Rates (v-BX)") +
#       theme(panel.grid.major = element_blank(), 
#           panel.grid.minor = element_blank(),
#           panel.background = element_blank(), 
#           axis.line = element_line(colour = "black"), 
#           axis.text = element_text(face="bold", size = 14),
#           axis.title = element_text(face="bold", size = 16),
#           legend.text = element_text(face="bold", size = 14),
#           legend.title = element_text(face = "bold", size = 16),
#           plot.title = element_text(face = "bold", size = 22))
# plot_vbx_neg
# 
# ggsave(paste0("graphs/clinical/", format(Sys.Date(), "%Y%m%d"), "_vBX_BPRSneg.png"),
#        plot_vbx_neg, width = 6, height = 4)

```

# days between visits
```{r}
dat_topx_AX <- filter(dat_topx_all, cttype == "AX")
dat_ddm_AX <- filter(dat_ddm_all, parameter == "v" & cttype == "AX")
dat_topx_AX <- subset(dat_topx_AX, (subj_idx %in% dat_ddm_AX$subj_idx))

dat_topx_AX$date <- gsub("_comb", "", dat_topx_AX$date)

dates <- dat_topx_AX %>%
  select(subj_idx, visit, date)

dates <- pivot_wider(dates, id_cols = subj_idx, values_from = date, names_from = visit)

dates$BL1 <- as.Date(dates$BL1, format = "%Y%m%d")
dates$BL2 <- as.Date(dates$BL2, format = "%Y%m%d")

dates$diff <- dates$BL2 - dates$BL1

mean(dates$diff)
sd(dates$diff)
median(dates$diff)
IQR(dates$diff)
```

# descriptives
```{r}
### error descriptives ----------
errTable <- dat_topx_all %>% 
  group_by(group, visit, cttype) %>%
  summarise(
    error_mean = round(mean(error, na.rm = TRUE),2),
    error_sd = round(sd(error, na.rm = TRUE),2))
errTable

### rt descriptives ----------
rtTable <- dat_topx_all %>% 
  group_by(group, visit, cttype) %>%
  summarise(
    rt_mdn_mean = round(mean(rt_mdn, na.rm = TRUE),0),
    rt_mdn_sd = round(sd(rt_mdn, na.rm = TRUE),0))
rtTable

#### d' descriptives ----------
dTable <- dat_dprime_all %>% 
  group_by(group, visit) %>%
  summarise(
    d_con_mean = round(mean(d_context, na.rm = TRUE),2),
    d_con_sd = round(sd(d_context, na.rm = TRUE),2),
    d_exp_mean = round(mean(d_expect, na.rm = TRUE),2),
    d_exp_sd = round(sd(d_expect, na.rm = TRUE),2))
dTable

## ddm descriptives ----------
ddmTable <- dat_ddm_behav %>% 
  group_by(group, visit, parameter, cttype) %>%
  summarise(
    param_mean = round(mean(mean, na.rm = TRUE),2),
    param_sd = round(sd(mean, na.rm = TRUE),2))
ddmTable

ddmTable_bl1 <- dat_ddm_bl1 %>% 
  group_by(group, parameter, cttype) %>%
  summarise(
    param_mean = round(mean(mean, na.rm = TRUE),2),
    param_sd = round(sd(mean, na.rm = TRUE),2))
ddmTable_bl1

ddmTable_bl2 <- dat_ddm_bl2 %>% 
  group_by(group, parameter, cttype) %>%
  summarise(
    param_mean = round(mean(mean, na.rm = TRUE),2),
    param_sd = round(sd(mean, na.rm = TRUE),2))
ddmTable_bl2
```

