---
title: "ddm_update"
author: "Jessica Arend"
date: "2025-02-21"
output: html_document
---

# prep data
## clear space & load packages
```{r}
# clear workspace
rm(list=ls())

# read in packages
pacman::p_load(stats, stringr, dplyr, tidyr, ggplot2, lme4, emmeans, lmerTest, Matrix, pbkrtest, psych, car, performance, parameters, xgboost, SHAPforxgboost, stats, corrplot)
```

## load DDM (hssm) data
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data <- function(block, types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_mri_ddm/data/20241206_ddm_data/", block, "/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]]))
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = toupper(block), .after = participant_id)
}

# Column mappings for different file types
column_mappings <- list(
  v = c("participant_id", "v_ax", "v_ay", "v_bx", "v_by"),
  a = c("participant_id", "a_ax", "a_ay", "a_bx", "a_by"),
  t = c("participant_id", "t_ax", "t_ay", "t_bx", "t_by"),
  z = c("participant_id", "z_a", "z_b")
)

# Process data for each block
types <- names(column_mappings)
dat_ddm_bl1 <- process_data("bl1", types, column_mappings)
dat_ddm_bl2 <- process_data("bl2", types, column_mappings)

# Filter to retain only common participant_ids
common_ids <- intersect(dat_ddm_bl1$participant_id, dat_ddm_bl2$participant_id)
dat_ddm_bl1 <- filter(dat_ddm_bl1, participant_id %in% common_ids)
dat_ddm_bl2 <- filter(dat_ddm_bl2, participant_id %in% common_ids)

# Combine both datasets
dat_ddm_all <- bind_rows(dat_ddm_bl1, dat_ddm_bl2)

dat_ddm_all_long <- dat_ddm_all

# Rename, pivot, and add `subj_type` column
dat_ddm_all <- dat_ddm_all %>%
  rename(subj_idx = participant_id) %>%
  pivot_longer(
    cols = c(v_ax, v_ay, v_bx, v_by, a_ax, a_ay, a_bx, a_by, 
             t_ax, t_ay, t_bx, t_by, z_a, z_b),
    names_to = c("parameter", "cttype"), 
    names_sep = "_", 
    values_to = "mean"
  ) %>%
  mutate(
    group = case_when(
      str_sub(subj_idx, 1, 3) == "SP1" ~ "Control",
      str_sub(subj_idx, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ NA
    )
  )

# rename trials
dat_ddm_all <- dat_ddm_all %>% 
  mutate(cttype = case_when(cttype == "ax" ~ "AX",
                             cttype == "ay" ~ "AY",
                             cttype == "bx" ~ "BX", 
                             cttype == "by" ~ "BY",
                             cttype == "a" ~ "A",
                             cttype == "b" ~ "B",
                             TRUE ~ cttype))

dat_ddm_all <- filter(dat_ddm_all, subj_idx != "SP1051")
dat_ddm_bl1 <- filter(dat_ddm_all, visit == "BL1")
dat_ddm_bl2 <- filter(dat_ddm_all, visit == "BL2")
```

## clean/reformat DDM data
```{r}
# filter out SP1051, which does not have all parameters at BL2
dat_ddm_bl1 <- filter(dat_ddm_bl1, subj_idx != "SP1051")
dat_ddm_bl2 <- filter(dat_ddm_bl2, subj_idx != "SP1051")

## match BL1 to BL2 DDM 
dat_ddm_bl1 <- subset(dat_ddm_bl1, (subj_idx %in% dat_ddm_bl2$subj_idx))
dat_ddm_bl2 <- subset(dat_ddm_bl2, (subj_idx %in% dat_ddm_bl1$subj_idx))


# add z-scores
calc_z_score <- function(x) {
  (x - mean(x)) / sd(x)
}

# Create the new variable "mean_z" using group_by and mutate
dat_ddm_all <- dat_ddm_all %>%
  group_by(parameter, cttype, visit, group) %>%
  mutate(mean_z = calc_z_score(mean))
```

## save list of DDM subj
```{r}
# save list of DDM subject IDs
# write.csv( data.frame(subj = unique(dat_ddm_all$subj_idx)), file = file.path("data", paste0("topx_ddm_sample_subjx_", format(Sys.Date(), "%Y%m%d"), ".csv")), row.names = FALSE)
```

## load TOPX data
```{r}
### TOPX data ----------
dat_topx <- read.csv("../topx_mri_clean/aggregate_data/aggregate_topx_20250125.csv")

# clean and rename
dat_topx[dat_topx == "BL1.5"] <- "BL1"
dat_topx[dat_topx == "BL2.5"] <- "BL2"
dat_topx[dat_topx == "6M.5"] <- "6M"
dat_topx[dat_topx == "7M.5"] <- "7M"
dat_topx[dat_topx == "12M.5"] <- "12M"

dat_topx <- dat_topx %>%
  rename(subj_idx = subj) %>% 
  rename(group = subj_type) %>% 
  rename(cttype = trial_type)

## Baseline 1
dat_topx_bl1 <- dat_topx %>% 
  filter(visit == "BL1") 

## Baseline 2
dat_topx_bl2 <- dat_topx %>% 
  filter(visit == "BL2") 

## 6-Month
dat_6m_topx <- dat_topx %>% 
  filter(visit == "6M") 

## match BL1 to BL2 TOPX 
dat_topx_bl1 <- subset(dat_topx_bl1, (subj_idx %in% dat_topx_bl2$subj_idx))
dat_topx_bl2 <- subset(dat_topx_bl2, (subj_idx %in% dat_topx_bl1$subj_idx))

## merge TOPX data
dat_topx_all <- rbind(dat_topx_bl1, dat_topx_bl2)

# remove TOPX data if not in DDM
dat_topx_all <- subset(dat_topx_all, (subj_idx %in% dat_ddm_all$subj_idx))
```

## load behav data
```{r}
dat_behav <- read.csv("data/step_behav_dat_20250222.csv")
colnames(dat_behav)[1] <- "subj_idx"
```

## combine all data
```{r}
# Merge DDM + behav data --------
dat_ddm_behav = merge(dat_ddm_all, dat_behav, by = c("subj_idx","group"), all.x = TRUE)

# Merge TOPX + behav data --------
dat_topx_behav = merge(dat_topx_all, dat_behav, by = c("subj_idx","group"), all.x = TRUE)
```

# Observed analyses
## error w/ visit
```{r}
### BL-Comb Error LMER w visit-----------
mod_errC <- lmer(error ~ group * cttype * visit + (1|subj_idx) + age + gender, data = dat_topx_behav)
anova(mod_errC, type = 3)
print(summary(mod_errC))
print(emmeans(mod_errC, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ visit), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ cttype|group), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ group|visit), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ visit|group), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ cttype|visit), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ visit|cttype), adjust = "mvt"))



### BL-Comb Error*Visit Graph  ----------
plot_err_sep <- ggplot(dat_topx_all, 
                        aes(x= cttype, y=error, group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Error Rates", 
       y = "Error Rate", 
       x = "Trial Type", 
       color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(0.05, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_sep

#ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_Error_Sep.png"), plot_err_sep, width = 6, height = 4)
```

## error w/o visit
```{r}
### BL-Comb Error LMER wo visit
mod_errC <- lmer(error ~ group * cttype + (1|subj_idx) + age + gender, data = dat_topx_behav)
anova(mod_errC, type = 3)
summary(mod_errC)
print(emmeans(mod_errC, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_errC, list(pairwise ~ cttype|group), adjust = "mvt"))

# plot with single line for BL-Comb
plot_err_comb <- ggplot(dat_topx_all, 
                        aes(x= cttype, y=error, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Error Rates", 
       y = "Error Rate", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.05, .35)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_comb

#ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_Error_Comb.png"), plot_err_comb, width = 6, height = 4)
```


## calculate d'
```{r}
## create df with  1 row/set of d-primes per subj, picked AX at random. And create numeric value for subj type
dat_dprime_all <- dat_topx_behav %>% 
  filter(cttype == "AX") %>% 
  mutate(group_n = ifelse(group=="Control", 0, 1))

# create long form of data - needed for graphs
dat_dprime_all_long <- dat_dprime_all %>% 
  select(subj_idx, visit, group, d_context, d_expect, age, gender) %>% 
  pivot_longer(
    cols = c(d_context, d_expect),
    names_to = "dprime_type",
    values_to = "dprime")

# ## create dataframes with only BL1/only BL2 dat - long
# dat_dprime_bl1_long <- dat_dprime_all_long %>% 
#   filter(visit == "BL1")
# dat_dprime_bl2_long <- dat_dprime_all_long %>% 
#   filter(visit == "BL2")
# 
# ## create dataframes with only BL1/only BL2 dat - wide
# dat_dprime_bl1 <- dat_dprime_all %>% filter(visit == "BL1")
# dat_dprime_bl2 <- dat_dprime_all %>% filter(visit == "BL2")
```


## d' w/ visit
```{r}
#### d'comb LMER w visit -----
mod_dprime <- lmer(dprime ~ group * dprime_type * visit + (1|subj_idx) + age + gender, data = dat_dprime_all_long)
anova(mod_dprime, type = 3)
print(emmeans(mod_dprime, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ dprime_type), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ visit), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ group|dprime_type), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ dprime_type|group), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ dprime_type|visit), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ visit|dprime_type), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ group|dprime_type|visit), adjust = "mvt"))
#check_model(mod_dprime)

plot_dprime_sep <- ggplot(dat_dprime_all_long, 
                             aes(x= dprime_type, y=dprime, 
                                 group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit),
               position = position_dodge(width = 0.1),
               linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group),
               position = position_dodge(width = 0.1), 
               size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               position = position_dodge(width = 0.1),
               width = 0.2, size = 1) + 
  labs(title = "D-primes (d')", 
       y = "d' Value", 
       x = "d' Type", color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(2.0, 3.5)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) + 
  scale_x_discrete(labels = c("d_context" = "d' Context", 
                              "d_expect" = "d' Expectancy")) +
  scale_y_continuous(breaks = c(seq(2.0, 3.5, by = 0.25)),
                     labels = c("2.0","", "2.5", "", "3.0", "", "3.5")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_dprime_sep

# ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_Dprime_Sep.png"), plot_dprime_sep, width = 6, height = 4)
```

##d' w/o visit
```{r}
#### d'comb LMER wo visit -----
mod_dprime <- lmer(dprime ~ group * dprime_type + (1|subj_idx) + age + gender, data = dat_dprime_all_long)
anova(mod_dprime, type = 3)
print(emmeans(mod_dprime, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ dprime_type), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ group|dprime_type), adjust = "mvt"))
print(emmeans(mod_dprime, list(pairwise ~ dprime_type|group), adjust = "mvt"))
#check_model(mod_dprime)

plot_dprime_comb <- ggplot(dat_dprime_all_long, 
                          aes(x= dprime_type, y=dprime, 
                              group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group),
               linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group),
               width = 0.05, size = 1) + 
  labs(title = "D-prime (d') Statistics", 
       y = "d' Value", 
       x = "d' Type", color = "Group") +
  coord_cartesian(ylim = c(2.0, 3.5)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_x_discrete(labels = c("d_context" = "d' Context", 
                              "d_expect" = "d' Expectancy")) +
  scale_y_continuous(breaks = c(seq(2.0, 3.5, by = 0.25)),
                     labels = c("2.0","", "2.5", "", "3.0", "", "3.5")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_dprime_comb

# ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_Dprime_Comb.png"), plot_dprime_comb, width = 6, height = 4)
```

## RT w/ visit
```{r}
### BL-Comb RT LMER w visit -----------
mod_rtC <- lmer(rt_mdn ~ group * cttype * visit + (1|subj_idx) + age + gender, data = dat_topx_behav)
anova(mod_rtC, type = 3)
summary(mod_rtC)
print(emmeans(mod_rtC, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ visit), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ cttype|group), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ group|visit), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ visit|group), adjust = "mvt"))

### BL-Comb RT*Visit Graph ----------
plot_rt_sep <- ggplot(dat_topx_all, 
                       aes(x= cttype, y=rt_mdn, 
                           group = interaction(group,visit))) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group, linetype = visit), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Reaction Times (RT)", 
       y = "RT (ms)", 
       x = "Trial Type", color = "Group", linetype = "Visit") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  scale_linetype_manual(values = c("solid", "dotted"), 
                        labels = c("Visit 1", "Visit 2")) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_sep

#ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_RT_Sep.png"), plot_rt_sep, width = 6, height = 4)
```

## RT w/o visit
```{r}
### BL-Comb RT LMER wo visit
mod_rtC <- lmer(rt_mdn ~ group * cttype + (1|subj_idx) + age + gender, data = dat_topx_behav)
anova(mod_rtC, type = 3)
summary(mod_rtC)
print(emmeans(mod_rtC, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_rtC, list(pairwise ~ cttype|group), adjust = "mvt"))

plot_rt_comb <- ggplot(dat_topx_all, 
                       aes(x= cttype, y=rt_mdn, group = group)) + 
  stat_summary(fun="mean", geom="line", 
               aes(color = group), linewidth = 1.5) + 
  stat_summary(fun="mean", geom="point", aes(color = group), size = 3) + 
  stat_summary(fun.data = mean_se, geom = "errorbar", aes(color = group), 
               width = 0.1, size = 1) + 
  labs(title = "Reaction Times (RT)", 
       y = "RT (ms)", 
       x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_comb

#ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_RT_Comb.png"), plot_rt_comb, width = 6, height = 4)
```

### investigate age
```{r}
# investigate age
dat_topx_behav <- dat_topx_behav %>%
  mutate(age_split = ifelse(age >= median(age), 1, 0)) %>% 
  mutate(age_split = as.numeric(age_split))

table(dat_topx_behav$age_split)/8

dat_topx_behav %>%
  group_by(age_split) %>%
  summarize(mean_rt_mdn = mean(rt_mdn, na.rm = TRUE))

t.test(dat_topx_behav$age_split, dat_topx_behav$rt_mdn, na.rm = TRUE)

mod_rtAge <- lmer(rt_mdn ~ age_split * cttype * visit + (1|subj_idx), data = dat_topx_behav)
anova(mod_rtAge)
```

# Modeled analyses
## ddm functions
```{r}
### write DDM LMER functions ---------------------
# lmer without visit, plot without visit
lmer_plot_comb <- function(dat, title_lab, param_lab, ymin, ymax, posthoc = FALSE) {
  model <- lmer(mean ~ group * cttype + (1|subj_idx) + age + gender, dat)
  print(anova(model, type = 3))
  if(posthoc == TRUE) {
    print(emmeans(model, list(pairwise ~ group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|group), adjust = "mvt"))
    }
  plot <- ggplot(dat, aes(x= cttype, y=mean, group = group)) + 
    stat_summary(fun="mean", geom="line", aes(color = group), linewidth = 1.5) + 
    stat_summary(fun="mean", geom="point", aes(color = group), size = 3) +
    stat_summary(fun.data = mean_se, geom = "errorbar", 
                 aes(color = group), width = 0.1, 
                 size = 1) + 
    labs(title = title_lab, y = param_lab, 
         x = "Trial Type", color = "Group") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    scale_color_manual(values=c("#2C737F", "#AA8829"),
                       labels=c("Ctl", "EP")) + 
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"), 
          axis.text = element_text(face="bold", size = 16),
          axis.title = element_text(face="bold", size = 20),
          legend.text = element_text(face="bold", size = 14),
          legend.title = element_text(face = "bold", size = 16),
          plot.title = element_text(face = "bold", size = 22))
  print(plot)
  #ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_", title_lab, "_Comb.png"), plot, width = 6, height = 4)
}

# lmer and plot with visit
lmer_plot_sep <- function(dat, title_lab, param_lab, ymin, ymax, posthoc = FALSE) {
  model <- lmer(mean ~ group * cttype * visit + (1|subj_idx) + age + gender, dat)
  print(anova(model, type = 3))
  if(posthoc == TRUE) {
    print(emmeans(model, list(pairwise ~ group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit|group), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit|cttype), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ group|cttype|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ cttype|group|visit), adjust = "mvt"))
    print(emmeans(model, list(pairwise ~ visit|group|cttype), adjust = "mvt"))

  }
  plot <- ggplot(dat, aes(x= cttype, y=mean, 
                   group = interaction(group,visit))) + 
    stat_summary(fun="mean", geom="line", 
                 aes(color = group, linetype = visit), size = 1.5) + 
    stat_summary(fun="mean", geom="point", aes(color = group), size = 3) +
    stat_summary(fun.data = mean_se, geom = "errorbar", 
                 aes(color = group), width = 0.1, 
                 size = 1) + 
    labs(title = title_lab, y = param_lab, 
         x = "Trial Type", color = "Group", linetype = "Visit") +
    coord_cartesian(ylim = c(ymin, ymax)) +
    scale_color_manual(values=c("#2C737F", "#AA8829"),
                       labels=c("Ctl", "EP")) + 
    scale_linetype_manual(values = c("solid", "dotted"), 
                          labels = c("Visit 1", "Visit 2")) + 
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"), 
          axis.text = element_text(face="bold", size = 16),
          axis.title = element_text(face="bold", size = 20),
          legend.text = element_text(face="bold", size = 14),
          legend.title = element_text(face = "bold", size = 16),
          plot.title = element_text(face = "bold", size = 22))
  print(plot)
  #ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_", title_lab, "_Sep.png"), plot, width = 6, height = 4)
}
```

## transform and subset ddm data
```{r}
# transform drift rates ---------
reformat_ddm_var <- function(data) {
data[data$cttype == "AY" & data$parameter == "v",]$mean <- (-1) * data[data$cttype == "AY" & data$parameter == "v",]$mean
return(as.data.frame(data))
}

dat_ddm_behav <- reformat_ddm_var(dat_ddm_behav)
#write.csv(dat_ddm_behav,file=paste0("/Users/arend103/Documents/UMN Work & General/TOPX analyses/mri ddm data/TOPX_ddm_behav_",gsub("-", "", Sys.Date()), ".csv"), row.names = FALSE)

# subset data by parameter ---------------------
v_dat_all = filter(dat_ddm_behav, parameter == 'v')

a_dat_all = filter(dat_ddm_behav, parameter == 'a')

t_dat_all = filter(dat_ddm_behav, parameter == 't')

z_dat_all= filter(dat_ddm_behav, parameter == 'z') 
# z_dat_all_trans <- z_dat_all %>%  mutate(mean = mean*(-1))

### DDM descriptives ----------
ddmTable <- dat_ddm_behav %>% 
  group_by(group, visit, parameter, cttype) %>%
  summarise(
    param_mean = round(mean(mean, na.rm = TRUE),2),
    param_sd = round(sd(mean, na.rm = TRUE),2))
ddmTable
```

## drift rate comb
```{r}
## run plots -----------
# v - all data
lmer_plot_comb(v_dat_all, "Drift Rates", 
           "Drift Rate (v)", 0.5, 3.5, posthoc = TRUE)
```

# drift rate sep
```{r}
lmer_plot_sep(v_dat_all, 
                "Drift Rates", 
                 "Drift Rate (v)", 0.5, 3.5, posthoc = TRUE)
```

## decision threshold comb
```{r}
# a - all data
lmer_plot_comb(a_dat_all, "Decision Thresholds", 
           "Decision Threshold (a)", 0.4, 0.7, posthoc = TRUE) 
```

## decision threshold sep
```{r}
lmer_plot_sep(a_dat_all, "Decision Thresholds",
                 "Decision Threshold (a)", 0.4, 0.7, posthoc = TRUE) 
```

### investigate age
```{r}
a_dat_all <- a_dat_all %>%
  mutate(age_split = ifelse(age >= median(age), 1, 0)) %>% 
  mutate(age_split = as.numeric(age_split))

a_dat_all %>%
  group_by(age_split) %>%
  summarize(mean = mean(mean, na.rm = TRUE))

t.test(a_dat_all$age_split, a_dat_all$mean, na.rm = TRUE)

mod_a_Age <- lmer(mean ~ age_split * cttype * visit + (1|subj_idx), data = a_dat_all)
anova(mod_a_Age)

# ggplot(a_dat_all, aes(x = age_split, y = mean)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Age", y = "Decision threshold", title = "1 = older, 0 = younger")

```

## non-decision time comb
```{r}
# t - all data
lmer_plot_comb(t_dat_all, "Non-Decision Times", 
           "Non-Decision Time (t)", 0.15, 0.30, posthoc = TRUE) 
```

## non-decision time sep
```{r}
lmer_plot_sep(t_dat_all, "Non-Decision Times", 
                 "Non-Decision Time (t)", 0.15, 0.30, posthoc = TRUE)
```

### investigate age
```{r}
# investigate age
t_dat_all <- t_dat_all %>%
  mutate(age_split = ifelse(age >= median(age), 1, 0)) %>% 
  mutate(age_split = as.numeric(age_split))

t.test(t_dat_all$age_split, t_dat_all$mean, na.rm = TRUE)

# ggplot(t_dat_all, aes(x = age_split, y = mean)) +
#   geom_bar(stat = "identity") +
#   labs(x = "Age", y = "Non-decision time", title = "1 = older, 0 = younger")
```

## bias comb
```{r}
# z - all data
lmer_plot_comb(z_dat_all, "Degrees of Bias", 
           "Degree of Bias (w)", 0.4, 0.7, posthoc = TRUE) 
```

# bias sep
```{r}
lmer_plot_sep(z_dat_all, "Degrees of Bias", 
                 "Degree of Bias (w)", 0.4, 0.7, posthoc = TRUE)

# investigate gender
# z_dat_all_trans$gender <- as.factor(z_dat_all_trans$gender)
# anova_result <- aov(mean ~ gender, data = z_dat_all_trans)
# summary(anova_result)
# TukeyHSD(anova_result) # 1 = woman, 2 = man, 3 = enby/other
```

# correlations - 14 param
## ddm matrix - all
```{r}
# filter ddm data (long form) to only include ddm variables, for correlation matrix
dat_cor_all <- dat_ddm_all_long %>% 
  select(-c(participant_id, visit))

# run the correlations
dat_cor_all <- cor(dat_cor_all)

# plot a correlation matrix
corrplot(dat_cor_all, method = "color", addCoef.col = 'white')
```

## ddm matrix - bl1
```{r}
dat_ddm_bl1_long <- dat_ddm_all_long %>% 
  filter(visit == "BL1")

dat_cor_bl1 <- dat_ddm_bl1_long %>% 
  select(-c(participant_id, visit))

dat_cor_bl1 <- cor(dat_cor_bl1)
corrplot(dat_cor_bl1, method = "color", addCoef.col = 'white')
  
```

## ddm matrix - bl2
```{r}
dat_ddm_bl2_long <- dat_ddm_all_long %>% 
  filter(visit == "BL2")

dat_cor_bl2 <- dat_ddm_bl2_long %>% 
  select(-c(participant_id, visit))

dat_cor_bl2 <- cor(dat_cor_bl2)
corrplot(dat_cor_bl2, method = "color", addCoef.col = 'white')

```

# correlations - 4 param
## calculate intercepts
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data_intc <- function(block, types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_mri_ddm/data/20241206_ddm_data/", block, "/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]])) %>%
      rename(!!paste0(type, "_ppt") := participant)
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = toupper(block), .after = participant_id)
}

# Column mappings for different file types
column_mappings_intc <- list(
  v = c("participant_id", "v_intc", "participant"),
  a = c("participant_id", "a_intc", "participant"),
  t = c("participant_id", "t_intc", "participant"),
  z = c("participant_id", "z_intc", "participant")
)

# Process data for each block
types_intc <- names(column_mappings_intc)
dat_ddm_bl1_intc <- process_data_intc("bl1", types_intc, column_mappings_intc)
dat_ddm_bl2_intc <- process_data_intc("bl2", types_intc, column_mappings_intc)


# Filter to retain only common participant_ids
common_ids_intc <- intersect(dat_ddm_bl1_intc$participant_id, dat_ddm_bl2_intc$participant_id)
dat_ddm_bl1_intc <- filter(dat_ddm_bl1_intc, participant_id %in% common_ids)
dat_ddm_bl2_intc <- filter(dat_ddm_bl2_intc, participant_id %in% common_ids)

# Combine both datasets
dat_ddm_all_intc <- bind_rows(dat_ddm_bl1_intc, dat_ddm_bl2_intc)
```

## ddm intc matrix - all
```{r}
dat_cor_all_intc <- dat_ddm_all_intc %>% 
  mutate(v = v_intc + v_ppt,
         a = a_intc + a_ppt,
         t = t_intc + t_ppt,
         z = z_intc + z_ppt) %>% 
  select(v, a, t, z)

dat_cor_all_intc <- cor(dat_cor_all_intc)
corrplot(dat_cor_all_intc, method = "color", addCoef.col = 'white')
```

## ddm intc matrix - bl1
```{r}
dat_cor_bl1_intc <- dat_ddm_bl1_intc %>% 
  mutate(v = v_intc + v_ppt,
         a = a_intc + a_ppt,
         t = t_intc + t_ppt,
         z = z_intc + z_ppt) %>% 
  select(v, a, t, z)

dat_cor_bl1_intc <- cor(dat_cor_bl1_intc)
corrplot(dat_cor_bl1_intc, method = "color", addCoef.col = 'white')
```

## ddm intc matrix - bl2
```{r}
dat_cor_bl2_intc <- dat_ddm_bl2_intc %>% 
  mutate(v = v_intc + v_ppt,
         a = a_intc + a_ppt,
         t = t_intc + t_ppt,
         z = z_intc + z_ppt) %>% 
  select(v, a, t, z)

dat_cor_bl2_intc <- cor(dat_cor_bl2_intc)
corrplot(dat_cor_bl2_intc, method = "color", addCoef.col = 'white')
```

# clinical sxs & ddm
```{r}
# write function for correlations
cor_sxs <- function(dat, var) {
  cor.test(dat$mean, dat[[var]], method = "spearman")
}

# filter data to include drift rate only
v_dat_all_pt = filter(dat_ddm_behav, parameter == 'v' & group == "Patient")

# create subsets for v-AX
v_dat_all_pt_AX <- filter(v_dat_all_pt, cttype == "AX")
v_dat_BL1_pt_AX <- filter(v_dat_all_pt, cttype == "AX" & visit == "BL1")
v_dat_BL2_pt_AX <- filter(v_dat_all_pt, cttype == "AX" & visit == "BL2")

# create subsets for v-BX
v_dat_all_pt_BX <- filter(v_dat_all_pt, cttype == "BX")
v_dat_BL1_pt_BX <- filter(v_dat_all_pt, cttype == "BX" & visit == "BL1")
v_dat_BL2_pt_BX <- filter(v_dat_all_pt, cttype == "BX" & visit == "BL2")

# create subsets for v-BY
v_dat_all_pt_BY <- filter(v_dat_all_pt, cttype == "BY")
v_dat_BL1_pt_BY <- filter(v_dat_all_pt, cttype == "BY" & visit == "BL1")
v_dat_BL2_pt_BY <- filter(v_dat_all_pt, cttype == "BY" & visit == "BL2")
```

```{r}
# v-AX - BPRS
cor_sxs(v_dat_all_pt_AX, "bprs_pos_ws")
cor_sxs(v_dat_all_pt_AX, "bprs_neg_ws")
cor_sxs(v_dat_all_pt_AX, "bprs_disorg_ws")
cor_sxs(v_dat_all_pt_AX, "bprs_dep_anx_ws")
cor_sxs(v_dat_all_pt_AX, "bprs_mania_ws")
# BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
cor_sxs(v_dat_BL1_pt_BX, "bprs_neg_ws")
cor_sxs(v_dat_BL2_pt_AX, "bprs_neg_ws")

# v-BX - BPRS
cor_sxs(v_dat_all_pt_BX, "bprs_pos_ws")
cor_sxs(v_dat_all_pt_BX, "bprs_neg_ws")
cor_sxs(v_dat_all_pt_BX, "bprs_disorg_ws")
cor_sxs(v_dat_all_pt_BX, "bprs_dep_anx_ws")
cor_sxs(v_dat_all_pt_BX, "bprs_mania_ws")
# BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
cor_sxs(v_dat_BL1_pt_BX, "bprs_neg_ws")
cor_sxs(v_dat_BL2_pt_BX, "bprs_neg_ws")

# v-BY - BPRS
cor_sxs(v_dat_all_pt_BY, "bprs_pos_ws")
cor_sxs(v_dat_all_pt_BY, "bprs_neg_ws")
cor_sxs(v_dat_all_pt_BY, "bprs_disorg_ws")
cor_sxs(v_dat_all_pt_BY, "bprs_dep_anx_ws")
cor_sxs(v_dat_all_pt_BY, "bprs_mania_ws")
# BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
cor_sxs(v_dat_BL1_pt_BY, "bprs_neg_ws")
cor_sxs(v_dat_BL2_pt_BY, "bprs_neg_ws")
```

```{r}
# v-AX - SANS-SAPS
cor_sxs(v_dat_all_pt_AX, "sanssaps_pos_tib2")
cor_sxs(v_dat_all_pt_AX, "sanssaps_neg_tib2")
cor_sxs(v_dat_all_pt_AX, "sanssaps_disorg_tib2")
# BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
cor_sxs(v_dat_BL1_pt_AX, "sanssaps_neg_tib2")
cor_sxs(v_dat_BL2_pt_AX, "sanssaps_neg_tib2")

# v-BX - SANS-SAPS
cor_sxs(v_dat_all_pt_BX, "sanssaps_pos_tib2")
cor_sxs(v_dat_all_pt_BX, "sanssaps_neg_tib2")
cor_sxs(v_dat_all_pt_BX, "sanssaps_disorg_tib2")
# BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
cor_sxs(v_dat_BL1_pt_BX, "sanssaps_neg_tib2")
cor_sxs(v_dat_BL2_pt_BX, "sanssaps_neg_tib2")

# # v-BY - SANS-SAPS
cor_sxs(v_dat_all_pt_BY, "sanssaps_pos_tib2")
cor_sxs(v_dat_all_pt_BY, "sanssaps_neg_tib2")
cor_sxs(v_dat_all_pt_BY, "sanssaps_disorg_tib2")
# BL1 and BL2 - but keep in mind, comparing 1 BPRS to 2 DDM
cor_sxs(v_dat_BL1_pt_BY, "sanssaps_neg_tib2")
cor_sxs(v_dat_BL2_pt_BY, "sanssaps_neg_tib2")


plot_vbx_neg <- ggplot(v_dat_BL1_pt_BX, aes(x = bprs_neg_ws, y = mean, color = group)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  scale_color_manual(values=c("#AA8829"),
                       labels=c("EP")) + 
  labs( title = "",
    x = "BPRS Negative Symptoms",
    y = "BX Drift Rates (v-BX)") +
      theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          panel.background = element_blank(), 
          axis.line = element_line(colour = "black"), 
          axis.text = element_text(face="bold", size = 14),
          axis.title = element_text(face="bold", size = 16),
          legend.text = element_text(face="bold", size = 14),
          legend.title = element_text(face = "bold", size = 16),
          plot.title = element_text(face = "bold", size = 22))
plot_vbx_neg

#ggsave(paste0("graphs/", format(Sys.Date(), "%Y%m%d"), "_vBX_BPRSneg.png"), plot_vbx_neg, width = 6, height = 4)

```

# days between visits
```{r}
dat_topx_AX <- filter(dat_topx_all, cttype == "AX")
dat_ddm_AX <- filter(dat_ddm_all, parameter == "v" & cttype == "AX")
dat_topx_AX <- subset(dat_topx_AX, (subj_idx %in% dat_ddm_AX$subj_idx))

dat_topx_AX$date <- gsub("_comb", "", dat_topx_AX$date)

dates <- dat_topx_AX %>%
  select(subj_idx, visit, date)

dates <- pivot_wider(dates, id_cols = subj_idx, values_from = date, names_from = visit)

dates$BL1 <- as.Date(dates$BL1, format = "%Y%m%d")
dates$BL2 <- as.Date(dates$BL2, format = "%Y%m%d")

dates$diff <- dates$BL2 - dates$BL1

mean(dates$diff)
median(dates$diff)
sd(dates$diff)
```

# descriptives
```{r}
#### d' descriptives ----------
dTable <- dat_dprime_all %>% 
  group_by(group, visit) %>%
  summarise(
    d_con_mean = round(mean(d_context, na.rm = TRUE),2),
    d_con_sd = round(sd(d_context, na.rm = TRUE),2),
    d_exp_mean = round(mean(d_expect, na.rm = TRUE),2),
    d_exp_sd = round(sd(d_expect, na.rm = TRUE),2))
dTable


### error descriptives ----------
errTable <- dat_topx_all %>% 
  group_by(group, visit, cttype) %>%
  summarise(
    error_mean = round(mean(error, na.rm = TRUE),2),
    error_sd = round(sd(error, na.rm = TRUE),2))
errTable

### rt descriptives ----------
rtTable <- dat_topx_all %>% 
  group_by(group, visit, cttype) %>%
  summarise(
    rt_mdn_mean = round(mean(rt_mdn, na.rm = TRUE),0),
    rt_mdn_sd = round(sd(rt_mdn, na.rm = TRUE),0))
rtTable


## ddm descriptives ----------
ddmTable_bl1 <- dat_ddm_bl1 %>% 
  group_by(group, parameter, cttype) %>%
  summarise(
    param_mean = round(mean(mean, na.rm = TRUE),2),
    param_sd = round(sd(mean, na.rm = TRUE),2))
ddmTable_bl1

ddmTable_bl2 <- dat_ddm_bl2 %>% 
  group_by(group, parameter, cttype) %>%
  summarise(
    param_mean = round(mean(mean, na.rm = TRUE),2),
    param_sd = round(sd(mean, na.rm = TRUE),2))
ddmTable_bl2

```

