---
title: "TOPX_ddm_dlPFC_20241214"
author: "Jessica Arend"
date: "2024-12-14"
output: html_document
---

```{r}
# clear workspace
rm(list=ls())

# read in packages
pacman::p_load(stats, stringr, dplyr, tidyr, ggplot2, lme4, emmeans, lmerTest, Matrix, pbkrtest, psych, purrr)
```

# read in fMRI data
```{r}
dat_mri <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/zstats_schaefer400+Tian_B-A.csv")
dat_mri$sub <- gsub("sub-", "", dat_mri$sub)
dat_mri$ses <- gsub("ses-", "", dat_mri$ses)
colnames(dat_mri)[1] <- "subj"
colnames(dat_mri)[2] <- "visit"
colnames(dat_mri)<-gsub("X17Networks_","",colnames(dat_mri))

# note: names ending in .rh or .lh are Tian parcels, names starting in RH_ or LH_ are Schaefer parcels

dat_mri <- dat_mri %>% 
  mutate(
    group = case_when(
      str_sub(subj, 1, 3) == "SP1" ~ "Control",
      str_sub(subj, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ "UNK"), .after = contrast)

dat_mri_names <- colnames(dat_mri)

# Filter dataset by hemisphere
dat_mri_lh <- dat_mri[, grepl("LH", colnames(dat_mri)) | colnames(dat_mri) %in% c("subj", "visit", "group")]

dat_mri_rh <- dat_mri[, grepl("RH", colnames(dat_mri)) | colnames(dat_mri) %in% c("subj", "visit", "group")]

# this is wrong! schaefer400 <- data.frame(parcelname = colnames(dat_mri), parcelnum = c((1:57), (1:400)))
parcelname <- read.table("~/Documents/2024 Fall/OHBM 2025/schaefer400NodeNames.txt")
colnames(parcelname)[1] <- "parcelname"
schaefer400 <- data.frame(parcelname = parcelname, parcelnum = c (1:400))

# save list of mri subject IDs
mri_sample_subjx <- unique(dat_mri$subj)
mri_sample_subjx <- as.data.frame(mri_sample_subjx)
colnames(mri_sample_subjx)[1] = "subj"
# write.csv(mri_sample_subjx,file=paste0("/Users/arend103/Documents/umn_work/topx_analyses/topx_mri_ddm/topx_mri_sample_subjx_",gsub("-", "", Sys.Date()), ".csv"), row.names = FALSE)
```

# read in DDM data
```{r}
dat_all_ddm <- read.csv("~/Documents/umn_work/topx_analyses/topx_mri_ddm/data/data_20240920/TOPX_ddm_fullmerge_20240920.csv")
colnames(dat_all_ddm)[1] = "subj"

# filter out SP1051, which does not have all parameters at BL2
dat_all_ddm <- filter(dat_all_ddm, subj != "SP1051")

setdiff(dat_all_ddm$subj, dat_mri$subj) # in DDM not MRI
setdiff(dat_mri$subj, dat_all_ddm$subj) # in MRI not DDM

# subset DDM by available MRI data
dat_all_ddm <- subset(dat_all_ddm, subj %in% mri_sample_subjx$subj)

# subset MRI by available DDM data
dat_mri <- subset(dat_mri, subj %in% dat_all_ddm$subj)

# create set for each timepoint
dat_bl1_ddm <- filter(dat_all_ddm, visit == "BL1")
# dat_bl2_ddm <- filter(dat_all_ddm, visit == "BL2")

# subset by available MRI data
dat_bl1_ddm <- subset(dat_bl1_ddm, subj %in% mri_sample_subjx$subj)

### BL1 DDM LMER
dat_bl1_ddm_v <- filter(dat_bl1_ddm, dat_bl1_ddm$parameter == "v")

mod_v <- lmer(mean ~ group * cttype + (1|subj), data = dat_bl1_ddm_v)
anova(mod_v, type = 3)

# descriptives - means by group 
#v_desc <- 
  dat_bl1_ddm_v %>%
  group_by(group, cttype) %>%
  summarise(mean = mean(mean), na.rm = TRUE)
  
# save list of DDM+MRI subject IDs
mri_ddm_sample_subjx <- unique(dat_bl1_ddm$subj)
mri_ddm_sample_subjx <- as.data.frame(mri_ddm_sample_subjx)
colnames(mri_ddm_sample_subjx)[1] = "subj"
```

# read in TOPX data
```{r}
dat_topx <- read.csv("~/Documents/umn_work/topx_analyses/data/aggregated_data_20240802.csv")
colnames(dat_topx)[15] <- "group"
colnames(dat_topx)[7] <- "cttype"
# subset by available MRI data
dat_topx <- subset(dat_topx, subj %in% mri_ddm_sample_subjx$subj)

## Baseline 1
dat_bl1_topx <- dat_topx %>% 
  filter(visit == "BL1") 

# ## Baseline 2
# dat_bl2_topx <- dat_topx %>% 
#   filter(visit == "BL2") 
# 
# ## match BL1 to BL2 TOPX 
# dat_bl1_topx <- subset(dat_bl1_topx, (subj %in% dat_bl2_topx$subj))
# dat_bl2_topx<- subset(dat_bl2_topx, (subj %in% dat_bl1_topx$subj))
# 
# ## merge TOPX data
# dat_all_topx <- rbind(dat_bl1_topx, dat_bl2_topx)
# dat_all_topx$subj_idx <- dat_all_topx$subj

### BL 1 Error LMER
mod_err <- lmer(error ~ group * cttype + (1|subj), data = dat_bl1_topx)
anova(mod_err, type = 3)
# significant, but not appropriate - need random effect
# mod_err <- lm(error ~ group * cttype, data = dat_bl1_topx)
# anova(mod_err)
# tried t-test but not significant - ugh this sample is so small!
dat_bl1_topx_bx <- filter(dat_bl1_topx, dat_bl1_topx$cttype == "BX")
t.test(error ~ group, dat_bl1_topx_bx)

# descriptives - means by group 
#err_desc <- 
  dat_bl1_topx %>%
  group_by(group, cttype) %>%
  summarise(error = mean(error), na.rm = TRUE)

### BL1 RT LMER
mod_rt <- lmer(rt_mdn ~ group * cttype + (1|subj), data = dat_bl1_topx)
anova(mod_rt, type = 3)

```

# read in demographics
```{r}
dat_demo <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/demographics/step_demographics_dx_20241101.csv")

## function to remove test cases, fix name formatting -------
clean_data <- function(data) {
  # rename subject id as "subj"
  data <- data %>% rename(subj = record_id)
  # identify test rows and filter them out
  ex_strings <- c('TEST', "Test", "test", "NDAR", "archive")
  dat_probs <- data[grep(paste(ex_strings, collapse='|'), 
                         data$subj, ignore.case = TRUE), ]
  data <- data[!data$subj %in% dat_probs$subj, ]
  # remove the "proofpoint" string from subj ids
  data$subj <- gsub('PROOFPOINT|-|[*]','', data$subj)
  # trim white spaces
  data$subj <- trimws(data$subj)
  return(as.data.frame(data))
}

dat_demo <- clean_data(dat_demo)

# subset by available DDM+MRI data
dat_demo <- subset(dat_demo, subj %in% mri_ddm_sample_subjx$subj)
```

# subset MRI data
## Bryon's edit LH
```{r}
# recommended from Google: 
# 137, 140, 141, 142, 148, 182, and 186
# Left_ContB_IPL_2, Left_ContB_PFClv_1, Left_ContB_PFClv_2, Left_ContB_PFClv_3, Left_ContC_Cingp_2, Left_DefaultB_PFCl_2, Left_DefaultB_PFCv_4
# mapped using: https://github.com/brainspaces/schaefer400/blob/master/schaefer400NodeNames.txt

dat_dlPFC_LH_Bryon <- dat_mri %>%
  select("subj", "visit", "group", "LH_ContB_IPL_2",
         "LH_ContB_PFClv_1",
         "LH_ContB_PFClv_2",
         "LH_ContB_PFClv_3",
         "LH_ContC_Cingp_2",
         "LH_DefaultB_PFCl_2",
         "LH_DefaultB_PFCv_4")

# descriptives - means by group 
dat_dlPFC_LH_Bryon %>%
  group_by(group) %>%
  summarise(
    LH_ContB_IPL_2 = mean(LH_ContB_IPL_2, 
                               na.rm = TRUE),
    LH_ContB_PFClv_1 = mean(LH_ContB_PFClv_1,
                                  na.rm = TRUE),
    LH_ContB_PFClv_2 = mean(LH_ContB_PFClv_2,
                                 na.rm = TRUE),
    LH_ContB_PFClv_3 = mean(LH_ContB_PFClv_3,
                            na.rm = TRUE),
    LH_ContC_Cingp_2 = mean(LH_ContC_Cingp_2,
                            na.rm = TRUE),
    LH_DefaultB_PFCl_2 = mean(LH_DefaultB_PFCl_2,
                              na.rm = TRUE),
    LH_DefaultB_PFCv_4 = mean(LH_DefaultB_PFCv_4,
                              na.rm = TRUE))

# combine all parcels into one dlPFC variable
dat_dlPFC_LH_Bryon$LH_PFCdl <- rowSums(dat_dlPFC_LH_Bryon[, c("LH_ContB_IPL_2", "LH_ContB_PFClv_1", "LH_ContB_PFClv_2", "LH_ContB_PFClv_3", "LH_ContC_Cingp_2", "LH_DefaultB_PFCl_2", "LH_DefaultB_PFCv_4")]) / 7

# compare group means
dat_dlPFC_LH_Bryon %>%
  group_by(group) %>%
  summarise(LH_PFCdl = mean(LH_PFCdl, na.rm = TRUE))

t.test(LH_PFCdl ~ group, data = dat_dlPFC_LH_Bryon)
```
## Bryon's edit RH
```{r}
# recommended from Google: 
# 137, 140, 141, 142, 148, 182, and 186

dat_dlPFC_RH_Bryon <- dat_mri %>%
  select("subj", "visit", "group", "RH_ContB_IPL_2",
         "RH_ContB_PFClv_1",
         "RH_ContB_PFClv_2",
         "RH_ContB_PFClv_3",
         "RH_ContC_Cingp_2")

# descriptives - means by group 
dat_dlPFC_RH_Bryon %>%
  group_by(group) %>%
  summarise(
    RH_ContB_IPL_2 = mean(RH_ContB_IPL_2, 
                               na.rm = TRUE),
    RH_ContB_PFClv_1 = mean(RH_ContB_PFClv_1,
                                  na.rm = TRUE),
    RH_ContB_PFClv_2 = mean(RH_ContB_PFClv_2,
                                 na.rm = TRUE),
    RH_ContB_PFClv_3 = mean(RH_ContB_PFClv_3,
                            na.rm = TRUE),
    RH_ContC_Cingp_2 = mean(RH_ContC_Cingp_2,
                            na.rm = TRUE))
# dropped last two parcels bc they don't exist in RH!

# combine all parcels into one dlPFC variable
dat_dlPFC_RH_Bryon$RH_PFCdl <- rowSums(dat_dlPFC_RH_Bryon[, c("RH_ContB_IPL_2", "RH_ContB_PFClv_1", "RH_ContB_PFClv_2", "RH_ContB_PFClv_3", "RH_ContC_Cingp_2")]) / 5

# compare group means
dat_dlPFC_RH_Bryon %>%
  group_by(group) %>%
  summarise(RH_PFCdl = mean(RH_PFCdl, na.rm = TRUE))

t.test(RH_PFCdl ~ group, data = dat_dlPFC_RH_Bryon)
```

## guess 1- all topographic networks
```{r}
# BA 9 and 46 = Control A, Default A, Default B,  DorsalAttn A
# Per MacDonald 2000:  left DLPFC (BA 9; Talairach coordinates x = –41, y = 18,z = 28; maximum F = 7.14; 36 pixels)

dat_dlPFC_v1 <- dat_mri %>%
  select("subj", "visit", "group", "LH_DorsAttnA_TempOcc_1","LH_DorsAttnA_TempOcc_2",
"LH_DorsAttnA_TempOcc_3", "LH_DorsAttnA_TempOcc_4",
"LH_DorsAttnA_ParOcc_1", "LH_DorsAttnA_ParOcc_2",
"LH_DorsAttnA_SPL_1", "LH_DorsAttnA_SPL_2",
"LH_DorsAttnA_SPL_3", "LH_DorsAttnA_SPL_4",
"LH_DorsAttnA_SPL_5", "LH_DorsAttnA_SPL_6",
"LH_DorsAttnA_SPL_7",
"RH_DorsAttnA_TempOcc_1", "RH_DorsAttnA_TempOcc_2",
"RH_DorsAttnA_TempOcc_3", "RH_DorsAttnA_ParOcc_1",
"RH_DorsAttnA_ParOcc_2", "RH_DorsAttnA_ParOcc_3",
"RH_DorsAttnA_SPL_1", "RH_DorsAttnA_SPL_2",
"RH_DorsAttnA_SPL_3", "RH_DorsAttnA_SPL_4",
"RH_DorsAttnA_SPL_5", "RH_DorsAttnA_SPL_6",
"RH_DorsAttnA_SPL_7", "RH_DorsAttnA_SPL_8",
"LH_ContA_Temp_1", "LH_ContA_IPS_1", "LH_ContA_IPS_2",
"LH_ContA_IPS_3", "LH_ContA_IPS_4", "LH_ContA_IPS_5",
"LH_ContA_PFCd_1", "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
"LH_ContA_PFCl_1", "LH_ContA_PFCl_2", "LH_ContA_PFCl_3", 
"LH_ContA_Cingm_1",
"RH_ContA_IPS_1", "RH_ContA_IPS_2", "RH_ContA_IPS_3",
"RH_ContA_IPS_4", "RH_ContA_PFCd_1", "RH_ContA_PFCl_1",
"RH_ContA_PFCl_2", "RH_ContA_PFCl_3", "RH_ContA_PFCl_4",
"RH_ContA_PFCl_5", "RH_ContA_Cingm_1",
"LH_DefaultA_IPL_1", "LH_DefaultA_IPL_2",
"LH_DefaultA_PFCd_1", "LH_DefaultA_PFCd_2",
"LH_DefaultA_PFCd_3", "LH_DefaultA_pCunPCC_1",
"LH_DefaultA_pCunPCC_2", "LH_DefaultA_pCunPCC_3", 
"LH_DefaultA_pCunPCC_4", "LH_DefaultA_pCunPCC_5",
"LH_DefaultA_pCunPCC_6", "LH_DefaultA_pCunPCC_7",
"LH_DefaultA_PFCm_1", "LH_DefaultA_PFCm_2",
"LH_DefaultA_PFCm_3", "LH_DefaultA_PFCm_4",
"LH_DefaultA_PFCm_5", "LH_DefaultA_PFCm_6",
"RH_DefaultA_Temp_1", "RH_DefaultA_IPL_1",
"RH_DefaultA_IPL_2", "RH_DefaultA_PFCd_1",
"RH_DefaultA_PFCd_2", "RH_DefaultA_pCunPCC_1",
"RH_DefaultA_pCunPCC_2", "RH_DefaultA_pCunPCC_3",
"RH_DefaultA_pCunPCC_4", "RH_DefaultA_pCunPCC_5",
"RH_DefaultA_PFCm_1", "RH_DefaultA_PFCm_2",
"RH_DefaultA_PFCm_3", "RH_DefaultA_PFCm_4",
"RH_DefaultA_PFCm_5", "RH_DefaultA_PFCm_6",
"LH_DefaultB_Temp_1", "LH_DefaultB_Temp_2",
"LH_DefaultB_Temp_3", "LH_DefaultB_Temp_4", 
"LH_DefaultB_Temp_5", "LH_DefaultB_Temp_6",
"LH_DefaultB_IPL_1", "LH_DefaultB_IPL_2",
"LH_DefaultB_PFCd_1", "LH_DefaultB_PFCd_2",
"LH_DefaultB_PFCd_3", "LH_DefaultB_PFCd_4",
"LH_DefaultB_PFCd_5", "LH_DefaultB_PFCd_6",
"LH_DefaultB_PFCl_1", "LH_DefaultB_PFCl_2",
"LH_DefaultB_PFCv_1", "LH_DefaultB_PFCv_2",
"LH_DefaultB_PFCv_3", "LH_DefaultB_PFCv_4",
"LH_DefaultB_PFCv_5",
"RH_DefaultB_Temp_1", "RH_DefaultB_Temp_2",
"RH_DefaultB_AntTemp_1", "RH_DefaultB_PFCd_1",
"RH_DefaultB_PFCd_2", "RH_DefaultB_PFCd_3",
"RH_DefaultB_PFCd_4", "RH_DefaultB_PFCd_5",
"RH_DefaultB_PFCv_1", "RH_DefaultB_PFCv_2", 
"RH_DefaultB_PFCv_3")

# data.frame(colnames(dat_dlPFC_v1))

dat_dlPFC_v1$dlPFC <- rowSums(dat_dlPFC_v1[, c(4:120)])/ 116

# Filter dataset by hemisphere
dat_dlPFC_v1_lh <- dat_dlPFC_v1[, grepl("LH", colnames(dat_dlPFC_v1)) | colnames(dat_dlPFC_v1) %in% c("subj", "visit", "group")]
dat_dlPFC_v1_lh$dlPFC_lh <- rowSums(dat_dlPFC_v1_lh[, c(4:68)])/ 64

dat_dlPFC_v1_rh <- dat_dlPFC_v1[, grepl("RH", colnames(dat_dlPFC_v1)) | colnames(dat_dlPFC_v1) %in% c("subj", "visit", "group")]
dat_dlPFC_v1_rh$dlPFC_rh <- rowSums(dat_dlPFC_v1_rh[, c(4:55)])/ 51

dat_comb <- merge(dat_dlPFC_v1, dat_bl1_ddm_v, by = "subj", all.x = TRUE)


```


```{r}
# # DorsalAttn A
# "LH_DorsAttnA_TempOcc_1","LH_DorsAttnA_TempOcc_2",
# "LH_DorsAttnA_TempOcc_3", "LH_DorsAttnA_TempOcc_4",
# "LH_DorsAttnA_ParOcc_1", "LH_DorsAttnA_ParOcc_2",
# "LH_DorsAttnA_SPL_1", "LH_DorsAttnA_SPL_2",
# "LH_DorsAttnA_SPL_3", "LH_DorsAttnA_SPL_4",
# "LH_DorsAttnA_SPL_5", "LH_DorsAttnA_SPL_6",
# "LH_DorsAttnA_SPL_7"
# 
# "RH_DorsAttnA_TempOcc_1", "RH_DorsAttnA_TempOcc_2",
# "RH_DorsAttnA_TempOcc_3", "RH_DorsAttnA_ParOcc_1",
# "RH_DorsAttnA_ParOcc_2", "RH_DorsAttnA_ParOcc_3",
# "RH_DorsAttnA_SPL_1", "RH_DorsAttnA_SPL_2",
# "RH_DorsAttnA_SPL_3", "RH_DorsAttnA_SPL_4",
# "RH_DorsAttnA_SPL_5", "RH_DorsAttnA_SPL_6",
# "RH_DorsAttnA_SPL_7", "RH_DorsAttnA_SPL_8"     
# 
# Control A
# "LH_ContA_Temp_1", "LH_ContA_IPS_1", "LH_ContA_IPS_2",
# "LH_ContA_IPS_3", "LH_ContA_IPS_4", "LH_ContA_IPS_5",
# "LH_ContA_PFCd_1", "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
# "LH_ContA_PFCl_1", "LH_ContA_PFCl_2", "LH_ContA_PFCl_3", 
# "LH_ContA_Cingm_1"  
# 
# "RH_ContA_IPS_1", "RH_ContA_IPS_2", "RH_ContA_IPS_3",
# "RH_ContA_IPS_4", "RH_ContA_PFCd_1", "RH_ContA_PFCl_1",
# "RH_ContA_PFCl_2", "RH_ContA_PFCl_3", "RH_ContA_PFCl_4",
# "RH_ContA_PFCl_5", "RH_ContA_Cingm_1"
# 
# Default A
# "LH_DefaultA_IPL_1", "LH_DefaultA_IPL_2",
# "LH_DefaultA_PFCd_1", "LH_DefaultA_PFCd_2",
# "LH_DefaultA_PFCd_3", "LH_DefaultA_pCunPCC_1",
# "LH_DefaultA_pCunPCC_2", "LH_DefaultA_pCunPCC_3", 
# "LH_DefaultA_pCunPCC_4", "LH_DefaultA_pCunPCC_5",
# "LH_DefaultA_pCunPCC_6", "LH_DefaultA_pCunPCC_7",
# "LH_DefaultA_PFCm_1", "LH_DefaultA_PFCm_2",
# "LH_DefaultA_PFCm_3", "LH_DefaultA_PFCm_4",
# "LH_DefaultA_PFCm_5", "LH_DefaultA_PFCm_6"
# 
# "RH_DefaultA_Temp_1", "RH_DefaultA_IPL_1",
# "RH_DefaultA_IPL_2", "RH_DefaultA_PFCd_1",
# "RH_DefaultA_PFCd_2", "RH_DefaultA_pCunPCC_1",
# "RH_DefaultA_pCunPCC_2", "RH_DefaultA_pCunPCC_3",
# "RH_DefaultA_pCunPCC_4", "RH_DefaultA_pCunPCC_5",
# "RH_DefaultA_PFCm_1", "RH_DefaultA_PFCm_2",
# "RH_DefaultA_PFCm_3", "RH_DefaultA_PFCm_4",
# "RH_DefaultA_PFCm_5", "RH_DefaultA_PFCm_6" 
# 
# Default B
# "LH_DefaultB_Temp_1", "LH_DefaultB_Temp_2",
# "LH_DefaultB_Temp_3", "LH_DefaultB_Temp_4", 
# "LH_DefaultB_Temp_5", "LH_DefaultB_Temp_6",
# "LH_DefaultB_IPL_1", "LH_DefaultB_IPL_2",
# "LH_DefaultB_PFCd_1", "LH_DefaultB_PFCd_2",
# "LH_DefaultB_PFCd_3", "LH_DefaultB_PFCd_4",
# "LH_DefaultB_PFCd_5", "LH_DefaultB_PFCd_6",
# "LH_DefaultB_PFCl_1", "LH_DefaultB_PFCl_2",
# "LH_DefaultB_PFCv_1", "LH_DefaultB_PFCv_2",
# "LH_DefaultB_PFCv_3", "LH_DefaultB_PFCv_4",
# "LH_DefaultB_PFCv_5"  
# 
# "RH_DefaultB_Temp_1", "RH_DefaultB_Temp_2",
# "RH_DefaultB_AntTemp_1", "RH_DefaultB_PFCd_1",
# "RH_DefaultB_PFCd_2", "RH_DefaultB_PFCd_3",
# "RH_DefaultB_PFCd_4", "RH_DefaultB_PFCd_5",
# "RH_DefaultB_PFCv_1", "RH_DefaultB_PFCv_2", 
# "RH_DefaultB_PFCv_3"


```

## guess 2 - select topographic networks

```{r}
dat_dlPFC_v2 <- dat_mri %>%
  select("subj", "visit", "group",
         
results <- dat %>%
  group_by(cttype) %>%
  do(model = lm(v ~ dlPFC, data = .)) %>%
  tidy(model) 
```

## guess 3 - all control networks
```{r}

dat_dlPFC_v2 <- dat_mri %>%
  select("subj", "visit", "group",

Control A
"LH_ContA_Temp_1", "LH_ContA_IPS_1", "LH_ContA_IPS_2",
"LH_ContA_IPS_3", "LH_ContA_IPS_4", "LH_ContA_IPS_5",
"LH_ContA_PFCd_1", "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
"LH_ContA_PFCl_1", "LH_ContA_PFCl_2", "LH_ContA_PFCl_3", 
"LH_ContA_Cingm_1"  

"RH_ContA_IPS_1", "RH_ContA_IPS_2", "RH_ContA_IPS_3",
"RH_ContA_IPS_4", "RH_ContA_PFCd_1", "RH_ContA_PFCl_1",
"RH_ContA_PFCl_2", "RH_ContA_PFCl_3", "RH_ContA_PFCl_4",
"RH_ContA_PFCl_5", "RH_ContA_Cingm_1"

Control B

Control C

```

## consensus
```{r}
dat_dlPFC_3p <- dat_mri %>%
  select("subj", "visit", "group", "LH_ContA_PFCd_1", 
         "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
         "LH_ContA_PFCl_1", "LH_ContA_PFCl_2",
         "LH_ContA_PFCl_3") 

dat_dlPFC_3p$dlPFC <- rowSums(dat_dlPFC_3p[, c(4:9)])/ 6

t.test(dlPFC ~ group, dat_dlPFC_3p)

# descriptives - means by group 
dat_dlPFC_3p %>%
  group_by(group) %>%
  summarise(
    LH_ContA_PFCd_1 = mean(LH_ContA_PFCd_1, 
                               na.rm = TRUE),
    LH_ContA_PFClv_1 = mean(LH_ContA_PFClv_1,
                                  na.rm = TRUE),
    LH_ContA_PFClv_2 = mean(LH_ContA_PFClv_2,
                                 na.rm = TRUE),
    LH_ContA_PFCl_1 = mean(LH_ContA_PFCl_1,
                            na.rm = TRUE),
    LH_ContA_PFCl_2 = mean(LH_ContA_PFCl_2,
                            na.rm = TRUE),
    LH_ContA_PFCl_3 = mean(LH_ContA_PFCl_3,
                              na.rm = TRUE))

dat_comb <- merge(dat_dlPFC_3p, dat_bl1_ddm_v, by = c("subj", "visit", "group"), all.x = TRUE)

# dat_comb %>%
#   group_by(cttype) %>%
#   nest() %>%
#   mutate(
#     model = map(data, ~ lm(mean ~ dlPFC * group, data = .x)),
#     tidied = map(model, tidy)                         
#   ) %>%
#   unnest(tidied)

# run LMER with all cttypes
mod_all <- lmer(mean ~ dlPFC * cttype * group + (1|subj), data = dat_comb)
anova(mod_all, type = 3)
print(emmeans(mod_all, list(pairwise ~ cttype), adjust = "mvt"))

dlPFC_center <- mean(dat_comb$dlPFC, na.rm = TRUE)
# Pairwise comparisons
emm <- emmeans(mod_all, ~ group * cttype | dlPFC, at = list(dlPFC = dlPFC_center))
# Contrast comparisons
pairs(emm)


# run LM with all cttypes
mod_all2 <- lm(mean ~ dlPFC * cttype * group, data = dat_comb)
anova(mod_all2)

# LMs separated by trial type
dat_comb_ax <- filter(dat_comb, cttype == "AX")
dat_comb_ay <- filter(dat_comb, cttype == "AY")
dat_comb_bx <- filter(dat_comb, cttype == "BX")
dat_comb_by <- filter(dat_comb, cttype == "BY")

mod_ax <- lm(mean ~ dlPFC * group, data = dat_comb_ax)
anova(mod_ax)
print(emmeans(mod_ax, list(pairwise ~ group), adjust = "mvt"))
cor.test(dat_comb_ax$mean, dat_comb_ax$dlPFC)

mod_ay <- lm(mean ~ dlPFC * group, data = dat_comb_ay)
anova(mod_ay)

mod_bx <- lm(mean ~ dlPFC * group, data = dat_comb_bx)
anova(mod_bx)

mod_by <- lm(mean ~ dlPFC * group, data = dat_comb_by)
anova(mod_by)

# patients only
dat_comb_ax_pt <- filter(dat_comb_ax, group == "Patient")
mod_ax_2 <- lm(mean ~ dlPFC, data = dat_comb_ax_pt)
anova(mod_ax_2)

# symptom relationships
cor.test(dat_comb_ax_pt$dlPFC, dat_comb_ax_pt$bprs_neg)
cor.test(dat_comb_ax_pt$dlPFC, dat_comb_ax_pt$bprs_disorg)
cor.test(dat_comb_ax_pt$dlPFC, dat_comb_ax_pt$bprs_pos)
cor.test(dat_comb_ax_pt$dlPFC, dat_comb_ax_pt$gfr)

```

# GOAL: linear regression to test if dlPFC activation predicts DR
More specifically, we 1) examined DRs associated with all trial types during this task, as well as cognitive control–associated DR, 2) recapitulated previously observed deficits in DLPFC activation during cognitive control in SZ, and 3) used linear regression to examine the extent to which DLPFC activation predicts DR in SZ and healthy control (HC) participants.
