---
title: "TOPX_ddm_dlPFC_20241214"
author: "Jessica Arend"
date: "2024-12-14"
output: html_document
---

```{r}
# clear workspace
rm(list=ls())

# read in packages
pacman::p_load(stats, stringr, dplyr, tidyr, ggplot2, lme4, emmeans, lmerTest, Matrix, pbkrtest, psych, purrr, performance)
```

# read in fMRI data
```{r}
# read in BL1 fMRI data
dat_mri <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/zstats_schaefer400+Tian_B-A.csv")

# look at column names - names ending in .rh or .lh are Tian parcels, names starting in RH_ or LH_ are Schaefer parcels
dat_mri_names <- colnames(dat_mri)

# reformat subject and visit variables
dat_mri$sub <- gsub("sub-", "", dat_mri$sub)
dat_mri$ses <- gsub("ses-", "", dat_mri$ses)
colnames(dat_mri)[1] <- "subj"
colnames(dat_mri)[2] <- "visit"

# shorten names for schaefer parcels by removing X17Networks
colnames(dat_mri)<-gsub("X17Networks_","",colnames(dat_mri))

# create group variable
dat_mri <- dat_mri %>% 
  mutate(
    group = case_when(
      str_sub(subj, 1, 3) == "SP1" ~ "Control",
      str_sub(subj, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ "UNK"), .after = contrast)

# store second variable list with rewritten names
dat_mri_names_abbrev <- colnames(dat_mri)

# Filter dataset by hemisphere
dat_mri_lh <- dat_mri[, grepl("LH", colnames(dat_mri)) | colnames(dat_mri) %in% c("subj", "visit", "group")]

dat_mri_rh <- dat_mri[, grepl("RH", colnames(dat_mri)) | colnames(dat_mri) %in% c("subj", "visit", "group")]

# save schaefer parcel names as dataframe
schaefer400 <- read.table("~/Documents/umn_work/topx_analyses/topx_ddm/dlpfc_project/schaefer400NodeNames.txt")
colnames(schaefer400)[1] <- "parcelname"
schaefer400 <- data.frame(parcelname = schaefer400, parcelnum = c (1:400))

# save list of mri subject IDs
mri_sample_subjx <- unique(dat_mri$subj)
mri_sample_subjx <- as.data.frame(mri_sample_subjx)
colnames(mri_sample_subjx)[1] = "subj"
# write.csv(mri_sample_subjx,file=paste0("/Users/arend103/Documents/umn_work/topx_analyses/topx_mri_ddm/topx_mri_sample_subjx_",gsub("-", "", Sys.Date()), ".csv"), row.names = FALSE)
```

# read in DDM data
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data <- function(types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_ddm/data/20241031_ddm_data/bl1/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]]))
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = "BL1", .after = participant_id)
}

# Column mappings for different file types
column_mappings <- list(
  v = c("participant_id", "v_ax", "v_ay", "v_bx", "v_by"),
  a = c("participant_id", "a_ax", "a_ay", "a_bx", "a_by"),
  t = c("participant_id", "t_ax", "t_ay", "t_bx", "t_by"),
  z = c("participant_id", "z_a", "z_b")
)

# Process data for each block
types <- names(column_mappings)
dat_ddm_bl1_wide <- process_data(types, column_mappings)

# Rename, pivot longer, and add `subj_type` column
dat_ddm_bl1 <- dat_ddm_bl1_wide %>%
  rename(subj = participant_id) %>%
  pivot_longer(
    cols = c(v_ax, v_ay, v_bx, v_by, a_ax, a_ay, a_bx, a_by, 
             t_ax, t_ay, t_bx, t_by, z_a, z_b),
    names_to = c("parameter", "cttype"), 
    names_sep = "_", 
    values_to = "mean"
  ) %>%
  mutate(
    group = case_when(
      str_sub(subj, 1, 3) == "SP1" ~ "Control",
      str_sub(subj, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ NA
    )
  )

# rename trials
dat_ddm_bl1 <- dat_ddm_bl1 %>% 
  mutate(cttype = case_when(cttype == "ax" ~ "AX",
                             cttype == "ay" ~ "AY",
                             cttype == "bx" ~ "BX", 
                             cttype == "by" ~ "BY",
                             cttype == "a" ~ "A",
                             cttype == "b" ~ "B",
                             TRUE ~ cttype))

# subset fMRI + DDM data
# compare subjects in MRI and DDM datasets and merge cases with both
setdiff(dat_ddm_bl1$subj, dat_mri$subj) # in DDM not MRI: n = 86
setdiff(dat_mri$subj, dat_ddm_bl1$subj) # in MRI not DDM: n = 0
# subset DDM by available MRI data
dat_ddm_bl1 <- subset(dat_ddm_bl1, subj %in% mri_sample_subjx$subj)
# subset MRI by available DDM data
dat_mri <- subset(dat_mri, subj %in% dat_ddm_bl1$subj)

# save list of DDM+MRI subject IDs
mri_ddm_sample_subjx <- unique(dat_ddm_bl1$subj)
mri_ddm_sample_subjx <- as.data.frame(mri_ddm_sample_subjx)
colnames(mri_ddm_sample_subjx)[1] = "subj"
```

# analyze + plot DDM
```{r}
# test group differences in drift rate
### BL1 DDM LMER
dat_ddm_bl1_v <- filter(dat_ddm_bl1, parameter == "v")

# don't need to use lmer because no repeated measures
mod_v <- lm(mean ~ group * cttype, data = dat_ddm_bl1_v)
check_model(mod_v)
anova(mod_v)

# descriptives - means by group 
(v_desc <- dat_ddm_bl1_v %>%
  group_by(group, cttype) %>%
  summarise(mean = mean(mean)))

# transform AY drift rate
dat_ddm_bl1_v_Abs <- dat_ddm_bl1_v %>%
  mutate(mean = if_else(cttype == "AY", -1 * mean, mean))

# plot
v_plot <- ggplot(dat_ddm_bl1_v_Abs,
                 aes(x = cttype, y = mean, group = group)) +
  stat_summary(fun ="mean", geom ="line", 
               aes(color = group), linewidth = 1.5,
               position = position_dodge(width = 0.3)) + 
  stat_summary(fun="mean", geom="point",
               aes(color = group), size = 3,
               position = position_dodge(width = 0.3)) +
  stat_summary(fun.data = mean_se, geom = "errorbar",
               aes(color = group), width = 0.2, linewidth = 1,
               position = position_dodge(width = 0.3)) + 
  labs(title = "TOPX Drift Rates", y = "Drift Rate (v)",
       x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.5, 3.2)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
print(v_plot)
# save plot
ggsave(paste0("graphs/", 
              format(Sys.Date(), "%Y%m%d"),
              "_dlpfc_driftrate_bl1.png"),
       v_plot, width = 6, height = 4)
```

# read in TOPX data
```{r}
# read in TOPX data
dat_topx <- read.csv("~/Documents/umn_work/topx_analyses/data/topx_aggregate_data/aggregate_topx_20250315.csv")

# keep BL1 data only and rename variables
dat_topx <- dat_topx %>% 
  filter(visit == "BL1") %>% 
  rename(group = subj_type, cttype = trial_type)

# subset by available MRI data
# compare subjects in MRI and TOPX datasets and merge cases with both
setdiff(dat_topx$subj, dat_mri$subj) # in TOPX not MRI: n = 107
setdiff(dat_mri$subj, dat_topx$subj) # in MRI not DDM: n = 0
dat_topx <- subset(dat_topx, subj %in% mri_ddm_sample_subjx$subj)
```

# analyze + plot TOPX
```{r}
### BL 1 Error LMER
mod_err <- lmer(error ~ group * cttype + (1|subj), data = dat_topx)
anova(mod_err, type = 3) # trial significant, group and interaction not
# mod_err <- lm(error ~ group * cttype, data = dat_topx)
# anova(mod_err) # closer to significant, but not appropriate - need random effect
# tried t-test but not significant - ugh this sample is so small!
dat_topx_bx <- filter(dat_topx, dat_topx$cttype == "BX")
t.test(error ~ group, dat_topx_bx)

### BL1 RT LMER
mod_rt <- lmer(rt_mdn ~ group * cttype + (1|subj), data = dat_topx)
anova(mod_rt, type = 3) # trial singificant, group and interaction trending

# descriptives - means by group 
(topx_desc <- 
  dat_topx %>%
  group_by(group, cttype) %>%
  summarise(error_mn = mean(error, na.rm = TRUE),
            err_sd = sd(error, na.rm = TRUE),
            rt_mn = mean(rt_mdn, na.rm = TRUE),
            rt_sd = sd(rt_mdn, na.rm = TRUE)))

# plot error BL1
plot_err_bl1 <- ggplot(dat_topx, 
                        aes(x= cttype, y=error, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group),
               linewidth = 1.5, 
               position = position_dodge(width = 0.3)) +
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3, position = position_dodge(width = 0.3)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar",
               aes(color = group), 
               width = .2, linewidth = 1,
               position = position_dodge(width = 0.3)) + 
  labs(title = "TOPX Error Rates", 
       y = "Error Rate", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.04, .31)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_bl1
# ggsave(paste0("graphs/", 
#               format(Sys.Date(), "%Y%m%d"),
#               "_dlpfc_error_bl1.png"),
#        plot_err_bl1, width = 6, height = 4)

# plot rt BL1
plot_rt_bl1 <- ggplot(dat_topx, 
                        aes(x= cttype, y=rt_mdn, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group),
               linewidth = 1.5, 
               position = position_dodge(width = 0.3)) +
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3, position = position_dodge(width = 0.3)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar",
               aes(color = group), 
               width = .2, linewidth = 1,
               position = position_dodge(width = 0.3)) + 
  labs(title = "TOPX Reaction Times", 
       y = "Median RT (ms)", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_bl1
# ggsave(paste0("graphs/", 
#               format(Sys.Date(), "%Y%m%d"),
#               "_dlpfc_rt_bl1.png"),
#        plot_rt_bl1, width = 6, height = 4)
```

# read in demographics
```{r}
#dat_demo <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/demographics/step_demographics_dx_20241101.csv")
dat_demo <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/demographics/step_demo_dx_20250125.csv")

## function to remove test cases, fix name formatting -------
clean_data <- function(data) {
  # rename subject id as "subj"
  data <- data %>% rename(subj = record_id)
  # identify test rows and filter them out
  ex_strings <- c('TEST', "Test", "test", "NDAR", "archive")
  dat_probs <- data[grep(paste(ex_strings, collapse='|'), 
                         data$subj, ignore.case = TRUE), ]
  data <- data[!data$subj %in% dat_probs$subj, ]
  # remove the "proofpoint" string from subj ids
  data$subj <- gsub('PROOFPOINT|-|[*]','', data$subj)
  # trim white spaces
  data$subj <- trimws(data$subj)
  return(as.data.frame(data))
}

dat_demo <- clean_data(dat_demo)

setdiff(dat_demo$subj, dat_mri$subj) # in demo not mri: n = 142
setdiff(dat_mri$subj, dat_demo$subj) # in mri not demo: n = 0

# subset by available DDM+MRI data
dat_demo <- dat_demo %>%
  filter(as.character(subj) %in% as.character(dat_mri$subj))
```

# subset MRI data
## Bryon's rec
```{r}
# # mapped using: https://github.com/brainspaces/schaefer400/blob/master/schaefer400NodeNames.txt
# 
# ###### Bryon's edit LH ###########
# # recommended from Google: 
# # 137, 140, 141, 142, 148, 182, and 186
# 
# dat_dlPFC_LH_Bryon <- dat_mri %>%
#   select("subj", "visit", "group", 
#          "LH_ContB_IPL_2",
#          "LH_ContB_PFClv_1",
#          "LH_ContB_PFClv_2",
#          "LH_ContB_PFClv_3",
#          "LH_ContC_Cingp_2",
#          "LH_DefaultB_PFCl_2",
#          "LH_DefaultB_PFCv_4")
# 
# # descriptives - means by group 
# dat_dlPFC_LH_Bryon %>%
#   group_by(group) %>%
#   summarise(
#     LH_ContB_IPL_2 = mean(LH_ContB_IPL_2, na.rm = TRUE),
#     LH_ContB_PFClv_1 = mean(LH_ContB_PFClv_1, na.rm = TRUE),
#     LH_ContB_PFClv_2 = mean(LH_ContB_PFClv_2, na.rm = TRUE),
#     LH_ContB_PFClv_3 = mean(LH_ContB_PFClv_3, na.rm = TRUE),
#     LH_ContC_Cingp_2 = mean(LH_ContC_Cingp_2, na.rm = TRUE),
#     LH_DefaultB_PFCl_2 = mean(LH_DefaultB_PFCl_2, na.rm = TRUE),
#     LH_DefaultB_PFCv_4 = mean(LH_DefaultB_PFCv_4, na.rm = TRUE))
# 
# # combine all parcels into one dlPFC variable
# dat_dlPFC_LH_Bryon$LH_PFCdl <- rowSums(dat_dlPFC_LH_Bryon[, c("LH_ContB_IPL_2", "LH_ContB_PFClv_1", "LH_ContB_PFClv_2", "LH_ContB_PFClv_3", "LH_ContC_Cingp_2", "LH_DefaultB_PFCl_2", "LH_DefaultB_PFCv_4")]) / 7
# 
# # compare group means
# dat_dlPFC_LH_Bryon %>%
#   group_by(group) %>%
#   summarise(LH_PFCdl = mean(LH_PFCdl, na.rm = TRUE))
# 
# t.test(LH_PFCdl ~ group, data = dat_dlPFC_LH_Bryon) # not sig - trend?
# 
# ####### Bryon's edit RH#########
# # recommended from Google: 
# # 137, 140, 141, 142, 148, 182, and 186
# 
# dat_dlPFC_RH_Bryon <- dat_mri %>%
#   select("subj", "visit", "group", 
#          "RH_ContB_IPL_2",
#          "RH_ContB_PFClv_1",
#          "RH_ContB_PFClv_2",
#          "RH_ContB_PFClv_3",
#          "RH_ContC_Cingp_2")
# # dropped last two parcels bc they don't exist in RH!
# 
# # descriptives - means by group 
# dat_dlPFC_RH_Bryon %>%
#   group_by(group) %>%
#   summarise(
#     RH_ContB_IPL_2 = mean(RH_ContB_IPL_2, na.rm = TRUE),
#     RH_ContB_PFClv_1 = mean(RH_ContB_PFClv_1, na.rm = TRUE),
#     RH_ContB_PFClv_2 = mean(RH_ContB_PFClv_2, na.rm = TRUE),
#     RH_ContB_PFClv_3 = mean(RH_ContB_PFClv_3, na.rm = TRUE),
#     RH_ContC_Cingp_2 = mean(RH_ContC_Cingp_2, na.rm = TRUE))
# 
# # combine all parcels into one dlPFC variable
# dat_dlPFC_RH_Bryon$RH_PFCdl <- rowSums(dat_dlPFC_RH_Bryon[, c("RH_ContB_IPL_2", "RH_ContB_PFClv_1", "RH_ContB_PFClv_2", "RH_ContB_PFClv_3", "RH_ContC_Cingp_2")]) / 5
# 
# # compare group means
# dat_dlPFC_RH_Bryon %>%
#   group_by(group) %>%
#   summarise(RH_PFCdl = mean(RH_PFCdl, na.rm = TRUE))
# 
# t.test(RH_PFCdl ~ group, data = dat_dlPFC_RH_Bryon) # not sig
```

## topographic networks
```{r}
# # Brodmanns Areas 9 and 46 = Control A, Default A, Default B,  DorsalAttn A
# # Per MacDonald 2000:  left DLPFC (BA 9; Talairach coordinates x = –41, y = 18,z = 28; maximum F = 7.14; 36 pixels)
# 
# dat_dlPFC_v1 <- dat_mri %>%
#   select("subj", "visit", "group",
#          # Dorsal Attention A Left
#          "LH_DorsAttnA_TempOcc_1","LH_DorsAttnA_TempOcc_2",
#          "LH_DorsAttnA_TempOcc_3", "LH_DorsAttnA_TempOcc_4",
#          "LH_DorsAttnA_ParOcc_1", "LH_DorsAttnA_ParOcc_2",
#          "LH_DorsAttnA_SPL_1", "LH_DorsAttnA_SPL_2",
#          "LH_DorsAttnA_SPL_3", "LH_DorsAttnA_SPL_4",
#          "LH_DorsAttnA_SPL_5", "LH_DorsAttnA_SPL_6",
#          "LH_DorsAttnA_SPL_7",
#          # Dorsal Attention A Right
#          "RH_DorsAttnA_TempOcc_1", "RH_DorsAttnA_TempOcc_2",
#          "RH_DorsAttnA_TempOcc_3", "RH_DorsAttnA_ParOcc_1",
#          "RH_DorsAttnA_ParOcc_2", "RH_DorsAttnA_ParOcc_3",
#          "RH_DorsAttnA_SPL_1", "RH_DorsAttnA_SPL_2",
#          "RH_DorsAttnA_SPL_3", "RH_DorsAttnA_SPL_4",
#          "RH_DorsAttnA_SPL_5", "RH_DorsAttnA_SPL_6",
#          "RH_DorsAttnA_SPL_7", "RH_DorsAttnA_SPL_8",
#          # Control A Left
#          "LH_ContA_Temp_1", "LH_ContA_IPS_1", "LH_ContA_IPS_2",
#          "LH_ContA_IPS_3", "LH_ContA_IPS_4", "LH_ContA_IPS_5",
#          "LH_ContA_PFCd_1", "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
#          "LH_ContA_PFCl_1", "LH_ContA_PFCl_2", "LH_ContA_PFCl_3", 
#          "LH_ContA_Cingm_1",
#          # Control A Right
#          "RH_ContA_IPS_1", "RH_ContA_IPS_2", "RH_ContA_IPS_3",
#          "RH_ContA_IPS_4", "RH_ContA_PFCd_1", "RH_ContA_PFCl_1",
#          "RH_ContA_PFCl_2", "RH_ContA_PFCl_3", "RH_ContA_PFCl_4",
#          "RH_ContA_PFCl_5", "RH_ContA_Cingm_1",
#          # Default A Left
#          "LH_DefaultA_IPL_1", "LH_DefaultA_IPL_2",
#          "LH_DefaultA_PFCd_1", "LH_DefaultA_PFCd_2",
#          "LH_DefaultA_PFCd_3", "LH_DefaultA_pCunPCC_1",
#          "LH_DefaultA_pCunPCC_2", "LH_DefaultA_pCunPCC_3",
#          "LH_DefaultA_pCunPCC_4", "LH_DefaultA_pCunPCC_5",
#          "LH_DefaultA_pCunPCC_6", "LH_DefaultA_pCunPCC_7",
#          "LH_DefaultA_PFCm_1", "LH_DefaultA_PFCm_2",
#          "LH_DefaultA_PFCm_3", "LH_DefaultA_PFCm_4",
#          "LH_DefaultA_PFCm_5", "LH_DefaultA_PFCm_6",
#          # Default A Right
#          "RH_DefaultA_Temp_1", "RH_DefaultA_IPL_1",
#          "RH_DefaultA_IPL_2", "RH_DefaultA_PFCd_1",
#          "RH_DefaultA_PFCd_2", "RH_DefaultA_pCunPCC_1",
#          "RH_DefaultA_pCunPCC_2", "RH_DefaultA_pCunPCC_3",
#          "RH_DefaultA_pCunPCC_4", "RH_DefaultA_pCunPCC_5",
#          "RH_DefaultA_PFCm_1", "RH_DefaultA_PFCm_2",
#          "RH_DefaultA_PFCm_3", "RH_DefaultA_PFCm_4",
#          "RH_DefaultA_PFCm_5", "RH_DefaultA_PFCm_6",
#          # Default B Left
#          "LH_DefaultB_Temp_1", "LH_DefaultB_Temp_2",
#          "LH_DefaultB_Temp_3", "LH_DefaultB_Temp_4", 
#          "LH_DefaultB_Temp_5", "LH_DefaultB_Temp_6",
#          "LH_DefaultB_IPL_1", "LH_DefaultB_IPL_2",
#          "LH_DefaultB_PFCd_1", "LH_DefaultB_PFCd_2",
#          "LH_DefaultB_PFCd_3", "LH_DefaultB_PFCd_4",
#          "LH_DefaultB_PFCd_5", "LH_DefaultB_PFCd_6",
#          "LH_DefaultB_PFCl_1", "LH_DefaultB_PFCl_2",
#          "LH_DefaultB_PFCv_1", "LH_DefaultB_PFCv_2",
#          "LH_DefaultB_PFCv_3", "LH_DefaultB_PFCv_4",
#          "LH_DefaultB_PFCv_5",
#          # Default B Right
#          "RH_DefaultB_Temp_1", "RH_DefaultB_Temp_2",
#          "RH_DefaultB_AntTemp_1", "RH_DefaultB_PFCd_1",
#          "RH_DefaultB_PFCd_2", "RH_DefaultB_PFCd_3",
#          "RH_DefaultB_PFCd_4", "RH_DefaultB_PFCd_5",
#          "RH_DefaultB_PFCv_1", "RH_DefaultB_PFCv_2", 
#          "RH_DefaultB_PFCv_3")
# # data.frame(colnames(dat_dlPFC_v1))
# 
# # create variable for summed activation of dlPFC
# dat_dlPFC_v1$dlPFC <- rowSums(dat_dlPFC_v1[, c(4:120)])/ 116
# 
# # Filter dataset by hemisphere
# dat_dlPFC_v1_lh <- dat_dlPFC_v1[, grepl("LH", colnames(dat_dlPFC_v1)) | colnames(dat_dlPFC_v1) %in% c("subj", "visit", "group")]
# dat_dlPFC_v1_lh$dlPFC_lh <- rowSums(dat_dlPFC_v1_lh[, c(4:68)])/ 64
# 
# dat_dlPFC_v1_rh <- dat_dlPFC_v1[, grepl("RH", colnames(dat_dlPFC_v1)) | colnames(dat_dlPFC_v1) %in% c("subj", "visit", "group")]
# dat_dlPFC_v1_rh$dlPFC_rh <- rowSums(dat_dlPFC_v1_rh[, c(4:55)])/ 51
# 
# #dat_comb <- merge(dat_dlPFC_v1, dat_ddm_bl1_v, by = "subj", all.x = TRUE)
```

## consensus (?)
```{r}
# dat_dlPFC_3p <- dat_mri %>%
#   select("subj", "visit", "group", "LH_ContA_PFCd_1", 
#          "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
#          "LH_ContA_PFCl_1", "LH_ContA_PFCl_2",
#          "LH_ContA_PFCl_3") 
# 
# dat_dlPFC_3p$dlPFC <- rowSums(dat_dlPFC_3p[, c(4:9)])/ 6
# 
# t.test(dlPFC ~ group, dat_dlPFC_3p)
# 
# # descriptives - means by group 
# dat_dlPFC_3p %>%
#   group_by(group) %>%
#   summarise(
#     LH_ContA_PFCd_1 = mean(LH_ContA_PFCd_1, 
#                                na.rm = TRUE),
#     LH_ContA_PFClv_1 = mean(LH_ContA_PFClv_1,
#                                   na.rm = TRUE),
#     LH_ContA_PFClv_2 = mean(LH_ContA_PFClv_2,
#                                  na.rm = TRUE),
#     LH_ContA_PFCl_1 = mean(LH_ContA_PFCl_1,
#                             na.rm = TRUE),
#     LH_ContA_PFCl_2 = mean(LH_ContA_PFCl_2,
#                             na.rm = TRUE),
#     LH_ContA_PFCl_3 = mean(LH_ContA_PFCl_3,
#                               na.rm = TRUE))
```

##  all control networks
```{r}
dat_dlPFC <- dat_mri %>%
  select("subj", "visit", "group",
         
         # Control A Left
         "LH_ContA_Temp_1", "LH_ContA_IPS_1", "LH_ContA_IPS_2",
         "LH_ContA_IPS_3", "LH_ContA_IPS_4", "LH_ContA_IPS_5",
         "LH_ContA_PFCd_1", "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
         "LH_ContA_PFCl_1", "LH_ContA_PFCl_2", "LH_ContA_PFCl_3", 
         "LH_ContA_Cingm_1",
         # Control A Right
         "RH_ContA_IPS_1", "RH_ContA_IPS_2", "RH_ContA_IPS_3",
         "RH_ContA_IPS_4", "RH_ContA_PFCd_1", "RH_ContA_PFCl_1",
         "RH_ContA_PFCl_2", "RH_ContA_PFCl_3", "RH_ContA_PFCl_4",
         "RH_ContA_PFCl_5", "RH_ContA_Cingm_1",
         
         # Control B Left
         "LH_ContB_Temp_1", "LH_ContB_Temp_2", "LH_ContB_IPL_1",
         "LH_ContB_IPL_2", "LH_ContB_IPL_3", "LH_ContB_PFCd_1",
         "LH_ContB_PFClv_1", "LH_ContB_PFClv_2", "LH_ContB_PFClv_3",
         "LH_ContB_PFCmp_1",
         # Control B Right
         "RH_ContB_Temp_1", "RH_ContB_Temp_2", "RH_ContB_IPL_1",
         "RH_ContB_IPL_2", "RH_ContB_IPL_3", "RH_ContB_IPL_4",
         "RH_ContB_PFCld_1", "RH_ContB_PFCld_2", "RH_ContB_PFCld_3",
         "RH_ContB_PFCld_4", "RH_ContB_PFClv_1", "RH_ContB_PFClv_2",
         "RH_ContB_PFClv_3", "RH_ContB_PFClv_4", "RH_ContB_PFCmp_1",

         # Control C Left
         "LH_ContC_pCun_1", "LH_ContC_pCun_2", "LH_ContC_pCun_3",
         "LH_ContC_Cingp_1", "LH_ContC_Cingp_2",
         # Control C Right
         "RH_ContC_pCun_1", "RH_ContC_pCun_2", "RH_ContC_pCun_3",
         "RH_ContC_pCun_4", "RH_ContC_pCun_5", "RH_ContC_Cingp_1",
         "RH_ContC_Cingp_2")

dat_dlPFC <- dat_dlPFC %>%
  mutate(dlPFC_sum = rowSums(across(4:64), na.rm = TRUE),
         ContA_sum = rowSums(select(., contains("ContA")), na.rm = TRUE),
         ContA_LH_sum = rowSums(select(., contains("LH_ContA")), na.rm = TRUE),
         ContA_RH_sum = rowSums(select(., contains("RH_ContA")), na.rm = TRUE),
         ContB_sum = rowSums(select(., contains("ContB")), na.rm = TRUE),
         ContB_LH_sum = rowSums(select(., contains("LH_ContB")), na.rm = TRUE),
         ContB_RH_sum = rowSums(select(., contains("RH_ContB")), na.rm = TRUE),
         ContC_sum = rowSums(select(., contains("ContC")), na.rm = TRUE),
         ContC_LH_sum = rowSums(select(., contains("LH_ContC")), na.rm = TRUE),
         ContC_RH_sum = rowSums(select(., contains("RH_ContC")), na.rm = TRUE),
         )

dat_dlPFC_lh <- dat_dlPFC %>%
  select(subj, visit, group, matches("LH_"))

dat_dlPFC_rh <- dat_dlPFC %>%
  select(subj, visit, group, matches("RH_"))
```

```{r}
t.test(dlPFC_sum ~ group, dat_dlPFC)
t.test(ContA_sum ~ group, dat_dlPFC)
t.test(ContB_sum ~ group, dat_dlPFC)
t.test(ContC_sum ~ group, dat_dlPFC)

# descriptives - means by group 
dat_dlPFC %>%
  group_by(group) %>%
  summarise(
    dlPFC_sum = mean(dlPFC_sum, na.rm = TRUE),
    ContA_sum = mean(ContA_sum, na.rm = TRUE),
    ContB_sum = mean(ContB_sum, na.rm = TRUE),
    ContC_sum = mean(ContC_sum, na.rm = TRUE))

```

```{r}
dat_comb <- merge(dat_dlPFC, dat_ddm_bl1_v, by = c("subj", "visit", "group"), all.x = TRUE)

# run LMER with all cttypes
# mod_all <- lmer(mean ~ dlPFC_sum * cttype * group + (1|subj), data = dat_comb) # not fitting
# mod_all <- lmer(mean ~ dlPFC_sum * cttype + group + (1|subj), data = dat_comb) # nonsig int
# mod_all <- lmer(mean ~ dlPFC_sum + cttype + group + (1|subj), data = dat_comb) # need group int for interpretation
mod_all <- lmer(mean ~ dlPFC_sum * group + cttype + (1|subj), data = dat_comb) # nonsig int
anova(mod_all, type = 3)
# posthocs
print(emtrends(mod_all, pairwise ~ group, var = "dlPFC_sum"))
print(emmeans(mod_all, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_all, list(pairwise ~ group), adjust = "mvt"))

# LMs separated by trial type
dat_comb_ax <- filter(dat_comb, cttype == "AX")
dat_comb_ay <- filter(dat_comb, cttype == "AY")
dat_comb_bx <- filter(dat_comb, cttype == "BX")
dat_comb_by <- filter(dat_comb, cttype == "BY")

mod_ax <- lm(mean ~ dlPFC_sum * group, data = dat_comb_ax)
anova(mod_ax)
print(emmeans(mod_ax, list(pairwise ~ group), adjust = "mvt"))
cor.test(dat_comb_ax$mean, dat_comb_ax$dlPFC)

mod_ay <- lm(mean ~ dlPFC_sum * group, data = dat_comb_ay)
anova(mod_ay)

mod_bx <- lm(mean ~ dlPFC_sum * group, data = dat_comb_bx)
anova(mod_bx)

mod_by <- lm(mean ~ dlPFC_sum * group, data = dat_comb_by)
anova(mod_by)

# patients only
dat_comb_ax_pt <- filter(dat_comb_ax, group == "Patient")
mod_ax_2 <- lm(mean ~ dlPFC_sum, data = dat_comb_ax_pt)
anova(mod_ax_2)

# symptom relationships
# error - need to merge in BPRS
cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$bprs_neg)
cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$bprs_disorg)
cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$bprs_pos)
cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$gfr)
```

# GOAL: linear regression to test if dlPFC activation predicts DR
More specifically, we 1) examined DRs associated with all trial types during this task, as well as cognitive control–associated DR, 2) recapitulated previously observed deficits in DLPFC activation during cognitive control in SZ, and 3) used linear regression to examine the extent to which DLPFC activation predicts DR in SZ and healthy control (HC) participants.
