---
title: "TOPX_ddm_dlPFC_20241214"
author: "Jessica Arend"
date: "2024-12-14"
output: html_document
---

```{r}
# clear workspace
rm(list=ls())

# read in packages
pacman::p_load(stats, stringr, dplyr, tidyr, ggplot2, lme4, emmeans, lmerTest, Matrix, pbkrtest, psych, purrr, performance, car)
```

# fMRI data
## read in
```{r}
# read in BL1 fMRI data
dat_mri <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/zstats_schaefer400+Tian_B-A.csv")

# look at column names - names ending in .rh or .lh are Tian parcels, names starting in RH_ or LH_ are Schaefer parcels
dat_mri_names <- colnames(dat_mri)

# reformat subject and visit variables
dat_mri$sub <- gsub("sub-", "", dat_mri$sub)
dat_mri$ses <- gsub("ses-", "", dat_mri$ses)
colnames(dat_mri)[1] <- "subj"
colnames(dat_mri)[2] <- "visit"

# shorten names for schaefer parcels by removing X17Networks
colnames(dat_mri)<-gsub("X17Networks_","",colnames(dat_mri))

# create group variable
dat_mri <- dat_mri %>% 
  mutate(
    group = case_when(
      str_sub(subj, 1, 3) == "SP1" ~ "Control",
      str_sub(subj, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ "UNK"), .after = contrast)

# store second variable list with rewritten names
dat_mri_names_abbrev <- colnames(dat_mri)

# Filter dataset by hemisphere
dat_mri_lh <- dat_mri[, grepl("LH", colnames(dat_mri)) | colnames(dat_mri) %in% c("subj", "visit", "group")]

dat_mri_rh <- dat_mri[, grepl("RH", colnames(dat_mri)) | colnames(dat_mri) %in% c("subj", "visit", "group")]

# save schaefer parcel names as dataframe
schaefer400 <- read.table("~/Documents/umn_work/topx_analyses/topx_ddm/dlpfc_project/schaefer400NodeNames.txt")
colnames(schaefer400)[1] <- "parcelname"
schaefer400 <- data.frame(parcelname = schaefer400, parcelnum = c (1:400))

# save list of mri subject IDs
mri_sample_subjx <- unique(dat_mri$subj)
mri_sample_subjx <- as.data.frame(mri_sample_subjx)
colnames(mri_sample_subjx)[1] = "subj"
# write.csv(mri_sample_subjx,file=paste0("/Users/arend103/Documents/umn_work/topx_analyses/topx_mri_ddm/topx_mri_sample_subjx_",gsub("-", "", Sys.Date()), ".csv"), row.names = FALSE)
```

## create networks - all control
```{r}
dat_dlPFC <- dat_mri %>%
  select("subj", "visit", "group",
         
         # Control A Left
         "LH_ContA_Temp_1", "LH_ContA_IPS_1", "LH_ContA_IPS_2",
         "LH_ContA_IPS_3", "LH_ContA_IPS_4", "LH_ContA_IPS_5",
         "LH_ContA_PFCd_1", "LH_ContA_PFClv_1", "LH_ContA_PFClv_2",
         "LH_ContA_PFCl_1", "LH_ContA_PFCl_2", "LH_ContA_PFCl_3", 
         "LH_ContA_Cingm_1",
         # Control A Right
         "RH_ContA_IPS_1", "RH_ContA_IPS_2", "RH_ContA_IPS_3",
         "RH_ContA_IPS_4", "RH_ContA_PFCd_1", "RH_ContA_PFCl_1",
         "RH_ContA_PFCl_2", "RH_ContA_PFCl_3", "RH_ContA_PFCl_4",
         "RH_ContA_PFCl_5", "RH_ContA_Cingm_1",
         
         # Control B Left
         "LH_ContB_Temp_1", "LH_ContB_Temp_2", "LH_ContB_IPL_1",
         "LH_ContB_IPL_2", "LH_ContB_IPL_3", "LH_ContB_PFCd_1",
         "LH_ContB_PFClv_1", "LH_ContB_PFClv_2", "LH_ContB_PFClv_3",
         "LH_ContB_PFCmp_1",
         # Control B Right
         "RH_ContB_Temp_1", "RH_ContB_Temp_2", "RH_ContB_IPL_1",
         "RH_ContB_IPL_2", "RH_ContB_IPL_3", "RH_ContB_IPL_4",
         "RH_ContB_PFCld_1", "RH_ContB_PFCld_2", "RH_ContB_PFCld_3",
         "RH_ContB_PFCld_4", "RH_ContB_PFClv_1", "RH_ContB_PFClv_2",
         "RH_ContB_PFClv_3", "RH_ContB_PFClv_4", "RH_ContB_PFCmp_1",

         # Control C Left
         "LH_ContC_pCun_1", "LH_ContC_pCun_2", "LH_ContC_pCun_3",
         "LH_ContC_Cingp_1", "LH_ContC_Cingp_2",
         # Control C Right
         "RH_ContC_pCun_1", "RH_ContC_pCun_2", "RH_ContC_pCun_3",
         "RH_ContC_pCun_4", "RH_ContC_pCun_5", "RH_ContC_Cingp_1",
         "RH_ContC_Cingp_2")

dat_dlPFC <- dat_dlPFC %>%
  mutate(dlPFC_sum = rowSums(across(4:64), na.rm = TRUE),
         ContA_sum = rowSums(select(., contains("ContA")), na.rm = TRUE),
         ContA_LH_sum = rowSums(select(., contains("LH_ContA")), na.rm = TRUE),
         ContA_RH_sum = rowSums(select(., contains("RH_ContA")), na.rm = TRUE),
         ContB_sum = rowSums(select(., contains("ContB")), na.rm = TRUE),
         ContB_LH_sum = rowSums(select(., contains("LH_ContB")), na.rm = TRUE),
         ContB_RH_sum = rowSums(select(., contains("RH_ContB")), na.rm = TRUE),
         ContC_sum = rowSums(select(., contains("ContC")), na.rm = TRUE),
         ContC_LH_sum = rowSums(select(., contains("LH_ContC")), na.rm = TRUE),
         ContC_RH_sum = rowSums(select(., contains("RH_ContC")), na.rm = TRUE),
         )

dat_dlPFC_lh <- dat_dlPFC %>%
  select(subj, visit, group, matches("LH_"))

dat_dlPFC_rh <- dat_dlPFC %>%
  select(subj, visit, group, matches("RH_"))
```

# DDM data
## read in
```{r}
# read in separate stats for bl1 and bl2, merge them - short form (thanks ChatGPT)
# Custom function to read, select, and join datasets
process_data <- function(types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_ddm/data/20241031_ddm_data/bl1/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]]))
  })
  
  # Perform full joins on all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = "BL1", .after = participant_id)
}

# Column mappings for different file types
column_mappings <- list(
  v = c("participant_id", "v_ax", "v_ay", "v_bx", "v_by"),
  a = c("participant_id", "a_ax", "a_ay", "a_bx", "a_by"),
  t = c("participant_id", "t_ax", "t_ay", "t_bx", "t_by"),
  z = c("participant_id", "z_a", "z_b")
)

# Process data for each block
types <- names(column_mappings)
dat_ddm_bl1_wide <- process_data(types, column_mappings)

# Rename, pivot longer, and add `subj_type` column
dat_ddm_bl1 <- dat_ddm_bl1_wide %>%
  rename(subj = participant_id) %>%
  pivot_longer(
    cols = c(v_ax, v_ay, v_bx, v_by, a_ax, a_ay, a_bx, a_by, 
             t_ax, t_ay, t_bx, t_by, z_a, z_b),
    names_to = c("parameter", "cttype"), 
    names_sep = "_", 
    values_to = "mean"
  ) %>%
  mutate(
    group = case_when(
      str_sub(subj, 1, 3) == "SP1" ~ "Control",
      str_sub(subj, 1, 3) == "SP2" ~ "Patient",
      TRUE ~ NA
    )
  )

# rename trials
dat_ddm_bl1 <- dat_ddm_bl1 %>% 
  mutate(cttype = case_when(cttype == "ax" ~ "AX",
                             cttype == "ay" ~ "AY",
                             cttype == "bx" ~ "BX", 
                             cttype == "by" ~ "BY",
                             cttype == "a" ~ "A",
                             cttype == "b" ~ "B",
                             TRUE ~ cttype))

# subset fMRI + DDM data
# compare subjects in MRI and DDM datasets and merge cases with both
setdiff(dat_ddm_bl1$subj, dat_mri$subj) # in DDM not MRI: n = 86
setdiff(dat_mri$subj, dat_ddm_bl1$subj) # in MRI not DDM: n = 0
# subset DDM by available MRI data
dat_ddm_bl1 <- subset(dat_ddm_bl1, subj %in% mri_sample_subjx$subj)
# subset MRI by available DDM data
dat_mri <- subset(dat_mri, subj %in% dat_ddm_bl1$subj)

# save list of DDM+MRI subject IDs
mri_ddm_sample_subjx <- unique(dat_ddm_bl1$subj)
mri_ddm_sample_subjx <- as.data.frame(mri_ddm_sample_subjx)
colnames(mri_ddm_sample_subjx)[1] = "subj"
```
## DDM intercepts
```{r}
# Custom function to read, select, and process datasets
process_data_intc <- function(block, types, column_mappings) {
  datasets <- lapply(types, function(type) {
    file_path <- paste0("~/Documents/umn_work/topx_analyses/topx_ddm/data/20241031_ddm_data/", block, "/stats_", type, ".csv")
    read.csv(file_path) %>%
      select(all_of(column_mappings[[type]])) %>%
      rename(!!paste0(type, "_ppt") := participant)
  })
  
  # Merge all datasets by "participant_id"
  Reduce(function(x, y) full_join(x, y, by = "participant_id"), datasets) %>%
    mutate(visit = toupper(block), .after = participant_id)
}

# Column mappings for each DDM parameter type
column_mappings_intc <- list(
  v = c("participant_id", "v_intc", "participant"),
  a = c("participant_id", "a_intc", "participant"),
  t = c("participant_id", "t_intc", "participant"),
  z = c("participant_id", "z_intc", "participant")
)

# Process only BL1 data
types_intc <- names(column_mappings_intc)
dat_ddm_bl1_intc <- process_data_intc("bl1", types_intc, column_mappings_intc)


# Compute combined subject+group intercepts
dat_ddm_bl1_intc <- dat_ddm_bl1_intc %>%
  mutate(v_sum = v_intc + v_ppt, .after = v_ppt) %>%
  mutate(a_sum = a_intc + a_ppt, .after = a_ppt) %>%
  mutate(t_sum = t_intc + t_ppt, .after = t_ppt) %>%
  mutate(z_sum = z_intc + z_ppt, .after = z_ppt)

dat_ddm_bl1_intc <- dat_ddm_bl1_intc %>% 
  rename(subj = participant_id) %>% 
  select(c(subj, v_sum))
dat_ddm_bl1_intc <- subset(dat_ddm_bl1_intc, subj %in% mri_sample_subjx$subj)
dat_intc_comb <- merge(dat_ddm_bl1_intc, dat_dlPFC, by = c("subj"), all.x = TRUE)
dat_intc_comb <- as.data.frame(dat_intc_comb)
```

## analyze + plot DDM
```{r}
# test group differences in drift rate
### BL1 DDM LMER
dat_ddm_bl1_v <- filter(dat_ddm_bl1, parameter == "v")
plot(density(dat_ddm_bl1_v$mean)) # bimodal distribution

# # model not converging
# mod_v <- lmer(mean ~ group * cttype + (1|subj), data = dat_ddm_bl1_v)
# isSingular(mod_v) # needs random effect
# 
# # z scores - doesn't help model converge
# hist(dat_ddm_bl1_v$mean)  # Check for extreme values
# dat_ddm_bl1_v$mean_z <- scale(dat_ddm_bl1_v$mean)
# mod_v_z <- lmer(mean_z ~ group * cttype + (1 | subj), data = dat_ddm_bl1_v)
# 
# # optimizer - doesn't help
# mod_v <- lmer(mean ~ group * cttype + (1|subj), data = dat_ddm_bl1_v,
#               control = lmerControl(optimizer = "bobyqa"))
# 
# # forced fixed effects - doesn't help
# mod_FEsubj <- lm(mean ~ group * cttype + factor(subj), data = dat_ddm_bl1_v)
# anova(mod_FEsubj)
# 
# # glmm - doesn't help
# pacman::p_load(glmmTMB)
# mod_tmb <- glmmTMB(mean ~ group * cttype + (1 | subj), data = dat_ddm_bl1_v)

# report this because it includes interaction
mod_v_fixed <- lm(mean ~ group * cttype, data = dat_ddm_bl1_v) 
check_model(mod_v_fixed)
Anova(mod_v_fixed, type = 3)
print(emmeans(mod_v_fixed, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_v_fixed, list(pairwise ~ group), adjust = "mvt"))
print(emmeans(mod_v_fixed, list(pairwise ~ group|cttype), adjust = "mvt"))
print(emmeans(mod_v_fixed, list(pairwise ~ cttype|group), adjust = "mvt"))

# dont report this but crossreference to validate above
mod_v_simple <- lmer(mean ~ group + cttype + (1|subj), data = dat_ddm_bl1_v)
check_model(mod_v_simple)
Anova(mod_v_simple, type = 3)
print(emmeans(mod_v_simple, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_v_simple, list(pairwise ~ group), adjust = "mvt"))

# LMs separated by trial type
dat_v_ax <- filter(dat_ddm_bl1_v, cttype == "AX")
dat_v_ay <- filter(dat_ddm_bl1_v, cttype == "AY")
dat_v_bx <- filter(dat_ddm_bl1_v, cttype == "BX")
dat_v_by <- filter(dat_ddm_bl1_v, cttype == "BY")

t.test(mean ~ group, dat_v_ax) #sig
t.test(mean ~ group, dat_v_ay) #not sig
t.test(mean ~ group, dat_v_bx) #sig
t.test(mean ~ group, dat_v_by) #sig

# descriptives - means by group 
(v_desc <- dat_ddm_bl1_v %>%
  group_by(group, cttype) %>%
  summarise(mean = mean(mean)))

# transform AY drift rate for plotting
dat_ddm_bl1_v_Abs <- dat_ddm_bl1_v %>%
  mutate(mean = if_else(cttype == "AY", -1 * mean, mean))

# plot
v_plot <- ggplot(dat_ddm_bl1_v_Abs,
                 aes(x = cttype, y = mean, group = group)) +
  stat_summary(fun ="mean", geom ="line", 
               aes(color = group), linewidth = 1.5,
               position = position_dodge(width = 0.3)) + 
  stat_summary(fun="mean", geom="point",
               aes(color = group), size = 3,
               position = position_dodge(width = 0.3)) +
  stat_summary(fun.data = mean_se, geom = "errorbar",
               aes(color = group), width = 0.2, linewidth = 1,
               position = position_dodge(width = 0.3)) + 
  labs(title = "TOPX Drift Rates", y = "Drift Rate",
       x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.5, 3.2)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                     labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
print(v_plot)
# save plot
ggsave(paste0("graphs/", 
              format(Sys.Date(), "%Y%m%d"),
              "_dlpfc_driftrate_bl1.png"),
       v_plot, width = 6, height = 4)
```

# TOPX data
## read in
```{r}
# read in TOPX data
dat_topx <- read.csv("~/Documents/umn_work/topx_analyses/data/topx_aggregate_data/aggregate_topx_20250315.csv")

# keep BL1 data only and rename variables
dat_topx <- dat_topx %>% 
  filter(visit == "BL1") %>% 
  rename(group = subj_type, cttype = trial_type)

# subset by available MRI data
# compare subjects in MRI and TOPX datasets and merge cases with both
setdiff(dat_topx$subj, dat_mri$subj) # in TOPX not MRI: n = 107
setdiff(dat_mri$subj, dat_topx$subj) # in MRI not DDM: n = 0
dat_topx <- subset(dat_topx, subj %in% mri_ddm_sample_subjx$subj)
```

## analyze + plot TOPX
```{r}
### BL 1 Error LMER
mod_err <- lmer(error ~ group * cttype + (1|subj), data = dat_topx)
anova(mod_err, type = 3) # trial significant, group and interaction not
# mod_err <- lm(error ~ group * cttype, data = dat_topx)
# anova(mod_err) # closer to significant, but not appropriate - need random effect
# tried t-test but not significant - ugh this sample is so small!
dat_topx_bx <- filter(dat_topx, dat_topx$cttype == "BX")
t.test(error ~ group, dat_topx_bx) # but not parametric!
wilcox.test(error ~ group, data = dat_topx_bx, exact = FALSE)
print(emmeans(mod_err, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_err, list(pairwise ~ group), adjust = "mvt"))

### BL1 RT LMER
mod_rt <- lmer(rt_mdn ~ group * cttype + (1|subj), data = dat_topx)
anova(mod_rt, type = 3) # trial singificant, group and interaction trending
print(emmeans(mod_rt, list(pairwise ~ cttype), adjust = "mvt"))
print(emmeans(mod_rt, list(pairwise ~ group), adjust = "mvt"))

# descriptives - means by group 
(topx_desc <- 
  dat_topx %>%
  group_by(group, cttype) %>%
  summarise(error_mn = mean(error, na.rm = TRUE),
            err_sd = sd(error, na.rm = TRUE),
            rt_mn = mean(rt_mdn, na.rm = TRUE),
            rt_sd = sd(rt_mdn, na.rm = TRUE)))

# plot error BL1
plot_err_bl1 <- ggplot(dat_topx, 
                        aes(x= cttype, y=error, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group),
               linewidth = 1.5, 
               position = position_dodge(width = 0.3)) +
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3, position = position_dodge(width = 0.3)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar",
               aes(color = group), 
               width = .2, linewidth = 1,
               position = position_dodge(width = 0.3)) + 
  labs(title = "TOPX Error Rates", 
       y = "Error Rate", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(0.04, .31)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_err_bl1
ggsave(paste0("graphs/",
              format(Sys.Date(), "%Y%m%d"),
              "_dlpfc_error_bl1.png"),
       plot_err_bl1, width = 6, height = 4)

# plot rt BL1
plot_rt_bl1 <- ggplot(dat_topx, 
                        aes(x= cttype, y=rt_mdn, group = group)) + 
  stat_summary(fun="mean", geom="line", aes(color = group),
               linewidth = 1.5, 
               position = position_dodge(width = 0.3)) +
  stat_summary(fun="mean", geom="point", aes(color = group),
               size = 3, position = position_dodge(width = 0.3)) + 
  stat_summary(fun.data = mean_se, geom = "errorbar",
               aes(color = group), 
               width = .2, linewidth = 1,
               position = position_dodge(width = 0.3)) + 
  labs(title = "TOPX Reaction Times", 
       y = "Median RT (ms)", x = "Trial Type", color = "Group") +
  coord_cartesian(ylim = c(280, 600)) +
  scale_color_manual(values=c("#2C737F", "#AA8829"),
                   labels=c("Ctl", "EP")) + 
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face="bold", size = 16),
        axis.title = element_text(face="bold", size = 20),
        legend.text = element_text(face="bold", size = 14),
        legend.title = element_text(face = "bold", size = 16),
        plot.title = element_text(face = "bold", size = 22))
plot_rt_bl1
ggsave(paste0("graphs/",
              format(Sys.Date(), "%Y%m%d"),
              "_dlpfc_rt_bl1.png"),
       plot_rt_bl1, width = 6, height = 4)
```

# demographics
## read in
```{r}
#dat_demo <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/demographics/step_demographics_dx_20241101.csv")
dat_demo <- read.csv("~/Documents/umn_work/topx_analyses/data/nontask_data/demographics/step_demo_dx_20250125.csv")

## function to remove test cases, fix name formatting -------
clean_data <- function(data) {
  # rename subject id as "subj"
  data <- data %>% rename(subj = record_id)
  # identify test rows and filter them out
  ex_strings <- c('TEST', "Test", "test", "NDAR", "archive")
  dat_probs <- data[grep(paste(ex_strings, collapse='|'), 
                         data$subj, ignore.case = TRUE), ]
  data <- data[!data$subj %in% dat_probs$subj, ]
  # remove the "proofpoint" string from subj ids
  data$subj <- gsub('PROOFPOINT|-|[*]','', data$subj)
  # trim white spaces
  data$subj <- trimws(data$subj)
  return(as.data.frame(data))
}
dat_demo <- clean_data(dat_demo)

# subset by available DDM+MRI data
setdiff(dat_demo$subj, dat_mri$subj) # in demo not mri: n = 142
setdiff(dat_mri$subj, dat_demo$subj) # in mri not demo: n = 0
dat_demo <- dat_demo %>%
  filter(as.character(subj) %in% as.character(dat_mri$subj))

# recode status_ppt_type (numeric) to group (labelled category)
dat_demo$group <- ifelse(dat_demo$status_ppt_type == 1, "Control", 
                     ifelse(dat_demo$status_ppt_type == 2, 
                            "Patient", NA))

# recode diagnosis - 5 split
# before: 0=control, 1=Sz, 2=SzAff, 3=Szform, 4=NOS, 5=BP, 6=MDD, 7=other
# now: 0 = control, 1 = Sz/SzAff/Szform, 2 = BP, 3 = MDD, 4 = NOS/other
dat_demo$dx_5split <- as.character(dat_demo$primary_dx)
dat_demo$dx_5split <- as.numeric(
  dplyr::recode(dat_demo$dx_5split,
                "0" = "0",
                "1" = "1",
                "2" = "1",
                "3" = "1",
                "4" = "4",
                "5" = "2",
                "6" = "3",
                "7" = "4"))

# recode affective/nonaffective psychosis
dat_demo$dx_affect <- as.character(dat_demo$primary_dx)
dat_demo$dx_affect <- as.numeric(
  dplyr::recode(dat_demo$dx_affect,
                "0" = "0", # control
                "1" = "1", # schizophrenia -> non-affective (NA)
                "2" = "1", # schizoaffective -> NA
                "3" = "1", # schizophreniform -> NA
                "4" = "1", # psychosis NOS -> NA
                "5" = "2", # bipolar with psychosis -> Aff
                "6" = "2", # major depression with psychosis - Aff
                "7" = "1")) # other unspecified psychosis -> NA


# recode gender into one variable, rather than two
dat_demo$gender <- if_else(is.na(dat_demo$gender_cis), dat_demo$gender_trans, dat_demo$gender_cis)

# recode race NAs/other
dat_demo <- dat_demo %>%
  mutate(race = ifelse(is.na(race), 6, race))
dat_demo <- dat_demo %>%
  mutate(race_5split = ifelse(race == 6, 5, race))
```

## analyze demographics
```{r}
# number of patients and controls
table(dat_demo$group)

### create datasets by group ----------
dat_demo_pt <- subset(dat_demo, group == "Patient") 
dat_demo_ctl <- subset(dat_demo, group == "Control")
nPt <- nrow(dat_demo_pt)
nCtl <- nrow(dat_demo_ctl)
```

### functions
```{r, echo = FALSE}
# function for count, %, and NA table - 2 split (pt/ctl)
table_ct_pct_2split <- function(var) {
  
  # Calculate distribution and percentages for patients
  count_pt <- table(dat_demo_pt[[var]])
  pct_pt <- round((count_pt/nPt)*100, 0)
  na_pt <- sum(is.na(dat_demo_pt[[var]]))
  
  # Calculate distribution and percentages for controls
  count_ctl <- table(dat_demo_ctl[[var]])
  pct_ctl <- round((count_ctl/nCtl)*100, 0)
  na_ctl <- sum(is.na(dat_demo_ctl[[var]]))
  
  # Create a summary table
  summary <- tibble(
    Group = c(rep("Patient", length(count_pt) + 1), 
            rep("Control", length(count_ctl) + 1)),
    Variable = c(names(count_pt), "NA", 
             names(count_ctl), "NA"),
    Count = c(as.numeric(count_pt), na_pt,
            as.numeric(count_ctl), na_ctl),
    Percentage = c(as.numeric(pct_pt), NA,
                 as.numeric(pct_ctl), NA)
    )
  summary
}

# function for mean, sd, and NA table - 2 split (pt/ctl)
table_m_sd_2split <- function(var) {
  
  # Calculate mean and standard deviation for patients
  mean_pt <- mean(dat_demo_pt[[var]], na.rm = TRUE)
  sd_pt <- sd(dat_demo_pt[[var]], na.rm = TRUE)
  
  # Calculate mean and standard deviation for controls
  mean_ctl <- mean(dat_demo_ctl[[var]], na.rm = TRUE)
  sd_ctl <- sd(dat_demo_ctl[[var]], na.rm = TRUE)
  
  # Count missing values for patients and controls
  na_pt <- sum(is.na(dat_demo_pt[[var]]))
  na_ctl <- sum(is.na(dat_demo_ctl[[var]]))
  
  # Create a summary table
  summary <- tibble(
    Group = c("Patient", "Control"),
    Mean = c(round(mean_pt, 2), round(mean_ctl, 2)),
    SD = c(round(sd_pt, 2), round(sd_ctl, 2)),
    Missing_Values = c(na_pt, na_ctl)  # Add missing values count
  )
  summary %>% mutate(across(where(is.numeric), as.character)) # this is needed to report two digits
}
```

### report means
```{r}
#gender: 1=man, 2=woman, 3=nonbinary/other
table_ct_pct_2split("gender")

# age
table_m_sd_2split("age")

# race: 0=white, 1=black/african am, 2=indigenous am/alaska native, 3=asian/asian am, 4=native hawaiian/pacific islander, 5=multiracial/other
table_ct_pct_2split("race_5split")

# ethnicity
table_ct_pct_2split("hispanic")

# dx: 0 = control, 1 = Sz/SzAff/Szform, 2 = BP, 3 = MDD, 4 = NOS/other
table_ct_pct_2split("dx_5split")
```

### group differences
```{r}
# gender - report fisher
chisq.test(dat_demo$gender, dat_demo$group)
fisher.test(dat_demo$gender, dat_demo$group)

# age
# welch's two-sample t-test - report this
t.test(age ~ status_ppt_type, data = dat_demo)
# student t-test (assumes equal variances)
t.test(age ~ status_ppt_type, data = dat_demo, var.equal = TRUE)
# test group variances to see if t-test are appropriate
#leveneTest(dat_demo$age, dat_demo$status_ppt_type, data = dat_demo)
var.test(age ~ status_ppt_type, data = dat_demo)
# wilcox aka mann-whitney U test
wilcox.test(age ~ status_ppt_type, data = dat_demo)

# race - report fisher
chisq.test(dat_demo$race, dat_demo$group)
fisher.test(dat_demo$race, dat_demo$group)

# ethnicity
chisq.test(dat_demo$hispanic, dat_demo$group)
```

# main analyses
## group diff in neural activation
```{r}
t.test(dlPFC_sum ~ group, dat_dlPFC)
t.test(ContA_sum ~ group, dat_dlPFC)
t.test(ContB_sum ~ group, dat_dlPFC)
t.test(ContC_sum ~ group, dat_dlPFC)

# descriptives - means by group 
dat_dlPFC %>%
  group_by(group) %>%
  summarise(
    dlPFC_sum = mean(dlPFC_sum, na.rm = TRUE),
    ContA_sum = mean(ContA_sum, na.rm = TRUE),
    ContB_sum = mean(ContB_sum, na.rm = TRUE),
    ContC_sum = mean(ContC_sum, na.rm = TRUE))

# Helper function for standard error
se <- function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x)))

# Reshape to long format
dat_dlPFC_long <- dat_dlPFC %>%
  select(group, ContA_sum, ContB_sum, ContC_sum) %>%
  pivot_longer(cols = starts_with("Cont"), 
               names_to = "ControlRegion", 
               values_to = "Value")

# Summarize mean and SE
dat_dlPFC_summary <- dat_dlPFC_long %>%
  group_by(group, ControlRegion) %>%
  summarise(
    MeanValue = mean(Value, na.rm = TRUE),
    SE = se(Value),
    .groups = 'drop'
  )

# try to add asterisks
# t-tests: EP vs. HC per region
p_vals <- dat_dlPFC_long %>%
  group_by(ControlRegion) %>%
  summarise(p = t.test(Value ~ group)$p.value)

# assign significance labels
p_vals <- p_vals %>%
  mutate(sig_label = case_when(
    p < 0.001 ~ "***",
    p < 0.01 ~ "**",
    p < 0.05 ~ "*",
    TRUE ~ "ns"
  ))

# for label placement above error bars
sig_labels <- dat_dlPFC_summary %>%
  group_by(ControlRegion) %>%
  summarise(y = max(MeanValue + SE) * 1.1, .groups = "drop") %>%
  left_join(p_vals, by = "ControlRegion")

# Relabel x-axis values
# Step 4: relabel both summary and sig_labels
new_levels <- c("ContA_sum", "ContB_sum", "ContC_sum")
new_labels <- c("Control A", "Control B", "Control C")

dat_dlPFC_summary$ControlRegion <- factor(dat_dlPFC_summary$ControlRegion,
                                         levels = new_levels,
                                         labels = new_labels)

sig_labels$ControlRegion <- factor(sig_labels$ControlRegion,
                                   levels = new_levels,
                                   labels = new_labels)

# set max y value
y_max <- dat_dlPFC_summary %>%
  mutate(upper = MeanValue + SE) %>%
  pull(upper) %>%
  max() * 1.2  # add 20% space for stars
```

### plot neural activation
```{r}
# Plot with error bars
plot_dlPFC <- ggplot(dat_dlPFC_summary, aes(x = ControlRegion, y = MeanValue, fill = group)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.7), width = 0.6) +
  geom_errorbar(aes(ymin = MeanValue - SE, ymax = MeanValue + SE),
                width = 0.2,
                linewidth = .5,
                position = position_dodge(width = 0.7)) +
  # geom_text(data = sig_labels,
  #           aes(x = ControlRegion, y = y, label = sig_label),
  #           inherit.aes = FALSE,
  #           size = 8, fontface = "bold") +
  labs(title = "Neural Activation during B>A", x = "Schaefer Network", 
       y = "Activation (mean Z)", fill = "Group") +
  scale_fill_manual(values = c("Patient" = "#AA8829", "Control" = "#2C737F"),
                    labels = c("Control" = "Ctl", "Patient" = "EP")) +
  #coord_cartesian(ylim = c(0, y_max)) +
  coord_cartesian(ylim = c(0, 32)) +
  scale_y_continuous(expand = c(0, 0)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"), 
        axis.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 16),
        legend.text = element_text(face = "bold", size = 12),
        legend.title = element_text(face = "bold", size = 14),
        plot.title = element_text(face = "bold", size = 20))
plot_dlPFC
ggsave(paste0("graphs/",
              format(Sys.Date(), "%Y%m%d"),
              "_dlpfc_activation_bl1.png"),
       plot_dlPFC, width = 6, height = 4)
```

## sum of control networks
### LMER of all trials
```{r}
dat_v_comb <- merge(dat_ddm_bl1_v, dat_dlPFC, by = c("subj", "visit", "group"), all.x = TRUE)

# run LMER with all cttypes
# mod_all <- lmer(mean ~ dlPFC_sum * group * cttype + (1|subj), 
#                 data = dat_v_comb) # model not converging
mod_all_fixed <- lm(mean ~ dlPFC_sum * group * cttype,
                data = dat_v_comb)
check_model(mod_all_fixed)
car::Anova(mod_all_fixed, type = 3)
summary(mod_all_fixed)

mod_all <- lmer(mean ~ dlPFC_sum * group + cttype + (1|subj), 
                data = dat_v_comb) # nonsig int
check_model(mod_all)
anova(mod_all, type = 3)
summary(mod_all)
# posthocs
print(emtrends(mod_all, pairwise ~ group, var = "dlPFC_sum")) # group by dlPFC
#print(emmeans(mod_all, list(pairwise ~ dlPFC), adjust = "mvt")) # v by trial type
print(emmeans(mod_all, list(pairwise ~ cttype), adjust = "mvt")) # v by trial type
print(emmeans(mod_all, list(pairwise ~ group), adjust = "mvt")) # v by group
```

### LMs by trials
```{r}
# LMs separated by trial type
dat_comb_ax <- filter(dat_v_comb, cttype == "AX")
dat_comb_ay <- filter(dat_v_comb, cttype == "AY")
dat_comb_bx <- filter(dat_v_comb, cttype == "BX")
dat_comb_by <- filter(dat_v_comb, cttype == "BY")

mod_ax <- lm(mean ~ dlPFC_sum * group, data = dat_comb_ax)
Anova(mod_ax, type = 3)
print(emmeans(mod_ax, list(pairwise ~ group), adjust = "mvt"))
print(emtrends(mod_ax, pairwise ~ group, var = "dlPFC_sum"))
cor.test(dat_comb_ax$mean, dat_comb_ax$dlPFC)
plot(dat_comb_ax$mean, dat_comb_ax$dlPFC)
```

## control A network
```{r}
# run lm of v intercepts - in case it changes the significance of contA
mod_ctlA_intc <- lm(v_sum ~ ContA_sum * group, data = dat_intc_comb)
check_model(mod_ctlA_intc)
car::Anova(mod_ctlA_intc, type = 3)
summary(mod_ctlA_intc)
# doesn't really do anything, too complicated to go to intercepts

# shouldnt report this bc doesnt account for repeated measures
mod_ctlA_fixed <- lm(mean ~ ContA_sum * group * cttype, data = dat_v_comb)
check_model(mod_ctlA_fixed)
car::Anova(mod_ctlA_fixed, type = 3)
summary(mod_ctlA_fixed)

# report this
mod_ctlA <- lmer(mean ~ ContA_sum * group + cttype + (1|subj), 
                data = dat_v_comb) # nonsig int
check_model(mod_ctlA)
anova(mod_ctlA, type = 3)
summary(mod_ctlA)
# posthocs
print(emtrends(mod_ctlA, pairwise ~ group, var = "dlPFC_sum")) # group by dlPFC
#print(emmeans(mod_ctlA, list(pairwise ~ dlPFC_sum), adjust = "mvt")) # v by trial type
print(emmeans(mod_ctlA, list(pairwise ~ cttype), adjust = "mvt")) # v by trial type
print(emmeans(mod_ctlA, list(pairwise ~ group), adjust = "mvt")) # v by group
```

# plot dlPFC and BX drift
```{r}
# bx correlation - most hypothesis driven
shapiro.test(dat_comb_bx$mean) #ok
shapiro.test(dat_comb_bx$dlPFC_sum) #ok
# across all ppts
cor.test(dat_comb_bx$mean, dat_comb_bx$dlPFC_sum)
cor.test(dat_comb_bx$mean, dat_comb_bx$ContA_sum)
# by group
dat_comb_bx %>%
  group_split(group) %>%
  map(~ cor.test(.x$mean, .x$ContA_sum))



# Styled scatterplot of mean vs dlPFC
plot_cor_bl1 <- ggplot(dat_comb_bx, aes(x = ContA_sum, y = mean, color = group)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_smooth(method = "lm", se = FALSE, linewidth = 1.5) +
  labs(title = "dlPFC Activation and BX Drift Rate",
       x = "Control A Network Activation", y = "Drift Rate of BX Trials", color = "Group") +
  scale_color_manual(values = c("#2C737F", "#AA8829"),
                     labels = c("Ctl", "EP")) +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text = element_text(face = "bold", size = 12),
        axis.title = element_text(face = "bold", size = 16),
        legend.text = element_text(face = "bold", size = 12),
        legend.title = element_text(face = "bold", size = 14),
        plot.title = element_text(face = "bold", size = 20))
plot_cor_bl1
ggsave(paste0("graphs/",
              format(Sys.Date(), "%Y%m%d"),
              "_dlpfc_drift_cor_bl1_flip.png"),
       plot_cor_bl1, width = 6, height = 4)

mod_ay <- lm(mean ~ dlPFC_sum * group, data = dat_comb_ay)
Anova(mod_ay, type = 3)
cor.test(dat_comb_ay$mean, dat_comb_ay$dlPFC)

mod_bx <- lm(mean ~ dlPFC_sum * group, data = dat_comb_bx)
Anova(mod_bx, type = 3)
cor.test(dat_comb_bx$mean, dat_comb_bx$dlPFC)

mod_by <- lm(mean ~ dlPFC_sum * group, data = dat_comb_by)
Anova(mod_by, type = 3)
cor.test(dat_comb_by$mean, dat_comb_by$dlPFC)

# patients only
dat_comb_ax_pt <- filter(dat_comb_ax, group == "Patient")
mod_ax_2 <- lm(mean ~ dlPFC_sum, data = dat_comb_ax_pt)
anova(mod_ax_2)
summary(mod_ax_2)
#print(emtrends(mod_ax_2, list(pairwise ~ dlPFC_sum), adjust = "mvt"))

# symptom relationships
# error - need to merge in BPRS
# cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$bprs_neg)
# cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$bprs_disorg)
# cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$bprs_pos)
# cor.test(dat_comb_ax_pt$dlPFC_sum, dat_comb_ax_pt$gfr)
```


# GOAL: linear regression to test if dlPFC activation predicts DR
More specifically, we 1) examined DRs associated with all trial types during this task, as well as cognitive control–associated DR, 2) recapitulated previously observed deficits in DLPFC activation during cognitive control in SZ, and 3) used linear regression to examine the extent to which DLPFC activation predicts DR in SZ and healthy control (HC) participants.
